### 2023-11-08 manuscript/manuscript.qmd
All analysis should be now up to date - fixed issue with SE/SD calculation in initial data prep - also began manuscript qmd

---
title: "Self-talk interventions and sport/motor performance: An updated systematic review and Bayesian meta-analysis"
author: "Hannah Corcoran, James Steele"
format: pdf
abstract: "Self-talk has been researched as an aspect of mental preparation for performance in sports and other motor tasks since the late 1980s. In 2011 Hatzigeorgiadis and colleagues systematically reviewed and meta-analysed three decades of self-talk intervention research including 32 studies. Yet, despite the general proliferation of meta-analyses, this topic has not been meta-analysed in the decade since their review which, at least for the main effect, provided a reasonably precise standardised mean difference estimate (0.48 [95% confidence interval: 0.38, 0.58]). Several further studies on self-talk interventions have been conducted in that time and it is of interest to explore what additional evidence they offer regarding the effects of self-talk interventions on sport/motor performance. Bayesian approaches are well positioned to explore how additional evidence changes our understanding of an effect; to see whether it has changed in sign, magnitude, or precision, or whether further research has largely been a ‘waste’. Therefore, our aim was to conduct an updated systematic review and Bayesian meta-analysis replicating the search, inclusion, and models of Hatzigeorgiadis et al. Informative priors were taken directly from Hatzigeorgiadis et al. A total of 28 studies were included in the final updated meta-analysis. The overall posterior pooled estimate for the standardised mean difference was almost exactly the same as the prior (mean: 0.46 [95% quantile interval: 0.38, 0.59]). Bayes factors were calculated for a range of effect sizes and indicated that the included studies largely reflected ‘weak’ evidence against effects ranging from ~0.3 to 0.7, and only provided ‘substantial’ evidence or greater against more extreme effects (either very small or very large). Results were largely similar for all moderator analyses which were updated too; either providing relatively weak evidence against effects found in the previous meta-analysis or evidence suggesting smaller effects for certain moderators. The findings of our updated Bayesian meta-analyses reiterate the positive effect of self-talk interventions on sport/motor performance. However, they also suggest that cumulatively the past decade and more of research has done little to further our understanding of these effects. Considering the limited resources and time for conducting research, it may be worth moving onto to other more pertinent questions regarding psychological interventions for sport/motor performance."
editor: 
  markdown: 
    wrap: sentence
---

<!-- Notes: Hatzigeorgiadis et al meta Focused on various aspects of task, self-talk, participants, and intervention... also explored "matching hypothesis" -->

<!-- Hardy et al - reflections paper Focus on measurement? -->

<!-- Should we also conduct a moderator analysis of studies doing manipulation checks and measurement of self-talk? -->

<!-- Other moderators? -->

<!-- Pressure? -->

<!-- Attention? -->

<!-- Interaction of population and type of self talk (instructional/motivational)? -->

<!-- Focus the review atheoretically? -->

<!-- Examining the effect of self-talk interventions -->

<!-- Add impact on attentional focus outcomes? -->

# Introduction

Self-talk has a long history of philosophical, theoretical, and empirical work [@geurtsMakingSenseSelf2018; @brinthauptSelftalkResearchChallenges2023; @latinjakSelfTalkInterdisciplinaryReview2023].
One area in which self-talk remains a popular topic of research up to this day is in the sport sciences [@vanraalteSelftalkReviewSportspecific2016; @hardyReflectionsMaturingResearch2018; @latinjakSelfTalkInterdisciplinaryReview2023].
Sport psychology as a broad field has focused on the theorising of psychological constructs that might impact upon performance, and the subsequent experimental testing of theoretically informed interventions to address these constructs.
For example, a recent umbrella review identified thirty meta-analyses exploring the effects of different sport psychology constructs upon performance, thirteen of them examining the effects of interventions, finding an overall standardised mean effect for positive constructs of 0.51 \[95% confidence interval: 0.42, 0.58\] [@lochbaumSportPsychologyPerformance2022].
Only one meta-analysis explored the effects of self-talk interventions; Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011].

The meta-analysis by Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011] included a total of 32 studies and 62 effect size estimates revealing an overall standardised mean difference estimate of 0.48 \[95% confidence interval: 0.38, 0.58\] and also explored the effects of various moderators of the effectiveness of self-talk interventions.
Around the time that Hatzigeorgiadis et al. conducted their meta-analysis the quantitative synthesis of research findings using meta-analytic tools was still relatively new in the sport sciences [@haggerMetaanalysisSportExercise2006].
However in the last decade, particularly in sport psychology, there has been an increasing reliance on meta-analyses [@lochbaumSportPsychologyPerformance2022; @haggerMetaanalysis2022].
Yet, despite the general proliferation of meta-analyses in the past decade, the effects of self-talk interventions has not been re-evaluated by means of such quantitative synthesis since 2011 when Hatzigeorgiadis et al. completed their work.
During this period though, empirical research regarding self-talk interventions for sport and motor performance has burgeoned leading some to reflect on the field as "maturing" post-2011 [@hardyReflectionsMaturingResearch2018].

Whilst self-talk as a field may have matured in the post-2011 years with theoretical advancements in conceptualisation of the construct and mediators of its effects on performance, efforts to improve operationalisation/measurement, and efforts to improve methodology used in studying self-talk [@brinthauptSelftalkResearchChallenges2023; @geurtsMakingSenseSelf2018; @hardyReflectionsMaturingResearch2018; @latinjakSelfTalkInterdisciplinaryReview2023; @vanraalteSelftalkReviewSportspecific2016] it could be argued that understanding of the effectiveness of self-talk interventions was "mature" prior to 2011.
The effect estimate from the meta-analysis of Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011] was already fairly precise, and indeed so to where many of the moderator estimates.
Several further studies on self-talk interventions have been conducted since 2011 and it is a reasonable question to ask, given the limited time and resource for conducting research in the field of sport science, to whether and to what extent these have advanced our understanding or whether they have largely contributed to "research waste".

Two questions that should (though arguably are not often enough particularly in sport science) be asked by researchers when planning a study of an experimental intervention is "what is the likelihood that the experimental intervention is superior to the control intervention given the evidence accumulated so far?" and "what is the likelihood that a new trial, given some design parameters and previous evidence, will demonstrate the superiority of the experimental intervention?".
The key here is to consider the *cumulative* nature of evidence provided by research.
Cumulative meta-analyses were proposed in the early 1990s and have since then been argued to be key tools to answering these questions and considering whether or not additional research is a worthwhile use of resources [@clarkeAccumulatingResearchSystematic2014; @graingerEvidenceSynthesisTackling2020] and Bayesian approaches are well positioned to tackle this [@biauUsingBayesianStatistics2017].
Within Bayesian statistical inference a prior probability distribution regarding the effect of interest is *updated* after the introduction of new evidence to a posterior probability distribution given Bayes theorem.

Given that there has not been, to the best of our knowledge, a meta-analytic synthesis of the effects of self-talk interventions effects upon sport/motor performance since Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011] it is unclear the extent to which the past decade and more of research has advanced our understanding or potentially contributed to research waste.
Therefore, our aim was to conduct an updated systematic review and Bayesian meta-analysis replicating the search, inclusion, and models of Hatzigeorgiadis et al.

# Method
The method for this systematic review and meta-analysis was adapted from Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011]. We extended their previous research by following the Preferred Reporting Items for Systematic reviews and Meta-analysis (PRISMA) guidelines [@pagePRISMA2020Statement2021]. We limited our searches to the date range of November 2011 to November 2023 to avoid double counting as we used the estimates from Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011] as informative priors in our meta-analyses which contain the information from studies prior to November 2011.

## Criteria for including studies
Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011] did not explicitly state a process or strategy to formulating their research question and search methods. However, we assume that the PICO (Participants, Intervention, Comparator and Outcome) framework was implicitly used and, with that assumption, we adopted the following inclusion criteria based on their description. Participants were healthy and of any performance level. The intervention was instruction to engage in positive self-talk[^1]. The comparator was no self-talk or unrelated self-talk. Outcomes were sport or motor task performance. We included both between and within group experimental designs with either pre-post, or post-only measurements of performance as well as within group pre-post trials.

[^1]: Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011] stated: *"As our purpose was to test the effectiveness of interventions aiming to improve performance, groups or conditions using negative ... or inappropriate self-talk ... were excluded. In addition, groups or conditions using assisted self-talk ... were also excluded as assisted self-talk involves the use of external aids, such as headphones, and was not considered pure self-talk intervention."*

## Search strategy
Studies were obtained through electronic journal searches and review articles along with personal communication. The following databases – Sport Discus, PsycINFO, PsycARTICLES and Medline – were selected through the EBSCO database to search for the keywords. The SCOPUS database was not used as it was not accessible through Solent University. Boolean commands of AND and OR were used with the keywords. These keywords were searched in the format of, with the application of the Boolean commands, self-talk OR self-instruction OR self-statements OR self-verbalizations OR verbal cues OR stimulus cueing OR thought content instructions AND sport OR performance OR motor performance OR task performance. The studies were all peer-reviewed, full text and published in English language journals. The search was limited to the date range of November 2011-November 2022. The search took place from October 2022-November 2022. An ethics statement was not required for this study. Zotero software was used for referencing and to manage the bibliography (Zotero 2022).

## Selection of studies
The PRISMA flow diagram was used to show a clear layout of the systematic review process. Studies were identified by searching the keywords (stated in the search strategy) in the databases (stated in the search strategy). Those studies were then downloaded into Covidence, a screening programme, where duplicates were removed (Covidence 2022). The remaining studies were screened by their title and abstract to see if they met the requirements of the inclusion criteria. Once that was completed, those studies were exported into excel as comma-separated values (csv). This showed that if any studies did not meet the criteria, they were removed. The next part of the screening phase consisted of assessing the full text of the studies for eligibility. This led to the final pool of studies that were assessed for inclusion in the review and meta-analysis.

## Data extraction
The data extracted from the studies were for all groups, all relevant groups in the study, pre and/or post intervention, means, sample sizes and either standard deviation, standard errors, variances or confidence intervals in order to calculate the effect sizes. The data extracted was imported into a spreadsheet in excel as a csv.

## Statistical analysis
Statistical analysis of the data extracted was performed in R, (v 4.0.2; R Core Team, https://www.r-project.org/). Studies were categorised by design (i.e., between-group, within-group and pre-post-group) and the means, sample sizes and either standard deviation, standard errors, variances or confidence intervals were extracted to calculate the standardised mean effect sizes in R. The standardised mean effect sizes were interpreted by using Cohen’s thresholds such that <0.2 to <0.5 is small, 0.5 to <0.8 is moderate and >0.8 is large (Cohen 2013). The standardised mean effect sizes were calculated such that a positive effect size value favoured self-talk improving sports performance. Given the inclusion of different study designs, the standardised mean effects were calculated appropriately according to their study design.
As the effect sizes calculated from the studies included had a nested structure (i.e., multiple effects nested within groups and nested within studies), and the intention to update Hatzigeorgiadis et al. (2011) study, a Bayesian multi-level meta-analysis was performed. The precision of the posterior estimates using 95% compatibility (confidence) intervals (CIs) were produced, weighted by the inverse sampling variance to account for the within- between and pre-post-study variance.
The Hatzigeorgiadis et al. (2011) study was also used as a prior by using its effect size. From the prior, a t-distribution and variance of 0.05 from the 95% CI was used and a degrees of freedom of 3. Furthermore, the posterior estimates of effect were calculated for each individual study and for the overall pooled estimate of the 95% CI. R-hat values, trace plots and posterior effects were examined to check the model fit and convergence.

### 2023-11-08 R/functions.R

@@ -4,6 +4,18 @@ read_prepare_data <- function(file) {
     mutate_at(c(2:9, 41:43, 45:48), as.factor) %>%
     clean_names() %>%
 
+    # Convert SE to SD
+    mutate(
+      pre_sd_st = replace_na(if_else(is.na(pre_sd_st),
+                                     pre_se_st * sqrt(n_st), pre_sd_st)),
+      pre_sd_con = replace_na(if_else(is.na(pre_sd_con),
+                                     pre_se_con * sqrt(n_con), pre_sd_con)),
+      post_sd_st = replace_na(if_else(is.na(post_sd_st),
+                                     post_se_st * sqrt(n_st), post_sd_st)),
+      post_sd_con = replace_na(if_else(is.na(post_sd_con),
+                                      post_se_con * sqrt(n_con), post_sd_con))
+    ) %>%
+
     # Add in pre-post correlations
     mutate(
       # Convert p to t (Change scores)
@@ -21,8 +33,10 @@ read_prepare_data <- function(file) {
       delta_se_con = if_else(delta_se_con < 0, delta_se_con * -1, delta_se_con),
 
       # Convert SE to SD (Change scores)
-      delta_sd_st = replace_na(delta_se_st * sqrt(n_st)),
-      delta_sd_con = replace_na(delta_se_con * sqrt(n_con)),
+      delta_sd_st = replace_na(if_else(is.na(delta_sd_st),
+                                       delta_se_st * sqrt(n_st), delta_sd_st)),
+      delta_sd_con = replace_na(if_else(is.na(delta_sd_con),
+                                        delta_se_con * sqrt(n_con), delta_sd_con)),
 
       # Add missing deltas
       delta_m_st = replace_na(post_m_st - pre_m_st),

### 2023-11-25 manuscript.qmd
All models now finalised, preprint final

---
title: "Self-talk interventions and sport/motor performance: An updated systematic review and Bayesian meta-analysis"
author: "Hannah Corcoran, James Steele"
format:
  pdf:
    include-in-header:
      text: |
       \usepackage[font=scrtipsize]{caption}

abstract: "Self-talk has been researched as an aspect of mental preparation for performance in sports and other motor tasks since the late 1980s. In 2011 Hatzigeorgiadis and colleagues systematically reviewed and meta-analysed three decades of self-talk intervention research including 32 studies. Yet, despite the general proliferation of meta-analyses, this topic has not been meta-analysed in the decade since their review which, at least for the main effect, provided a reasonably precise standardised mean difference estimate (0.48 [95% confidence interval: 0.38, 0.58]). Several further studies on self-talk interventions have been conducted in that time and it is of interest to explore what additional evidence they offer regarding the effects of self-talk interventions on sport/motor performance. Bayesian approaches are well positioned to explore how additional evidence changes our understanding of an effect; to see whether it has changed in sign, magnitude, or precision, or whether further research has largely been a ‘waste’. Therefore, our aim was to conduct an updated systematic review and Bayesian meta-analysis replicating the search, inclusion, and models of Hatzigeorgiadis et al. Informative priors were taken directly from Hatzigeorgiadis et al. A total of 28 studies were included in the final updated meta-analysis. The overall posterior pooled estimate for the standardised mean difference was almost exactly the same as the prior (mean: 0.46 [95% quantile interval: 0.38, 0.59]). Bayes factors were calculated for a range of effect sizes and indicated that the included studies largely reflected ‘weak’ evidence against effects ranging from ~0.3 to 0.7, and only provided ‘substantial’ evidence or greater against more extreme effects (either very small or very large). Results were largely similar for all moderator analyses which were updated too; either providing relatively weak evidence against effects found in the previous meta-analysis or evidence suggesting smaller effects for certain moderators. The findings of our updated Bayesian meta-analyses reiterate the positive effect of self-talk interventions on sport/motor performance. However, they also suggest that cumulatively the past decade and more of research has done little to further our understanding of these effects. Considering the limited resources and time for conducting research, it may be worth moving onto to other more pertinent questions regarding psychological interventions for sport/motor performance."
editor: 
  markdown: 
    wrap: sentence
bibliography: references.bib
csl: apa.csl
execute: 
  echo: false
  message: false
  warning: false

---
```{r}
library(patchwork)

```

<!-- Notes: Hatzigeorgiadis et al meta Focused on various aspects of task, self-talk, participants, and intervention... also explored "matching hypothesis" -->

<!-- Hardy et al - reflections paper Focus on measurement? -->

<!-- Should we also conduct a moderator analysis of studies doing manipulation checks and measurement of self-talk? -->

<!-- Other moderators? -->

<!-- Pressure? -->

<!-- Attention? -->

<!-- Interaction of population and type of self talk (instructional/motivational)? -->

<!-- Focus the review atheoretically? -->

<!-- Examining the effect of self-talk interventions -->

<!-- Add impact on attentional focus outcomes? -->

# Introduction

Self-talk has a long history of philosophical, theoretical, and empirical work [@geurtsMakingSenseSelf2018; @brinthauptSelftalkResearchChallenges2023; @latinjakSelfTalkInterdisciplinaryReview2023].
One area in which self-talk remains a popular topic of research up to this day is in the sport sciences [@vanraalteSelftalkReviewSportspecific2016; @hardyReflectionsMaturingResearch2018; @latinjakSelfTalkInterdisciplinaryReview2023].
Sport psychology as a broad field has focused on the theorising of psychological constructs that might impact upon performance, and the subsequent experimental testing of theoretically informed interventions to address these constructs.
For example, a recent umbrella review identified thirty meta-analyses exploring the effects of different sport psychology constructs upon performance, thirteen of them examining the effects of interventions, finding an overall standardised mean effect for positive constructs of 0.51 \[95% confidence interval: 0.42, 0.58\] [@lochbaumSportPsychologyPerformance2022].
Only one meta-analysis explored the effects of self-talk interventions; Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011].

The meta-analysis by Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011] included a total of 32 studies and 62 effect size estimates revealing an overall standardised mean difference estimate of 0.48 \[95% confidence interval: 0.38, 0.58\] and also explored the effects of various moderators of the effectiveness of self-talk interventions.
Around the time that Hatzigeorgiadis et al. conducted their meta-analysis the quantitative synthesis of research findings using meta-analytic tools was still relatively new in the sport sciences [@haggerMetaanalysisSportExercise2006].
However in the last decade, particularly in sport psychology, there has been an increasing reliance on meta-analyses [@lochbaumSportPsychologyPerformance2022; @haggerMetaanalysis2022].
Yet, despite the general proliferation of meta-analyses in the past decade, the effects of self-talk interventions has not been re-evaluated by means of such quantitative synthesis since 2011 when Hatzigeorgiadis et al. completed their work.
During this period though, empirical research regarding self-talk interventions for sport and motor performance has burgeoned leading some to reflect on the field as "maturing" post-2011 [@hardyReflectionsMaturingResearch2018].

Whilst self-talk as a field may have matured in the post-2011 years with theoretical advancements in conceptualisation of the construct and mediators of its effects on performance, efforts to improve operationalisation/measurement, and efforts to improve methodology used in studying self-talk [@brinthauptSelftalkResearchChallenges2023; @geurtsMakingSenseSelf2018; @hardyReflectionsMaturingResearch2018; @latinjakSelfTalkInterdisciplinaryReview2023; @vanraalteSelftalkReviewSportspecific2016] it could be argued that understanding of the effectiveness of self-talk interventions was "mature" prior to 2011.
The effect estimate from the meta-analysis of Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011] was already fairly precise, and indeed so to where many of the moderator estimates.
Several further studies on self-talk interventions have been conducted since 2011 and it is a reasonable question to ask, given the limited time and resource for conducting research in the field of sport science, to whether and to what extent these have advanced our understanding or whether they have largely contributed to "research waste".

Two questions that should (though arguably are not often enough particularly in sport science) be asked by researchers when planning a study of an experimental intervention is "what is the likelihood that the experimental intervention is superior to the control intervention given the evidence accumulated so far?" and "what is the likelihood that a new trial, given some design parameters and previous evidence, will demonstrate the superiority of the experimental intervention?".
The key here is to consider the *cumulative* nature of evidence provided by research.
Cumulative meta-analyses were proposed in the early 1990s and have since then been argued to be key tools to answering these questions and considering whether or not additional research is a worthwhile use of resources [@clarkeAccumulatingResearchSystematic2014; @graingerEvidenceSynthesisTackling2020] and Bayesian approaches are well positioned to tackle this [@biauUsingBayesianStatistics2017].
Within Bayesian statistical inference a prior probability distribution regarding the effect of interest is *updated* after the introduction of new evidence to a posterior probability distribution given Bayes theorem.

Given that there has not been, to the best of our knowledge, a meta-analytic synthesis of the effects of self-talk interventions effects upon sport/motor performance since Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011] it is unclear the extent to which the past decade and more of research has advanced our understanding or potentially contributed to research waste.
Therefore, our aim was to conduct an updated systematic review and Bayesian meta-analysis replicating the search, inclusion, and models of Hatzigeorgiadis et al.

# Method

The method for this systematic review and meta-analysis was adapted from Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011].
We extended their previous research by following the Preferred Reporting Items for Systematic reviews and Meta-analysis (PRISMA) guidelines [@pagePRISMA2020Statement2021].
We limited our searches to the date range of November 2011 to November 2023 to avoid double counting as we used the estimates from Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011] as informative priors in our meta-analyses which contain the information from studies prior to November 2011.

## Criteria for including studies

Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011] did not explicitly state a process or strategy to formulating their research question and search methods.
However, we assume that the PICO (Participants, Intervention, Comparator and Outcome) framework was implicitly used and, with that assumption, we adopted the following inclusion criteria based on their description.
Participants were healthy and of any performance level.
The intervention was instruction to engage in positive self-talk[^1].
The comparator was no self-talk or unrelated self-talk.
Outcomes were sport or motor task performance.
We included both between and within group experimental designs with either pre-post, or post-only measurements of performance as well as within group pre-post trials.

[^1]: Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011] stated: *"As our purpose was to test the effectiveness of interventions aiming to improve performance, groups or conditions using negative ... or inappropriate self-talk ... were excluded. In addition, groups or conditions using assisted self-talk ... were also excluded as assisted self-talk involves the use of external aids, such as headphones, and was not considered pure self-talk intervention."*

## Search strategy

Studies were obtained through electronic journal searches and review articles along with personal records and communication.
The following databases -- Sport Discus, PsycINFO, PsycARTICLES and Medline -- were selected through the EBSCO database to search for the keywords.
The SCOPUS database was not used as it was not accessible through Solent University[^2].
Boolean commands of AND and OR were used with the keywords.
These keywords were searched in the format of, with the application of the Boolean commands, (self-talk OR self-instruction OR self-statements OR self-verbalizations OR verbal cues OR stimulus cueing OR thought content instructions) AND (sport OR performance OR motor performance OR task performance).
The studies were all peer-reviewed, full text and published in English language journals.
The search was limited to the date range of November 2011-November 2023.
An initial search took place from October 2022-November 2022 as this project was completed as part of the lead authors undergraduate thesis.
We subsequently updated the search from November 2022-November 2023 prior to preparing this manuscript for publication.

[^2]: Though we feel fairly confident, given the number of studies identified and the findings of our models reported below, that any missed studies would be unlikely to qualitatively impact the overall findings and conclusions of this work.

## Selection of studies

TO ADD

<!-- The PRISMA flow diagram was used to show a clear layout of the systematic review process. Studies were identified by searching the keywords (stated in the search strategy) in the databases (stated in the search strategy). Those studies were then downloaded into Covidence, a screening programme, where duplicates were removed (Covidence 2022). The remaining studies were screened by their title and abstract to see if they met the requirements of the inclusion criteria. Once that was completed, those studies were exported into excel as comma-separated values (csv). This showed that if any studies did not meet the criteria, they were removed. The next part of the screening phase consisted of assessing the full text of the studies for eligibility. This led to the final pool of studies that were assessed for inclusion in the review and meta-analysis. -->

## Data extraction

The data extracted from the studies were for all positive self-talk intervention groups/conditions and for control comparison designs for the relevant comparator group/condition.
Pre and/or post intervention and comparator, means, sample sizes and either standard deviation, standard errors, variances or confidence intervals were extracted in order to calculate the effect sizes. Also, in order to update the moderator analyses conducted by Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011] we also coded each effect size for motor demands (fine or gross), participant group (non-athletes[^3] vs beginner athletes vs experienced athletes), self-talk content[^4] (motivational vs instructional), the combination of motor demands and self-talk content to examine the matching hypothesis (motivational/gross vs motivational/fine vs instructional/gross vs instructional/fine), the task novelty (novel vs learned), cue selection and overtness selection (self-selected vs assigned), if the study was acute or involved a chronic training intervention (no-training vs training), and the study design[^5] (pre/post - experimental/control vs pre/post - experimental vs post - experimental/control). The data extracted was imported into a spreadsheet in excel as a csv.

[^3]: Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011] referred to their non-athlete group as "students" presumably because in all studies they included it was the case that all non-athletes were from student populations. As this was not necessarily the case for studies included in our updated analyses we refer to them as "non-athletes".

[^4]: Some studies we included in our updated analysis used combined instructional and motivational, and also other forms of self-talk content e.g., rational. We coded these new categories also.

[^5]: Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011] included studies with multiple baseline measures but we did not identify any studies meeting this design in our updated analysis.

## Statistical analysis

Statistical analysis of the data extracted was performed in R, (v 4.2.2; R Core Team, https://www.r-project.org/) and RStudio (.
As noted, we adopted a Bayesian approach to the present meta-analysis.
Specifically, we adopted informative priors from the models reported by Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011] and replicated their analyses using appropriate model specifications given the structure of the data.
All code utilised for data preparation and analyses are available in either the Open Science Framework page for this project [https://osf.io/dqwh5/](https://osf.io/dqwh5/) or the corresponding GitHub repository [https://github.com/jamessteeleii/self_talk_meta_analysis_update](https://github.com/jamessteeleii/self_talk_meta_analysis_update).
The `renv` package [@usheyRenvProjectEnvironments2023] was used for package version reproducibility, and the a function based analysis pipeline using the `targets` package [@landauTargetsDynamicFunctionOriented2023] was employed (the analysis pipeline can be viewed here *ADD VISNETWORK*). Standardised effect sizes were all calculated using the `metafor` package [@viechtbauerMetaforMetaAnalysisPackage2023]. The main package `brms` [@burknerBrmsBayesianRegression2023] was used in fitting all the Bayesian meta-analysis models. Prior and posterior draws were taken using `tidybayes` [@kayTidybayesTidyData2023] and `marginaleffects` [@arel-bundockMarginaleffectsPredictionsComparisons2023] packages. Bayes factors were calculated using the `bayestestR` package [@makowskiBayestestRUnderstandDescribe2023]. All visualisations were created using `ggplot2` [@wickhamGgplot2CreateElegant2023], `tidybayes`, and the `patchwork` [@pedersenPatchworkComposerPlots2023] packages.

Effect sizes were calculated as standardised mean differences dependent on the design of the study. Firstly all were signed such that a positive effect indicated that the self-talk intervention was favoured. For studies utilising a pre-post-test control comparison design we calculated the standardised mean difference between groups/conditions using the pooled pre-test standard deviation as per Morris [@morrisEstimatingEffectSizes2008]. For post-test only control comparison designs we calculated the standardised mean difference between groups/conditions based upon the pooled post-test standard deviation. Lastly, for single arm within group pre-post designs we calculated the standardised mean difference from pre- to post-intervention using the pre-test standard deviation. All were calculated using the `escalc` function from the `metafor` package.

Though it was not entirely clear from the reporting in the meta-analysis of Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011], they noted including a greater number of effect sizes than individual studies. As such it was likely that their data had a hierarchical structure with effects nested within studies whether they explicitly applied a hierarchical model to it or not. The studies we identified and included also had hierarchical structure whereby we had effects nested within groups (for example when there were multiple self-talk interventions examined) nested within experiments (for example when a study reported on multiple experiments using different samples and/or designs) nested within studies. As such, we used multilevel mixed effects meta-analyses with nested random intercepts for effects, groups, experiments, and studies. Effects were all weighted by the inverse sampling variance. A main model was produced which included all effects and was intended to update the overall model from Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011] whereby their overall estimate reflected the fixed model intercept. In addition we produced models for each of the aforementioned categorical moderators where we excluded the model intercept in order to set priors for each category directly based on the estimates and their precision reported by Hatzigeorgiadis et al.[^6].

[^6]: It is not clear exactly from the reporting by Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011] as to whether their moderator analyses involved fitting their models to datasets constructed separately whereby they were filtered to only include the relevant category for the moderator, or if they were fit together including all categories. We opted to fit them together for parsimony here.

Priors for each model were set informatively for the intervention effects, and were set to be weakly regularising for the heterogeneity (i.e., $\tau$) at all levels of the model[^7]. Intervention effects were set with priors based on the effect estimates from Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011] reported in their table 1 using a $t$-distribution ($t(k,\mu,\sigma)$) with $k-2$ degrees of freedom [@higginsReevaluationRandomeffectsMetaanalysis2009] in which we assumed $k$ to be the number of effects included in the models reported by Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011]. For the main model the prior for the intervention effect was set directly on the model intercept i.e., $t(60, 0.48, 0.05)$. For the moderator models as noted we removed the model intercept allowing us to set the priors directly on each category for each moderator based on the estimates from Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011] table 1. In cases where moderators had new categories introduced in the newer studies included in our analyses we used $\mu=0.48$ and $\sigma=0.05$ taken from the overall estimate of Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011] and applied degrees of freedom $k=3$ to be more conservative and allow greater mass in the tails of the prior distribution for these categories. In all models the heterogeneity priors at each level were set using the default weakly regularising prior in `brms`; a half-$t$-distribution with $\mu=0$, $\sigma=2.5$, and $k=3$. This constrained the prior to only allow positively signed values for $\tau$ though over a wide range of possible values.

[^7]: Though Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011] report on $\tau$ it is not clear what level this applies to (and as noted it is not clear if they employed a hierachical model) and they do not report any interval estimate for this making it difficult to specify an informative prior distribution. As such, and given suggestions regarding heterogeneity priors [@williamsBayesianMetaAnalysisWeakly2018; @roverWeaklyInformativePrior2021], we opted for a weakly regularising distribution at all levels.

As we were interested in determining how much the new evidence produced since Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011] had updated our understanding of the effects of self-talk interventions we fit each model using four Monte Carlo Markov Chains each with 4000 warmup and 40000 sampling iterations. This was in order to obtain precise Bayes Factors using the Savage-Dickey ratio [@gronauBridgesamplingPackageEstimating2020].

From each model we obtained draws from the posterior distributions for the intervention effects (i.e., the expectation of the value of the parameters posterior probability distribution) in order to present probability density functions visually, and also to calculate mean and 95% quantile intervals (i.e., 'credible' or 'compatibility' intervals) for each estimate. These gave us the most probably value of the parameter in addition to the range from 2.5% to 97.5% percentiles. The same was done drawing samples from the prior distributions only in order to present both distributions visually for comparison of the prior to posterior updating. For the main model draws were taken at the study level and an ordered forest plot produced showing each studies posterior distribution along with mean and 95% quantile intervals. We also calculated the 95% prediction intervals providing the range over which we can expect 95% of future effect estimates to fall and present each individual effect size on the forest plot. To compliment the visual inspection of prior to posterior updating we also present log10 Bayes Factors (log10[BF]) calculated *against* effects ranging from a standardised mean difference of 0 through to 1 and plot these log10(BF) curves for each model intervention effect estimate. These are compared to Jeffreys [-@jeffreysTheoryProbability1998] scale regarding evidence *against* (i.e., 0 to 0.5 = weak evidence; 0.5 to 1 = substantial evidence; 1 to 1.5 = strong evidence; 1.5 to 2 = very strong evidence; 2 or greater = decisive evidence). Thus, a positive log10(BF) value indicated that, compared to the prior distribution (meaning the estimates of Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011]), there was now greater evidence against the standardised mean difference for which the log10(BF) was calculated.

Lastly, as a supplemental analysis, we produced cumulative versions of our main model over each year since the publication of the meta-analysis from Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011]. The first model started with the prior distribution noted above for our main model and only included effects from studies reported in 2011. Then we took the posterior distribution for the intervention effect from this model as the prior for the next model which only included effects from studies reported in 2012. This was continued through each year up to the latest included studies. We then plotted the cumulative updating of the intervention effect based on the addition of each years newly reported studies. Note, for each of these models we employed four Monte Carlo Markov Chains each with 2000 warmup and 6000 sampling iterations given the focus was on presenting the updated estimates and to reduce the time required for cumulative models to be fit.

# Results

## Systematic review

TO ADD

## Main model
```{r}
targets::tar_load(main_model)
targets::tar_load(tidy_main_model)
targets::tar_load(main_model_logBF_curve)

```

The main model included `r length(unique(main_model$data$effect))` effects nested in `r length(unique(main_model$data$group))` groups nested in `r length(unique(main_model$data$experiment))` experiments nested in `r length(unique(main_model$data$study))` studies. The overall mean and interval estimate for the standardised mean difference for self-talk interventions was `r round(tidy_main_model$estimate[1],2)` [95% quantile interval: `r round(tidy_main_model$conf.low[1],2)`, `r round(tidy_main_model$conf.high[1],2)`]. This was very similar to the estimate of overall effect in Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011]. Heterogeneity ($\tau$) at the study level was also similar to that reported by Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011], though as noted it is not clear what level theirs pertained to exactly. At the study level $\tau$ = `r round(tidy_main_model$estimate[2],2)` [95% quantile interval: `r round(tidy_main_model$conf.low[2],2)`, `r round(tidy_main_model$conf.high[2],2)`], at the experiment level $\tau=$`r round(tidy_main_model$estimate[3],2)` [95% quantile interval: `r round(tidy_main_model$conf.low[3],2)`, `r round(tidy_main_model$conf.high[3],2)`], at the group level $\tau$ = `r round(tidy_main_model$estimate[4],2)` [95% quantile interval: `r round(tidy_main_model$conf.low[4],2)`, `r round(tidy_main_model$conf.high[4],2)`], and at the effect level $\tau$ = `r round(tidy_main_model$estimate[5],2)` [95% quantile interval: `r round(tidy_main_model$conf.low[5],2)`, `r round(tidy_main_model$conf.high[5],2)`]. An ordered forest plot of study level estimates is shown in @fig-main-model panel (A), and the posterior pooled estimate for the overall effect compared with the prior is shown in panel (B).

```{r}
#| label: fig-main-model 
#| fig-width: 9.375
#| fig-height: 16.6625
#| fig-cap: Panel (A) shows and ordered forest plot with study level posterior probability distributions, mean and 95% quantile intervals, individual effects (ticks), and the 95% prediction interval (grey band). Panel (B) shows the prior and posterior distributions for the overall pooled estimates. Panel (C) shows log10(BF) calculated against each each point effect size from 0 to 1 indicating whether there was greater evidence against them after updating the prior to the posterior (i.e., after the introduction of new evidence) and shows qualitative thresholds for interpretation based on Jeffreys scale.

targets::tar_load(main_model_forest_plot)
targets::tar_load(main_model_update_plot)
targets::tar_load(BF_curve_main_model_plot)

  # Combine plots
  (main_model_forest_plot / main_model_update_plot / BF_curve_main_model_plot) +
    plot_layout(heights = c(2, 1,1)) +
    plot_annotation(tag_levels = "A")

```

# References

### 2023-11-25 pre_print_manuscript.qmd
All models now finalised, preprint final

---
articletitle: |
  Self-talk interventions and sport/motor performance: An updated systematic review and Bayesian meta-analysis
format: 
  sportrxiv-pdf:
    include-in-header:
      text: |
       \usepackage[font=scriptsize]{caption}
       \usepackage{lscape}
        \newcommand{\blandscape}{\begin{landscape}}
        \newcommand{\elandscape}{\end{landscape}}
author:
  - name: Hannah Corcoran
    affiliations:
      - ref: 1
  - name: James Steele
    affiliations:
      - ref: 1
    orcid: 0000-0002-8003-0757
    corresponding: true
    email: james.steele@solent.ac.uk
affiliations:
      - id: 1
        name: Department of Sport and Health, Solent University, UK
abstract: |
  Self-talk has been researched as an aspect of mental preparation for performance in sports and other motor tasks since the late 1980s. In 2011 Hatzigeorgiadis and colleagues systematically reviewed and meta-analysed three decades of self-talk intervention research including 32 studies. Yet, despite the general proliferation of meta-analyses, this topic has not been meta-analysed in the decade since their review which, at least for the main effect, provided a reasonably precise standardised mean difference estimate (0.48 [95% confidence interval: 0.38, 0.58]). Several further studies on self-talk interventions have been conducted in that time and it is of interest to explore what additional evidence they offer regarding the effects of self-talk interventions on sport/motor performance. Bayesian approaches are well positioned to explore how additional evidence changes our understanding of an effect; to see whether it has changed in sign, magnitude, or precision, or whether further research has largely been a ‘waste’. Therefore, our aim was to conduct an updated systematic review and Bayesian meta-analysis replicating the search, inclusion, and models of Hatzigeorgiadis et al. Informative priors were taken directly from Hatzigeorgiadis et al. A total of 34 studies providing 128 effects nested in 64 groups across experiments 42 were included in the final updated meta-analysis representing data from 18761 participants. The overall posterior pooled estimate for the standardised mean difference was almost exactly the same as the prior: 0.47 [95% quantile interval: 0.39, 0.56]. Bayes factors were calculated for a range of effect sizes and indicated that the included studies largely reflected ‘Weak’ evidence against effects ranging from 0.30 to 0.59, and only provided ‘Decisive’ evidence or greater against more extreme effects: either very small (i.e., <0.02) or large (i.e., >0.81). Results were largely similar for all moderator analyses which were updated too; either providing relatively weak evidence against effects found in the previous meta-analysis or evidence suggesting smaller effects for certain moderators. The findings of our updated Bayesian meta-analyses reiterate the positive effect of self-talk interventions on sport/motor performance. However, they also suggest that cumulatively the past decade and more of research has done little to further our understanding of these effects. Considering the limited resources and time for conducting research, it may be worth moving onto to other more pertinent questions regarding psychological constructs impact upon sport/motor performance.
license-type: ccby # change if neccessary
# year: 2025 # defaults to current year
keywords: [psychological intervention, cumulative evidence, research waste] # optional
# optional link to Supplementary Material:
suppl-link: https://osf.io/dqwh5/ 
reference-section-title: References
printnote: "PREPRINT - NOT PEER REVIEWED" # if post print, include "POSTPRINT" then link to the published article
bibliography: references.bib  
pdf-engine: xelatex
execute: 
  echo: false
  message: false
  warning: false
---

```{r}
library(patchwork)
library(tidyverse)
library(grid)
library(kableExtra)
```

# Introduction

Self-talk has a long history of philosophical, theoretical, and empirical work [@geurtsMakingSenseSelf2018; @brinthauptSelftalkResearchChallenges2023; @latinjakSelfTalkInterdisciplinaryReview2023].
One area in which self-talk remains a popular topic of research up to this day is in the sport sciences [@vanraalteSelftalkReviewSportspecific2016; @hardyReflectionsMaturingResearch2018; @latinjakSelfTalkInterdisciplinaryReview2023].
Sport psychology as a broad field has focused on the theorising of psychological constructs that might impact upon performance, and the subsequent experimental testing of theoretically informed interventions to address these constructs.
For example, a recent umbrella review identified thirty meta-analyses exploring the effects of different sport psychology constructs upon performance, thirteen of them examining the effects of interventions, finding an overall standardised mean difference (SMD) for positive constructs of 0.51 \[95% confidence interval: 0.42, 0.58\] [@lochbaumSportPsychologyPerformance2022].
Only one meta-analysis explored the effects of self-talk interventions; Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011].

The meta-analysis by Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011] included a total of 32 studies and 62 effect size estimates revealing an overall SMD estimate of 0.48 \[95% confidence interval: 0.38, 0.58\] and also explored the effects of various moderators of the effectiveness of self-talk interventions.
Around the time that Hatzigeorgiadis et al. conducted their meta-analysis the quantitative synthesis of research findings using meta-analytic tools was still relatively new in the sport sciences [@haggerMetaanalysisSportExercise2006].
However in the last decade, particularly in sport psychology, there has been an increasing reliance on meta-analyses [@lochbaumSportPsychologyPerformance2022; @haggerMetaanalysis2022].
Yet, despite the general proliferation of meta-analyses in the past decade, the effects of self-talk interventions has not been re-evaluated by means of such quantitative synthesis since 2011, when Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011] completed their work.
During this period though, empirical research regarding self-talk interventions for sport and motor performance has burgeoned leading some to reflect on the field as "maturing" post-2011 [@hardyReflectionsMaturingResearch2018].

Whilst self-talk as a field may have matured in the post-2011 years with theoretical advancements in conceptualisation of the construct and mediators of its effects on performance, efforts to improve operationalisation/measurement, and efforts to improve methodology used in studying self-talk [@brinthauptSelftalkResearchChallenges2023; @geurtsMakingSenseSelf2018; @hardyReflectionsMaturingResearch2018; @latinjakSelfTalkInterdisciplinaryReview2023; @vanraalteSelftalkReviewSportspecific2016; @latinjakSpeakingClearly102019], it could be argued that understanding of the effectiveness of self-talk *interventions* (referred to in modern literature as 'strategic' self-talk; @latinjakSpeakingClearly102019) was "mature" prior to 2011.
The effect estimate from the meta-analysis of Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011] was already fairly precise, and indeed so to were many of the moderator estimates.
Several further studies on self-talk interventions have been conducted since 2011 and it is a reasonable question to ask, given the limited time and resource for conducting research in the field of sport science, to whether and to what extent these have advanced our understanding or whether they have largely contributed to "research waste".

Two questions that should (though arguably are not often enough particularly in sport science) be asked by researchers when planning a study of an experimental intervention is "what is the likelihood that the experimental intervention is superior to the control intervention given the evidence accumulated so far?", and "what is the likelihood that a new trial, given some design parameters and previous evidence, will demonstrate the superiority of the experimental intervention?".
The key here is to consider the *cumulative* nature of evidence provided by research.
Cumulative meta-analyses were proposed in the early 1990s and have since then been argued to be key tools to answering these questions and considering whether or not additional research is a worthwhile use of resources [@clarkeAccumulatingResearchSystematic2014; @graingerEvidenceSynthesisTackling2020]. Bayesian approaches are well positioned to tackle this [@biauUsingBayesianStatistics2017].
Within Bayesian statistical inference a prior probability distribution regarding the effect of interest is *updated* after the introduction of new evidence to a posterior probability distribution given Bayes theorem.

Given that there has not been, to the best of our knowledge, a meta-analytic synthesis of the effects of self-talk interventions effects upon sport/motor performance since Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011] it is unclear the extent to which the past decade and more of research has advanced our understanding or potentially contributed to “research waste”.
Therefore, our aim was to conduct an updated systematic review and Bayesian meta-analysis replicating the search, inclusion, and models of Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011].

# Method

The method for this systematic review and meta-analysis was replicated with slight adaptation from Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011]. We limited our searches to the date range of November 2011 to November 2023 to avoid double counting as we used the estimates from Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011] as informative priors in our meta-analyses which contain the information from studies prior to November 2011.

## Criteria for including studies

Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011] did not explicitly state a process or strategy to formulating their research question and search methods.
However, we assumed that the PICO (Participants, Intervention, Comparator and Outcome) framework was implicitly used and, with that assumption, we adopted the following inclusion criteria based on their description.
Participants were healthy and of any performance level.
The intervention was instruction to engage in positive self-talk[^1].
The comparator was no self-talk or unrelated self-talk.
Outcomes were sport or motor task performance.
We included both between and within group experimental designs with either pre-post, or post-only measurements of performance as well as within group pre-post trials.

[^1]: Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011] stated: *"As our purpose was to test the effectiveness of interventions aiming to improve performance, groups or conditions using negative ... or inappropriate self-talk ... were excluded. In addition, groups or conditions using assisted self-talk ... were also excluded as assisted self-talk involves the use of external aids, such as headphones, and was not considered pure self-talk intervention."*

## Search strategy

Studies were obtained through electronic journal searches and review articles along with personal records and communication.
The following databases -- Sport Discus, PsycINFO, PsycARTICLES and Medline -- were selected through the EBSCO database to search for the keywords.
The SCOPUS database, used by Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011], was not used as it was not accessible through Solent University[^2].
These keywords were searched in the format of, with the application of the Boolean commands, (self-talk OR self-instruction OR self-statements OR self-verbalizations OR verbal cues OR stimulus cueing OR thought content instructions) AND (sport OR performance OR motor performance OR task performance).
The studies were all peer-reviewed, full text and published in English language journals.
The search was limited to the date range of November 2011-November 2023.
An initial search took place from October 2022-November 2022 as this project was completed as part of the lead authors undergraduate thesis.
We subsequently updated the search from November 2022-November 2023 prior to preparing this manuscript for publication.

[^2]: Though we feel fairly confident, given the number of studies identified and the findings of our models reported below, that any missed studies would be unlikely to qualitatively impact the overall findings and conclusions of this work.

## Data extraction

The data extracted from the studies were for all positive self-talk intervention groups/conditions and for control comparison designs for the relevant comparator group/condition.
Pre and/or post intervention and comparator, means, sample sizes and either standard deviation, standard errors, variances or confidence intervals were extracted in order to calculate the effect sizes. Also, in order to update the moderator analyses conducted by Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011] we also coded each effect size for motor demands (fine or gross), participant group (non-athletes[^3] vs beginner athletes vs experienced athletes), self-talk content[^4] (motivational vs instructional), the combination of motor demands and self-talk content to examine the matching hypothesis (motivational/gross vs motivational/fine vs instructional/gross vs instructional/fine), the task novelty (novel vs learned), cue selection and overtness selection (self-selected vs assigned), if the study was acute or involved a chronic training intervention (no-training vs training), and the study design[^5] (pre/post - experimental/control vs pre/post - experimental vs post - experimental/control). The data extracted was imported into a spreadsheet in excel as a csv.

[^3]: Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011] referred to their non-athlete group as "students" presumably because in all studies they included it was the case that all non-athletes were from student populations. As this was not necessarily the case for studies included in our updated analyses we refer to them as "non-athletes".

[^4]: Some studies we included in our updated analysis used combined instructional and motivational, and also other forms of self-talk content e.g., rational. We coded these new categories also.

[^5]: Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011] included studies with multiple baseline measures but we did not identify any studies meeting this design in our updated analysis.

## Statistical analysis

Statistical analysis of the data extracted was performed in R, (v 4.2.2; R Core Team, https://www.r-project.org/) and RStudio (v 2023.06.1; Posit, https://posit.co/).
As noted, we adopted a Bayesian approach to the present meta-analysis.
Specifically, we adopted informative priors from the models reported by Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011] and replicated their analyses using appropriate model specifications given the structure of the data.
All code utilised for data preparation and analyses are available in either the Open Science Framework page for this project [https://osf.io/dqwh5/](https://osf.io/dqwh5/) or the corresponding GitHub repository [https://github.com/jamessteeleii/self_talk_meta_analysis_update](https://github.com/jamessteeleii/self_talk_meta_analysis_update).
The `renv` package [@usheyRenvProjectEnvironments2023] was used for package version reproducibility and a function based analysis pipeline using the `targets` package [@landauTargetsDynamicFunctionOriented2023] was employed (the analysis pipeline can be viewed by downloading the R Project and running the function `targets::tar_visnetwork()`). Standardised effect sizes were all calculated using the `metafor` package [@viechtbauerMetaforMetaAnalysisPackage2023]. The main package `brms` [@burknerBrmsBayesianRegression2023] was used in fitting all the Bayesian meta-analysis models. Prior and posterior draws were taken using `tidybayes` [@kayTidybayesTidyData2023] and `marginaleffects` [@arel-bundockMarginaleffectsPredictionsComparisons2023] packages. Bayes factors were calculated using the `bayestestR` package [@makowskiBayestestRUnderstandDescribe2023]. All visualisations were created using `ggplot2` [@wickhamGgplot2CreateElegant2023], `tidybayes`, and the `patchwork` [@pedersenPatchworkComposerPlots2023] packages.

Effect sizes were calculated as SMDs dependent on the design of the study. Firstly, all were signed such that a positive effect indicated that the self-talk intervention was favoured. For studies utilising a pretest-posttest-control comparison design we calculated the SMD between groups/conditions using the pooled pre-test standard deviation as per Morris [@morrisEstimatingEffectSizes2008]. For post-test only control comparison designs we calculated the SMD between groups/conditions based upon the pooled post-test standard deviation. Lastly, for single arm within group pre-post (or control-intervention) designs we calculated the SMD from pre- to post-intervention using the pre-test standard deviation. Effect sizes were all calculated using the `escalc` function from the `metafor` package.

Though it was not entirely clear from the reporting in the meta-analysis of Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011], they noted including a greater number of effect sizes than individual studies. As such, it was likely that their data had a hierarchical structure with effects nested within studies whether they explicitly applied a hierarchical model to it or not. The studies we identified and included also had hierarchical structure whereby we had effects nested within groups (for example when there were multiple self-talk interventions examined) nested within experiments (for example when a study reported on multiple experiments using different samples and/or designs) nested within studies. As such, we used multilevel mixed effects meta-analyses with nested random intercepts for effects, groups, experiments, and studies. Effects were all weighted by the inverse sampling variance. A main model was produced which included all effects and was intended to update the overall model from Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011], whereby their overall estimate reflected the fixed model intercept. In addition, we produced models for each of the aforementioned categorical moderators where we excluded the model intercept in order to set priors for each category directly based on the estimates and their precision reported[^6] by Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011].

[^6]: It is not clear exactly from the reporting by Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011] as to whether their moderator analyses involved fitting their models to datasets constructed separately, whereby they were filtered to only include the relevant category for the moderator, or if they were fit together including all categories. We opted to fit them together for parsimony here.

Priors for each model were set informatively for the intervention effects, and were set to be weakly regularising for the heterogeneity (i.e., $\tau$) at all levels of the model[^7]. Intervention effects were set with priors based on the effect estimates from Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011], reported in their Table 1, using a $t$-distribution ($t(k,\mu,\sigma)$) with $k-2$ degrees of freedom [@higginsReevaluationRandomeffectsMetaanalysis2009]. We assumed $k$ to be the number of effects included in the models reported by Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011]. For the main model the prior for the intervention effect was set directly on the model intercept i.e., $t(60, 0.48, 0.05)$. For the moderator models, as noted, we removed the model intercept allowing us to set the priors directly on each category for each moderator based on the estimates from Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011] Table 1. In cases where moderators had new categories introduced in the newer studies, included in our analyses, we used $\mu=0.48$ and $\sigma=0.05$ taken from the overall estimate of Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011] and applied degrees of freedom $k=3$ to be more conservative and allow greater mass in the tails of the prior distribution for these categories. In all models the heterogeneity priors at each level were set using the default weakly regularising prior in `brms`; a half-$t$-distribution with $\mu=0$, $\sigma=2.5$, and $k=3$. This constrained the prior to only allow positively signed values for $\tau$ though over a wide range of possible values.

[^7]: Though Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011] report on $\tau$ it is not clear what level this applies to (and as noted it is not clear if they employed a hierachical model) and they do not report any interval estimate for this making it difficult to specify an informative prior distribution. As such, and given suggestions regarding heterogeneity priors [@williamsBayesianMetaAnalysisWeakly2018; @roverWeaklyInformativePrior2021], we opted for a weakly regularising distribution at all levels.

As we were interested in determining how much the new evidence produced since Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011] had updated our understanding of the effects of self-talk interventions, we fit each model using four Monte Carlo Markov Chains each with 4000 warmup and 40000 sampling iterations. This was in order to obtain precise Bayes Factors using the Savage-Dickey ratio [@gronauBridgesamplingPackageEstimating2020].

From each model we obtained draws from the posterior distributions for the intervention effects (i.e., the expectation of the value of the parameters posterior probability distribution) in order to present probability density functions visually, and also to calculate mean and 95% quantile intervals (i.e., 'credible' or 'compatibility' intervals) for each estimate. These gave us the most probably value of the parameter in addition to the range from 2.5% to 97.5% percentiles. The same was done drawing samples from the prior distributions only in order to present both distributions visually for comparison of the prior to posterior updating. For the main model draws were taken at the study level and an ordered forest plot produced showing each studies posterior distribution along with mean and 95% quantile intervals. We also calculated the 95% prediction intervals providing the range over which we can expect 95% of future effect estimates to fall and present each individual effect size on the forest plot. To compliment the visual inspection of prior to posterior updating we also present log10 Bayes Factors (log10[BF]) calculated *against* 100 effects ranging from a SMD of 0 through to 1 and plot these log10(BF) curves for each model intervention effect estimate i.e.., the Savage-Dickey ratio was calculated for each of 100 point effects in the interval (0,1) equally spaced. These were compared to Jeffreys [-@jeffreysTheoryProbability1998] scale regarding evidence *against* (i.e., 0 to 0.5 = weak evidence; 0.5 to 1 = substantial evidence; 1 to 1.5 = strong evidence; 1.5 to 2 = very strong evidence; 2 or greater = decisive evidence). Thus, a positive log10(BF) value indicated that, compared to the prior distribution (meaning the estimates of Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011]), there was now greater evidence against the SMD for which the log10(BF) was calculated. A loess smooth was then applied to these 100 values.

Lastly, as a supplemental analysis, we produced cumulative versions of our main model over each year since the publication of the meta-analysis from Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011]. The first model started with the prior distribution noted above for our main model and only included effects from studies reported in 2011. Then we took the posterior distribution for the intervention effect from this model and used it as the prior for the next model which only included effects from studies reported in 2012. This was continued through each year up to the latest included studies. We then plotted the cumulative updating of the intervention effect based on the addition of each years newly reported studies. Note, for each of these models we employed four Monte Carlo Markov Chains each with 2000 warmup and 6000 sampling iterations given the focus was on presenting the updated estimates and to reduce the time required for cumulative models to be fit.

# Results
```{r}
targets::tar_load(data)
sample_sizes_st <- data %>%
  select(group, n_st) %>%
  group_by(group) %>%
  summarise(n_st = max(n_st)) %>%
  summarise(`All ST` = sum(n_st),
            `Minumum ST` = min(n_st),
            `Median ST` = median(n_st),
            `Maximum ST` = max(n_st)
            ) %>%
  pivot_longer(1:4, names_to = "Group", values_to = "Sample Size")
sample_sizes_con <- data %>%
  select(study, n_con) %>%
  group_by(study) %>%
  summarise(n_con = max(n_con)) %>%
  summarise(`All CON` = sum(n_con, na.rm =TRUE), 
            `Minumum CON` = min(n_con, na.rm =TRUE),
            `Median CON` = median(n_con, na.rm =TRUE),
            `Maximum CON` = max(n_con, na.rm =TRUE)) %>%
  pivot_longer(1:4, names_to = "Group", values_to = "Sample Size")
sample_sizes <- bind_rows(sample_sizes_st, sample_sizes_con)

```

We identified `r length(unique(data$study))` new studies published from November 2011 up to November 2023 [@abdoliCloserLookHow2018; @hatzigeorgiadisSelftalkCompetitiveSport2014; @panteliAcquisitionLongJump2013; @hongEmpiricalTestSelfTalk2020; @hatzigeorgiadisBeatHeatEffects2018; @laneBriefOnlineTraining2016; @latinjakCombiningSelfTalk2011; @gregersenCounteringConsequencesEgo2017; @mccormickEffectsMotivationalSelfTalk2018; @galanisEffectsStrategicSelftalk2022; @benekaEffectsInstructionalMotivational2013; @wallaceEffectsMotivationalSelfTalk2017; @walterEffectsSelfTalkTraining2019; @galanisLabFieldEffects2018; @youngHowMuchDoes2023; @raalteWillUseDeclarative2018; @liuInteractiveEffectsMotor2022; @dematosMotivationalSelftalkImproves2021; @barwoodImprovement10kmTimetrial2015; @cabralMotivationalSelftalkMitigates2023; @changSelftalkSoftballPerformance2014; @raalteSelfTalkSCUBADiving2018; @galanisStrategicSelfTalkAssists2022; @blanchfieldTalkingYourselfOut2014; @turnerTeeingSuccessEffects2018; @naderiradEffectInstructionalMotivational2023; @zetouEffectSelftalkTaekwondo2014; @zourbanosEffectsSelftalkIntervention2013; @osmanEffectsInstructionalMotivational2022; @kolovelonisEffectsInstructionalMotivational2011; @sarigEffectsInstructionalSelfTalk2023; @marshallEffectsSelfTalkCues2016; @zourbanosEffectsSelfTalkDominant2013; @galanisEffectsStrategicSelftalk2023; @weinbergInfluenceSelftalkIntervention2012]. These included `r length(unique(data$effect))` effects nested in `r length(unique(data$group))` groups nested in `r length(unique(data$experiment))` experiments. The included studies contained a total of `r sample_sizes[1,2] + sample_sizes[5,2]` participants (see @tbl-sample-sizes). We included all but one study [@marshallEffectsSelfTalkCues2016], due to the sample size for groups in this study being too small to calculate SMDs (i.e., n = 2 to 3), in our analyses.

```{r}
#| label: tbl-sample-sizes 
#| tbl-cap-location: "top"
#| tbl-cap: Sample sizes for self-talk intervention and non-intervention control groups.
knitr::kable(
  sample_sizes
  ) %>%
  pack_rows("Self-talk", 1, 4) %>%
  pack_rows("Control", 5, 8) %>%
  footnote(general = c("ST = self-talk", "CON = non-intervention control")
           ) %>%
  row_spec(0, bold = TRUE) %>%
  kable_classic(full_width = FALSE) 
```

## Main model
```{r}
targets::tar_load(main_model)
targets::tar_load(tidy_main_model)
targets::tar_load(main_model_logBF_curve)
```

The overall mean and interval estimate for the SMD for self-talk interventions was `r round(tidy_main_model$estimate[1],2)` [95% quantile interval: `r round(tidy_main_model$conf.low[1],2)`, `r round(tidy_main_model$conf.high[1],2)`]. This was very similar to the estimate of overall effect in Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011] of 0.48 [95% confidence interval: 0.38, 0.58]. Heterogeneity ($\tau$) at the study level was also similar to that reported by Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011], though as noted it is not clear what level theirs pertained to exactly. At the study level $\tau$ = `r round(tidy_main_model$estimate[2],2)` [95% quantile interval: `r round(tidy_main_model$conf.low[2],2)`, `r round(tidy_main_model$conf.high[2],2)`], at the experiment level $\tau$ = `r round(tidy_main_model$estimate[3],2)` [95% quantile interval: `r round(tidy_main_model$conf.low[3],2)`, `r round(tidy_main_model$conf.high[3],2)`], at the group level $\tau$ = `r round(tidy_main_model$estimate[4],2)` [95% quantile interval: `r round(tidy_main_model$conf.low[4],2)`, `r round(tidy_main_model$conf.high[4],2)`], and at the effect level $\tau$ = `r round(tidy_main_model$estimate[5],2)` [95% quantile interval: `r round(tidy_main_model$conf.low[5],2)`, `r round(tidy_main_model$conf.high[5],2)`]. An ordered forest plot of study level estimates is shown in @fig-main-model panel (A), and the posterior pooled estimate for the overall SMD effect compared with the prior is shown in panel (B).

```{r}
#| label: fig-main-model 
#| fig-width: 7.5
#| fig-height: 13.33
#| fig-cap: Panel (A) shows and ordered forest plot of study level effects. Panel (B) shows the prior and posterior distributions for the overall pooled estimates. Panel (C) shows log10(BF) calculated against each each point effect size from 0 to 1.
targets::tar_load(main_model_forest_plot)
targets::tar_load(main_model_update_plot)
targets::tar_load(BF_curve_main_model_plot)

  # Combine plots
  (main_model_forest_plot / main_model_update_plot / BF_curve_main_model_plot) +
    plot_layout(heights = c(2, 1,1)) +
    plot_annotation(tag_levels = "A")
```

```{r}
main_model_logBF_curve <-  main_model_logBF_curve %>%
  mutate(log10BF = log10(exp(BF.log_BF)))
log10BF_loess <- loess(log10BF ~ effect,
                       data = main_model_logBF_curve)
Jeffreys_scales <- main_model_logBF_curve %>%
  mutate(log10BF_pred = predict(log10BF_loess)) %>%
  mutate(Jeffreys_scale = case_when(
    log10BF_pred <= 0.5 ~ "Weak",
    log10BF_pred <= 1 ~ "Substantial",
    log10BF_pred <= 1.5 ~ "Strong",
    log10BF_pred <= 2.0 ~ "Very Strong",
    log10BF_pred > 2.0  ~ "Decisive"
  )) %>%
  mutate(log10BF_diff = log10BF_pred - lag(log10BF_pred, default = log10BF_pred[1]),
         sign = case_when(
           log10BF_diff < 0 ~ "Negative",
           log10BF_diff >= 0 ~ "Positive"
         )) %>%
  slice(2:100) %>%
  group_by(Jeffreys_scale, sign) %>%
  select(Jeffreys_scale, sign, effect) %>%
  summarise(min_effect = min(effect),
            max_effect = max(effect)) 
```

Considering the log10(BF) values calculated against the range of SMD effect sizes from 0 to 1 compared to Jeffreys scale (see @fig-main-model panel [C]), the newly added evidence suggested that there was only "Decisive" evidence updating the prior against effect sizes ranging from 0 to `r round(Jeffreys_scales$max_effect[1],2)` and from `r round(Jeffreys_scales$min_effect[2],2)` to `r round(Jeffreys_scales$max_effect[2],2)`. "Very Strong" evidence was indicated against effect sizes ranging from `r round(Jeffreys_scales$min_effect[7],2)` to `r round(Jeffreys_scales$max_effect[7],2)` and from `r round(Jeffreys_scales$min_effect[8],2)` to `r round(Jeffreys_scales$max_effect[8],2)`. "Strong" evidence was indicated against effect sizes ranging from `r round(Jeffreys_scales$min_effect[3],2)` to `r round(Jeffreys_scales$max_effect[3],2)` and from `r round(Jeffreys_scales$min_effect[4],2)` to `r round(Jeffreys_scales$max_effect[4],2)`. "Substantial" evidence was indicated against effect sizes ranging from `r round(Jeffreys_scales$min_effect[5],2)` to `r round(Jeffreys_scales$max_effect[5],2)` and from `r round(Jeffreys_scales$min_effect[6],2)` to `r round(Jeffreys_scales$max_effect[6],2)`. "Weak" or "Negative" evidence was indicated against effect sizes ranging from `r round(Jeffreys_scales$min_effect[9],2)` to `r round(Jeffreys_scales$max_effect[10],2)`. This suggested that the newly acquired evidence generally decreased our belief in effect sizes that would likely already have been ruled out by the analysis of Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011]. The supplementary cumulative models further supported this. They showed little change in either point or interval estimates for the SMD from year to year as a result of new studies during the period of November 2011 to November 2023 (see [https://osf.io/9qrh5](cumulative model plot)).

## Moderators
```{r}
targets::tar_load(tidy_motor_demands_model)
targets::tar_load(tidy_selftalk_content_model)
targets::tar_load(tidy_matching_model)
targets::tar_load(tidy_task_novelty_model)
targets::tar_load(tidy_training_model)
```

For most of the moderators explored there was similarly little impact upon posterior estimates for the SMD from the introduction of new evidence accumulated since the analysis of Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011]. @fig-moderators-models shows each of the prior and posterior distributions for the moderators estimates and the log10(BF) results for each are available in the supplementary materials (see 'plots' folder [https://osf.io/dqwh5/](https://osf.io/dqwh5/)). Where there were more substantial changes from prior to posterior these typically revealed a reduction in the magnitude of SMD estimate e.g., for fine tasks in the motor demands model (Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011] = 0.67 [95% confidence interval: 0.53, 0.82]; posterior pooled estimate = `r round(tidy_motor_demands_model$estimate[1],2)` [95% quantile interval: `r round(tidy_motor_demands_model$conf.low[1],2)`, `r round(tidy_motor_demands_model$conf.high[1],2)`]), instructional in the self-talk content model (Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011] = 0.55 [95% confidence interval: 0.40, 0.70]; posterior pooled estimate = `r round(tidy_selftalk_content_model$estimate[2],2)` [95% quantile interval: `r round(tidy_selftalk_content_model$conf.low[2],2)`, `r round(tidy_selftalk_content_model$conf.high[2],2)`]), instructional/fine in the matching hypothesis model (Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011] = 0.83 [95% confidence interval: 0.64, 1.02]; posterior pooled estimate = `r round(tidy_matching_model$estimate[1],2)` [95% quantile interval: `r round(tidy_matching_model$conf.low[1],2)`, `r round(tidy_matching_model$conf.high[1],2)`]), for novel tasks in the task novelty model (Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011] = 0.73 [95% confidence interval: 0.47, 1.00]; posterior pooled estimate = `r round(tidy_task_novelty_model$estimate[2],2)` [95% quantile interval: `r round(tidy_task_novelty_model$conf.low[2],2)`, `r round(tidy_task_novelty_model$conf.high[2],2)`]), and for training interventions in the training model (Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011] = 0.80 [95% confidence interval: 0.57, 1.03]; posterior pooled estimate = `r round(tidy_training_model$estimate[2],2)` [95% quantile interval: `r round(tidy_training_model$conf.low[2],2)`, `r round(tidy_training_model$conf.high[2],2)`]).

\newpage

\blandscape

```{r}
#| label: fig-moderators-models 
#| fig-width: 21
#| fig-height: 12
#| fig-cap: Prior and posterior distributions for each moderator explored; Panel (A) motor demands, (B) participant population, (C) self-talk content, (D) matching hypothesis, (E) task novelty, (F) cue selection, (G) overtness selection, (H) training intervention or not, and (I) study design.
targets::tar_load(motor_demands_model_plot) 
targets::tar_load(participant_group_model_plot) 
targets::tar_load(selftalk_content_model_plot)
targets::tar_load(matching_model_plot) 
targets::tar_load(task_novelty_model_plot) 
targets::tar_load(cue_selection_model_plot)
targets::tar_load(overtness_selection_model_plot) 
targets::tar_load(training_model_plot) 
targets::tar_load(study_design_model_plot)

((motor_demands_model_plot / participant_group_model_plot / selftalk_content_model_plot) |
      (matching_model_plot / task_novelty_model_plot / cue_selection_model_plot) |
      (overtness_selection_model_plot / training_model_plot / study_design_model_plot) ) +
    plot_annotation(tag_levels = "A",
                    title = "Updated Posterior Moderators Estimates",
                    subtitle = "Prior and posterior distributions for pooled estimates, individual effects (ticks), and mean and 95% quantile interval for posterior (text label)") +
    plot_layout(guides = "collect") & theme(legend.position = 'bottom')

```
\elandscape

# Discussion
The aim of this systematic review and meta-analysis was to update, using Bayesian methods, the results of Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011]. Since that time a further `r length(unique(data$study))` new studies had been published which were identified in our searches and we could include all but one in our analysis. Our finding suggested that the cumulative impact of this research over the last decade and more has done little to further our understanding of the effects of self-talk interventions. The results showed that the overall pooled estimate from the meta-analysis was a SMD of `r round(tidy_main_model$estimate[1],2)` [95% quantile interval: `r round(tidy_main_model$conf.low[1],2)`, `r round(tidy_main_model$conf.high[1],2)`]. This was very similar to the previous estimate of overall effect in Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011] of 0.48 [95% confidence interval: 0.38, 0.58]. The Bayes factors calculated indicated that the included studies largely reflected “Weak”, or even very mildly "Negative", evidence against effects ranging from `r round(Jeffreys_scales$min_effect[9],2)` to `r round(Jeffreys_scales$max_effect[10],2)`, and only provided "Decisive" evidence updating the prior against effect sizes ranging from 0 to `r round(Jeffreys_scales$max_effect[1],2)` and from `r round(Jeffreys_scales$min_effect[2],2)` to `r round(Jeffreys_scales$max_effect[2],2)`.

```{r}
lochbaum <- c(0.57,1.35,0.65,0.32,0.24,0.51,0.51,0.48,0.72,1,0.22,0.49,0.48,0.47,0.68,0.28,0.2,0.44,0.32,0.34,0.84,0.38,0.38,0.38,0.74,0.72,0.82,0.72,0.15,0.47,0.31,0.49,0.49,0.65)
# Prediction interval
targets::tar_load(main_model)
  nd <- data.frame(study = "new", vi = 0)
  pred_int_data <- brms::posterior_predict(
    object = main_model,
    newdata = nd,
    re_formula = NULL,
    allow_new_levels = TRUE,
    sample_new_levels = "gaussian"
  )
  pred_int_data <- tidybayes::median_qi(pred_int_data) %>%
    mutate(label = as.character("Posterior Pooled Estimate"))
```

The findings of our updated Bayesian meta-analyses reiterate the positive effect of self-talk interventions on sport/motor performance on average. Indeed, the estimate reflects the typical effect of other psychological interventions (0.51 \[95% confidence interval: 0.42, 0.58\]) as identified by Lochbaum et al.  [-@lochbaumSportPsychologyPerformance2022] in their umbrella review; though notable they also reported a wide range of overall effect estimates between positively directed interventions/strategies (`r min(lochbaum)` to `r max(lochbaum)`). Reflecting this, Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011] reported $\tau$ = 0.27 (though as noted in footnote[^7] it is not clear which level this pertains to) for the self-talk intervention studies they explored, and our study level estimate was not dissimilar to this ($\tau$ = `r round(tidy_main_model$estimate[2],2)` [95% quantile interval: `r round(tidy_main_model$conf.low[2],2)`, `r round(tidy_main_model$conf.high[2],2)`]). Indeed, our prediction interval ranged from `r round(pred_int_data$ymin,2)` to `r round(pred_int_data$ymax,2)`. Considering this heterogeneity in effects, Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011] previously examined varied theoretically plausible moderators of the effectiveness of self-talk interventions.

Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011] suggested that, under certain task conditions, or the nature of the intervention, or the specific participants, there could possibly be differential effects of self-talk. Their results suggested that, whilst self-talk interventions in general were effective, greater effects were seen for fine motor tasks and the performance of novel tasks. They also found results supportive of the matching hypothesis (i.e., that instructional self-talk as more effective for fine motor tasks than motivational, and that instructional was more effective for fine compared with gross motor tasks). By and large, our moderator analyses reiterated the findings of Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011]. Posterior estimates were largely similar for all moderators which were updated, and Bayes factors suggested that the newer evidence provided relatively weak evidence against the prior effects reported by Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011] or evidence suggesting slightly smaller effects for certain moderators (though qualitative conclusions remained the same).

Despite further supporting the effectiveness of self-talk interventions and the factors that moderate this, our results suggest that cumulatively the past decade and more of research has done little to further our understanding of these effects. Of course, as we noted in the introduction, this lack of change to our beliefs despite the cumulative evidence could be considered as evidence that the production of such evidence is wasteful. The present updated Bayesian meta-analyses makes this quite clear; considering the limited resources and time for conducting research, it may be worth moving onto to other more pertinent questions regarding psychological interventions for sport/motor performance.

It is worth noting though that any conclusions regarding “research waste” are specific to the context explored here: namely, self-talk *interventions*. As explained, the post-2011 years have seen theoretical advancements in conceptualisation of the construct of self-talk [@brinthauptSelftalkResearchChallenges2023; @geurtsMakingSenseSelf2018; @hardyReflectionsMaturingResearch2018; @latinjakSelfTalkInterdisciplinaryReview2023; @vanraalteSelftalkReviewSportspecific2016; @latinjakSpeakingClearly102019]. A key distinction in modern integrative reviews of the construct in relation to sport/motor performance is between “strategic” and “organic” self-talk [@latinjakSpeakingClearly102019]. Latinjak et al. [-@latinjakSpeakingClearly102019] highlights this and note research has focused primarily on the former given it, by definition, can be deliberately employed in a predetermined interventional manner. As such, most research has focused upon the exploration of self-talk *interventions* at the expense of exploring the use of spontaneous or reflexive self-talk that organically occurs as thoughts for the performer addressed to themselves. Latinjak et al. [-@latinjakSpeakingClearly102019] argue that future research on any kinds of self-talk interventions can improve our understanding of the effectiveness of self-talk strategies, we would disagree given the results of our updated analyses. However, we do agree with Latinjak et al. [-@latinjakSpeakingClearly102019] that it may be more appropriate to focus on other research questions regarding self-talk. For example, in their reflection Hardy et al. [-@hardyReflectionsMaturingResearch2018] argue that greater efforts should be made in extending the existing cross-sectional work exploring organic self-talk into longitudinal designs and the use of structural equation modeling (preferably informed by causal directed acyclic graphs). The use of such designs might allow for the exploration of causal effects of organic self-talk strategies which might be less amenable to structured experimental intervention research, as compared to the glut of strategic self-talk intervention studies. These can also support cumulative evidence synthesis through meta-analysis as techniques have been developed to combine and analyse them in such a framework [@cheungMetaAnalysisStructuralEquation2015; @cheungMetaAnalyticStructuralEquation2021].

# Conclusion

This review and meta-analysis has shown that evidence still supports positive self-talk interventions as improving performance since the publication of the meta-analysis by Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011]. Overall, the posterior estimates for both overall and moderator effects in this updated meta-analysis were very similar to the priors from Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011], giving confidence in the overall positive effects. Therefore, coaches and athletes might still consider implementing positive self-talk to maximise performance. However, given that cumulatively the past decade and more of research has done little to further our understanding of self-talk intervention effects specifically it is reasonable to consider it suggestive of “research waste”. Considering the limited resources and time for conducting research, it may be worth moving onto other more pertinent questions regarding psychological constructs impact upon sport/motor performance. In the case of self-talk specifically, future research should look to explore and test the more recent theoretical contributions regarding the conceptualisation of self-talk and, in particular, the use of appropriate designs to test the effects of organic self-talk upon sport/motor performance.

# Contributions

All authors contributed substantially to conception and design, acquisition of data, analysis and interpretation of data, drafting the article or revising it critically for important intellectual content, and provided final approval of the version to be published.

# Funding Information

No funding was received for this project.

# Data and Supplementary Material Accessibility

All extracted data and code utilised for data preparation and analyses are available in either the Open Science Framework page for this project [https://osf.io/dqwh5/](https://osf.io/dqwh5/) or the corresponding GitHub repository [https://github.com/jamessteeleii/self_talk_meta_analysis_update](https://github.com/jamessteeleii/self_talk_meta_analysis_update). Other supplementary analyses and plots are also available there.

### 2023-11-25 R/functions.R

@@ -257,6 +257,10 @@ get_logBF_curve <- function(model) {
   return(BF_curve)
 }
 
+get_tidy_model <- function(model) {
+  tidy(model)
+}
+
 # Setup rstan to run quicker
 rstan_setup <- function() {
   rstan_options(auto_write = TRUE)
@@ -266,9 +270,11 @@ rstan_setup <- function() {
 # Priors
 set_main_prior <- function() {
 
-  # Taken form Hatsigeorgiadis et al. (2011) overall estimate
+  # Taken fromm Hatsigeorgiadis et al. (2011) overall estimate
   main_model_prior <-
-    prior("student_t(3, 0.48, 0.05)", class = "Intercept")
+    c(
+      prior("student_t(60, 0.48, 0.05)", class = "Intercept")
+    )
 }
 
 sample_prior_main_model <- function(data, prior) {
@@ -292,8 +298,8 @@ set_motor_demands_prior <- function() {
   # Note, this model omits the intercept in order to include the priors on the groups directly
   motor_demands_prior <-
     c(
-      prior("student_t(3, 0.67, 0.07)", class = "b", coef = "motor_demandsFine"),
-      prior("student_t(3, 0.26, 0.04)", class = "b", coef = "motor_demandsGross")
+      prior("student_t(35, 0.67, 0.07)", class = "b", coef = "motor_demandsFine"),
+      prior("student_t(25, 0.26, 0.04)", class = "b", coef = "motor_demandsGross")
     )
 }
 
@@ -318,9 +324,9 @@ set_participant_group_prior <- function() {
   # Note, this model omits the intercept in order to include the priors on the groups directly
   participant_group_prior <-
     c(
-      prior("student_t(3, 0.5, 0.08)", class = "b", coef = "participant_groupNonMathletes"),
-      prior("student_t(3, 0.47, 0.08)", class = "b", coef = "participant_groupBeginnerathletes"),
-      prior("student_t(3, 0.38, 0.14)", class = "b", coef = "participant_groupExperiencedathletes")
+      prior("student_t(30, 0.5, 0.08)", class = "b", coef = "participant_groupNonMathletes"),
+      prior("student_t(20, 0.47, 0.08)", class = "b", coef = "participant_groupBeginnerathletes"),
+      prior("student_t(6, 0.38, 0.14)", class = "b", coef = "participant_groupExperiencedathletes")
     )
 }
 
@@ -346,8 +352,8 @@ set_selftalk_content_prior <- function() {
[…]

### 2023-11-25 _targets.R

@@ -22,7 +22,8 @@ tar_option_set(
     "base",
     "furrr",
     "patchwork",
-    "marginaleffects"
+    "marginaleffects",
+    "broom.mixed"
     )
 )
 
@@ -43,7 +44,11 @@ list(
   tar_target(trace_plot_main_model, make_trace_plot(main_model)),
   tar_target(pp_check_main_model, make_pp_check(main_model)),
   tar_target(main_model_logBF_curve, get_logBF_curve(main_model)),
-  tar_target(main_model_plot, plot_main_model(data_effect_sizes, prior_main_model, main_model, main_model_logBF_curve)),
+  tar_target(main_model_forest_plot, plot_main_model_forest(data_effect_sizes, main_model)),
+  tar_target(main_model_update_plot, plot_main_model_update(prior_main_model, main_model)),
+  tar_target(BF_curve_main_model_plot, plot_BF_curve_main_model(main_model_logBF_curve)),
+  tar_target(main_model_plot, plot_panel_main_model(main_model_forest_plot,main_model_update_plot,BF_curve_main_model_plot)),
+  tar_target(tidy_main_model, get_tidy_model(main_model)),
 
   # Fit, check, and plot motor demands model
   tar_target(motor_demands_prior, set_motor_demands_prior()),
@@ -54,6 +59,7 @@ list(
   tar_target(pp_check_motor_demands_model, make_pp_check(motor_demands_model)),
   tar_target(motor_demands_model_plot, plot_motor_demands_model(data_effect_sizes, prior_motor_demands_model, motor_demands_model)),
   tar_target(motor_demands_model_logBF_curve, get_logBF_curve(motor_demands_model)),
+  tar_target(tidy_motor_demands_model, get_tidy_model(motor_demands_model)),
 
   # Fit, check, and plot participant group model
   tar_target(participant_group_prior, set_participant_group_prior()),
@@ -64,6 +70,7 @@ list(
   tar_target(pp_check_participant_group_model, make_pp_check(participant_group_model)),
   tar_target(participant_group_model_plot, plot_participant_group_model(data_effect_sizes, prior_participant_group_model, participant_group_model)),
   tar_target(participant_group_model_logBF_curve, get_logBF_curve(participant_group_model)),
+  tar_target(tidy_participant_group_model, get_tidy_model(participant_group_model)),
 
   # Fit, check, and plot self-talk content model
   tar_target(selftalk_content_prior, set_selftalk_content_prior()),
[…]

### 2023-11-25 diagnostic_plots.qmd
Add diagnostic plots to repo

---
title: "Diagnostic Plots"
subtitle: "Self-talk interventions and sport/motor performance: An updated systematic review and Bayesian meta-analysis"
author: "Hannah Corcoran, James Steele"
format:
  pdf:
    documentclass: report
    toc: false
    number-sections: false
    highlight-style: github
    fig-width: 10
    fig-height: 10
---
# Main Model

## $\hat{R}$

```{r,message=FALSE,warning=FALSE,echo=FALSE}

targets::tar_load(rhat_main_model)

rhat_main_model

```

## Trace plots

```{r,message=FALSE,warning=FALSE,echo=FALSE}

targets::tar_load(trace_plot_main_model)

trace_plot_main_model

```

## Posterior predictive check

```{r,message=FALSE,warning=FALSE,echo=FALSE}

targets::tar_load(pp_check_main_model)

pp_check_main_model

```

# Motor Demands Model

## $\hat{R}$

```{r,message=FALSE,warning=FALSE,echo=FALSE}

targets::tar_load(rhat_motor_demands_model)

rhat_motor_demands_model

```

## Trace plots

```{r,message=FALSE,warning=FALSE,echo=FALSE}

targets::tar_load(trace_plot_motor_demands_model)

trace_plot_motor_demands_model

```

## Posterior predictive check

```{r,message=FALSE,warning=FALSE,echo=FALSE}

targets::tar_load(pp_check_motor_demands_model)

pp_check_motor_demands_model

```

# Participant Group Model

## $\hat{R}$

```{r,message=FALSE,warning=FALSE,echo=FALSE}

targets::tar_load(rhat_participant_group_model)

rhat_participant_group_model

```

## Trace plots

```{r,message=FALSE,warning=FALSE,echo=FALSE}

targets::tar_load(trace_plot_participant_group_model)

trace_plot_participant_group_model

```

## Posterior predictive check

```{r,message=FALSE,warning=FALSE,echo=FALSE}

targets::tar_load(pp_check_participant_group_model)

pp_check_participant_group_model

```

# Self-Talk Content Model

## $\hat{R}$

```{r,message=FALSE,warning=FALSE,echo=FALSE}

targets::tar_load(rhat_selftalk_content_model)

rhat_selftalk_content_model

```

## Trace plots

```{r,message=FALSE,warning=FALSE,echo=FALSE}

targets::tar_load(trace_plot_selftalk_content_model)

trace_plot_selftalk_content_model

```

## Posterior predictive check

```{r,message=FALSE,warning=FALSE,echo=FALSE}

targets::tar_load(pp_check_selftalk_content_model)

pp_check_selftalk_content_model

```

# Matching Model

## $\hat{R}$

```{r,message=FALSE,warning=FALSE,echo=FALSE}

targets::tar_load(rhat_matching_model)

rhat_matching_model

```

## Trace plots

```{r,message=FALSE,warning=FALSE,echo=FALSE}

targets::tar_load(trace_plot_matching_model)

trace_plot_matching_model

```

## Posterior predictive check

```{r,message=FALSE,warning=FALSE,echo=FALSE}

targets::tar_load(pp_check_matching_model)

pp_check_matching_model

```

# task_novelty Model

## $\hat{R}$

```{r,message=FALSE,warning=FALSE,echo=FALSE}

targets::tar_load(rhat_task_novelty_model)

rhat_task_novelty_model

```

## Trace plots

```{r,message=FALSE,warning=FALSE,echo=FALSE}

targets::tar_load(trace_plot_task_novelty_model)

trace_plot_task_novelty_model

```

## Posterior predictive check

```{r,message=FALSE,warning=FALSE,echo=FALSE}

targets::tar_load(pp_check_task_novelty_model)

pp_check_task_novelty_model

```

# Cue Selection Model

## $\hat{R}$

```{r,message=FALSE,warning=FALSE,echo=FALSE}

targets::tar_load(rhat_cue_selection_model)

rhat_cue_selection_model

```

## Trace plots

```{r,message=FALSE,warning=FALSE,echo=FALSE}

targets::tar_load(trace_plot_cue_selection_model)

trace_plot_cue_selection_model

```

## Posterior predictive check

```{r,message=FALSE,warning=FALSE,echo=FALSE}

targets::tar_load(pp_check_cue_selection_model)

pp_check_cue_selection_model

```

# Overtness Selection Model

## $\hat{R}$

```{r,message=FALSE,warning=FALSE,echo=FALSE}

targets::tar_load(rhat_overtness_selection_model)

rhat_overtness_selection_model

```

## Trace plots

```{r,message=FALSE,warning=FALSE,echo=FALSE}

targets::tar_load(trace_plot_overtness_selection_model)

trace_plot_overtness_selection_model

```

## Posterior predictive check

```{r,message=FALSE,warning=FALSE,echo=FALSE}

targets::tar_load(pp_check_overtness_selection_model)

pp_check_overtness_selection_model

```

# Training Model

## $\hat{R}$

```{r,message=FALSE,warning=FALSE,echo=FALSE}

targets::tar_load(rhat_training_model)

rhat_training_model

```

## Trace plots

```{r,message=FALSE,warning=FALSE,echo=FALSE}

targets::tar_load(trace_plot_training_model)

trace_plot_training_model

```

## Posterior predictive check

```{r,message=FALSE,warning=FALSE,echo=FALSE}

targets::tar_load(pp_check_training_model)

pp_check_training_model

```

# Study Design Model

## $\hat{R}$

```{r,message=FALSE,warning=FALSE,echo=FALSE}

targets::tar_load(rhat_study_design_model)

rhat_study_design_model

```

## Trace plots

```{r,message=FALSE,warning=FALSE,echo=FALSE}

targets::tar_load(trace_plot_study_design_model)

trace_plot_study_design_model

```

## Posterior predictive check

```{r,message=FALSE,warning=FALSE,echo=FALSE}

targets::tar_load(pp_check_study_design_model)

pp_check_study_design_model

```

### 2023-11-25 pre_print_manuscript.qmd
Linkked to diagnostic plots in manuscript

@@
   Self-talk has been researched as an aspect of mental preparation for performance in sports and other motor tasks since the late 1980s.
-In 2011 Hatzigeorgiadis and colleagues systematically reviewed and meta-analysed three decades of self-talk intervention research including 32 studies.
+In 2011, Hatzigeorgiadis and colleagues systematically reviewed and meta-analysed three decades of self-talk intervention research including 32 studies.
 Yet, despite the general proliferation of meta-analyses, this topic has not been meta-analysed in the decade since their review which, at least for the main effect, provided a reasonably precise standardised mean difference estimate (0.48 [95% confidence interval: 0.38, 0.58]).
@@
 Therefore, our aim was to conduct an updated systematic review and Bayesian meta-analysis replicating the search, inclusion, and models of Hatzigeorgiadis et al.
+(2011).
 Informative priors were taken directly from Hatzigeorgiadis et al.
@@
 This was in order to obtain precise Bayes Factors using the Savage-Dickey ratio [@gronauBridgesamplingPackageEstimating2020].
+Trace plots were produced along with $\hat{R}$ values to examine whether chains had converged, and posterior predictive checks for each model were also examined to understand the model implied distributions.
+These all showed good convergence with all $\hat{R}$ values close to 1 and  posterior predictive checks seemed appropriate distributions for the observed data (all diagnostic plots can be seen in the supplementary materials: [https://osf.io/xbcw8](https://osf.io/xbcw8)).
 

### 2024-07-23 response_to_reviewers.qmd
Rebuilding targets pipeline... up to motor demands up to date

---
title: "Response to Reviewers"
subtitle: "Updating meta-analyses cumulatively using Bayesian methods: An example updating a previous meta-analysis of self-talks interventions for sport/motor performance"
format: pdf
---

Dear \[insert editor name\],

Many thanks for considering our manuscript and placing it under review with \[insert journal name\]. We are very grateful for your efforts in obtaining reviews. We are very impressed with the quality and constructiveness of the feedback provided by the reviewers which we feel has significantly improved the quality of our manuscript.

Note, because of the extensive rewrite of the manuscript due to the shift in focus we have not used track changes or highlighting throughout, though changes can be viewed in the GitHub repository versions. However, please see below for our comments in response to some of the key points raised by the reviewers.

Again, we would like to thank all involved in the process of reviewing this manuscript and look forward to the next round of reviews in considering our revisions.

Many thanks

The authors

# Reviewer Comments and [Author Responses]{style="color:red;"}

## Reviewer 1 - Maik Bieleke

### Reviewer Comment

Contrary to what the title suggests, I did not have the impression that the article is best framed as a meta-analysis of self-talk interventions. It does not align particularly well with established standards for meta-analyses (PRISMA guidelines; e.g. flow charts, risk-of-bias analyses) and there are only very limited references to the self-talk literature. Rather, the article seems better described as a methodological contribution that demonstrates the benefits of Bayesian methods for cumulative science, using self-talk interventions as a convenient but largely interchangeable example. The keywords chosen by the authors reinforce this impression by omitting any reference to self-talk and meta-analysis. Therefore, a clearer and more consistent positioning of the article as valuable methodological contribution to cumulative science, rather than a standalone meta-analysis, might enhance clarity in this regard.

### [Author Response]{style="color:red;"}

[Thank you for your suggestion. It is actually a point which in retrospect after submitting the manuscript we realised more ourselves and so it is gratifying to have this reinforced by both reviewers. For clarity, the absence of certain methodological details such as those noted did stem partly from us wanting to replicate the methods employed by Hatzigeorgiadis et al. as closely as possible. As this was an undergraduate project being completed in a short period of time we opted to try to replicate to make the project more efficient under such constraints. We did initially intend though to include a PRISMA flow diagram to describe our updated searches, however we encountered an issue and realised that some of the searches we had conducted were not correctly recorded by the tool being used to manage the process. Unfortunately we were unable to exactly replicate it from attempting to reproduce the searches again. We have added this detail to footnote 2 for transparency.]{style="color:red;"}

[We do agree though that positioning this paper instead as an example of using Bayesian meta-analytic methods for cumulative science, whilst using the self-talk literature as an exemplar case-study given how long it has been since a quantitative evidence synthesis was conducted, is perhaps more suitable. As such we have attempted to rewrite the manuscript with this in mind, and have also changed the title to: *Cumulative evidence synthesis using Bayesian methods: An example updating a previous meta-analysis of self-talks interventions for sport/motor performance*]{style="color:red;"}

### Reviewer Comment

Whether or not the authors follow my previous suggestion, I think that a brief introduction to research on self-talk and self-talk interventions would aid readers in comprehending the narrative of the article (e.g., understanding and interpreting the moderator analyses). For example, the term self-talk is never explicitly introduced or defined, and the "key distinction" (p. 13) between strategic and organic self-talk is only mentioned towards the end of the discussion.

### [Author Response]{style="color:red;"}

[Given the reframing of the paper, we have now subsectioned the introduction and include a section more explicitly introducing self-talk.]{style="color:red;"}

### Reviewer Comment

On a quantitative note, I found it surprising that the confidence interval around the overall effect size remained virtually unchanged, although the amount of evidence doubled in terms of studies and effect sizes. Interestingly, the posterior CIs of the various moderators were indeed narrower than the prior CIs, an increase in precision one would expect when sample sizes increase. I wondered whether this might reflect unobserved qualitative differences between studies of some kind (e.g., additional moderators; also see comment 6 below) but maybe there is a simpler explanation that I'm missing.

### [Author Response]{style="color:red;"}

[This is an interesting, and somewhat counterintuitive result of our analysis. From the additional work we have conducted whereby we have utilised simulation to add a single new study and explore it's effects upon the prior distribution we were surprised that even a study simulated with one millions participants and a null effect had next to no impact in updating the prior estimate. As a result we conducted a little additional exploration regarding how the prior distribution was set. We utilised a $t$-distribution ($t(k,\mu,\sigma)$) with $k-2$ degrees of freedom as suggested by Higgins et al. (2009) cited in our manuscript. But, given the large degrees of freedom due to the large number of studies in the previous meta analysis from Hatzigeorgiadis et al., the $t$-distribution approximates a normal distribution more closely and thus has tight tails which influence the impact that an additional evidence might have on the prior when updating to a posterior (see this example from Richard McElreath - <https://x.com/rlmcelreath/status/1701165075493470644?s=20>). Out of curiosity we simulated a single study of one million participants and a null effect with a more skeptical $t$-distribution using only 3 degrees of freedom thus allowing the tails to be fatter. Even with this though \~85% of the entire posterior distribution was still within the 95% interval for the prior. To our interpretation this goes to show how certain the estimate from Hatzigeorgiadis et al. already was and highlights that further intervention research could be considered wasteful (assuming it has not contributed anything else to our understanding). However, as we explain in response to reviewer 2, we have now examined using various methods the possibility of small sample and publication bias in the studies included since 2011. This paints a concerning picture to our interpretation, though one that is perhaps not that surprising given that there is widespread evidence of such questionable research practices across many fields including the sport and exercise sciences. Hatzigeorgiadis et al. only examined this possibility using the now known to be flawed fail-safe N and from it concluded that there was likely no publication bias present prior to 2011. We find this hard to believe given that it is highly likely that prior to 2011, when many consider the current replication crisis in psychology (of course which sport psychology sits close to) kicked off, there were not many of the methodological reforms such as pre-registration and even registered reports, open data, materials, and code etc. in place that might help to mitigate somewhat the influence of QRPs such as publication bias. We didn't really want to end up down this route with the paper, and as noted due to it being an undergraduate project had deliberately conducted the updated systematic search to reduce the burden given the time available to complete the work. So we have not replicated the systematic search of Hatzigeorgiadis et al. for pre-2011. However, we have contacted the authors and asked for whether they still have their extracted data such that we might be able to examine this in the pre-2011 studies.]{style="color:red;"}

```         
    ### Reviewer Comment

    In the moderators section, the authors assert minimal differences between posterior estimates and priors. However, looking at Figure 2 it seems that the most extreme differences consistently decreased across moderator variables, pushing the posterior distributions closer to the overall effect size. Admittedly, this visual impression may be challenging to quantify or test, but it would be interesting to know the authors interpretation.

    ### [Author Response]{style="color:red;"}
    []{style="color:red;"}
```

### Reviewer Comment

I wondered whether "research waste" really is an appropriate label for all of the studies included in the present analysis. While these studies might have replicated the self-talk intervention effect, maybe this was not their main and/or only goal? Isn't it possible that these studies relied on the already established effect to answer a different question? For example, one might think of studies comparing self-talk as established intervention to a novel intervention. Such a study would likely be included in the present analysis due to its replication of the self-talk intervention effect, but its contribution mainly relates to examining the novel intervention. The term "research waste" then might overlook important contributions from these studies that go beyond (possibly unnecessary) replication efforts.

Relatedly, it might be worth noting that the analysis focused solely on quantitative aspects of replication (effect sizes, confidence intervals). This is fine but the authors also mention theoretical and conceptual advancements in the literature on self-talk. For somebody unfamiliar with the self-talk literature, it seems implausible that such improvements did not affect in any way how post-Hatzigeorgiadis self-talk interventions were delivered and/or evaluated. However, if administration or evaluation methods have changed (and potentially improved), the fact that our beliefs about intervention effects still remain mostly unchanged actually is reassuring, no? A qualitative analysis of the included studies might go beyond the scope of the present study, but it is still worth discussing whether and how it limits the interpretation of the quantitative analysis.

### [Author Response]{style="color:red;"}

[This is certainly a possibility and we have tried to soften the language regarding "research waste" somewhat throughout and also emphasise this limitation more in the discussion. We had considered in light of this comment whether to conduct a qualitative appraisal of the included studies to determine the extent to which they had either merely estimated the effects of self-talk interventions or explored moderators which were already well understood (though this we now question due to the possibility of publication bias in main effects) as opposed to contributing something new theoretically or methodologically. However, given the shift in the focus of the manuscript we opted not to do so but instead to highlight this as something those engaged in cumulative evidence synthesis should consider as well when determining whether research could be considered wasteful, or in the justification of a new trial by dint of the fact it might address theoretically or methodologically novel considerations.]{style="color:red;"}

### Reviewer Comment

In the introduction, the authors argue that "the effect estimate from the meta-analysis of Hatzigeorgiadis et al. (2011) was already fairly precise", implying that further research was unwarranted to begin with. I found the statement rather vague and the implication drawn with the benefit of hindsight. When is an estimate precise enough to discourage further replications, and aren't there other reasons for replicating an effect (e.g., robustness checks, changes in methodology) that warrant investigation?

### [Author Response]{style="color:red;"}

[We have now attempted to address this concern through the addition of simulations of the effects that a new study might have had post the meta-analysis of Hatzigeorgiadis et al. in terms of changing our conclusions regarding the effect. This lends some quantitative precision the the claim that it was already fairly precise adn that further research may have been unwarranted. Of course there may be other reasons to continue further research attempting to replicate an effect, though in this case we'd be skeptical that it is warranted.]{style="color:red;"}

### Reviewer Comment

There is currently no discussion of the potential strengths and limitations of the study. I think that adding this would make it easier for readers to gauge the contribution of the present research.

### [Author Response]{style="color:red;"}

[Given the reframing we instead have added discussion of the benefits of engaging with the kinds of methods demonstrated, but have also noted that supplementing this with qualitative appraisal is of value in determining wwhether addtional research is warranted.]{style="color:red;"}

## Reviewer 2 - Anonymous

### Reviewer Comment

Meta-analyses (as the authors of course know) estimate an average effect and deviations from this effect. Thus, meta-analyses only make sense when it is theoretically or conceptually meaningful to estimate an average effect over a set of studies. The Data Colada team makes this point better than I could, and they illustrate it with some nice examples (please see http://datacolada.org/104 and the related posts).

So, I was wondering: Does it make sense (both from a theoretical and an applied perspective) to estimate the average effect of self-talk? I am not saying that it doesn't, I simply do not know. In other words: The more the different self-talk interventions resemble each other (both in terms of theoretical foundations and in terms of their implementation), the more sense it makes to conduct a meta-analysis regarding their average effectiveness. Maybe the authors can address this point and add a couple of words on the similarity of the analyzed interventions.

### [Author Response]{style="color:red;"}

[This is a good question and one which we encounter often. Specifically in a random effects meta-analysis the overall main estimate is the weighted average of the effect*s* that each study has estimated. It begins with the assumption that the specific effect being estimated does differ across the studies for a range of factors mostly relating to the fact that they are all conceptual replications as opposed to direct replications. The benefit though is that we can quantify the heterogeneity via the $\tau$ parameter and determine whether it is meaningful enough to be concerned about. In addition, the moderator analyses allow for us to explore whether or not study, experiment, or group level factors might be influences of the effects that each study estimates within the overarching distribution of effects. So, we would argue that in the case of asking the question about the effects of an intervention, such as self-talk upon an outcome, such as sport/motor performance, meta-analysis can be appropriate if conducted appropriately.]{style="color:red;"}

### Reviewer Comment

I was a bit surprised that the authors did not assess potential publication bias, but maybe I missed something. It is my understanding that publication bias (e.g., only positive results are published) poses a serious threat to meta-analyses, and that therefore tools to assess publication bias have been developed. These tools may range from funnel plots to techniques such as Trim-and-fill, PET, PEESE and so on (e.g., Carter, E. C., Schönbrodt, F. D., Gervais, W. M., & Hilgard, J. (2019). Correcting for bias in psychology: A comparison of meta-analytic methods. Advances in Methods and Practices in Psychological Science, 2, 115-144. https://doi.org/10.1177/2515245919847196). Why did the authors not address potential publication bias? As far as I am concerned, one reason why results have not changed from 2011 till now might be that results that fit the picture get published easier?

### [Author Response]{style="color:red;"}

[Thank you for this suggestion. Somewhat in our haste and our focus on the updating aspect of the novel approach taken, we failed to consider this. However, we have now examined using various methods the possibility of small sample and publication bias in the studies included since 2011. The PET-PEESE and Robust Bayesian Model Averaging methods reveal evidence of publication bias and that the adjusted effect may in fact be null. This paints a concerning picture to our interpretation, though one that is perhaps not that surprising given that there is widespread evidence of such questionable research practices across many fields including the sport and exercise sciences. Hatzigeorgiadis et al. only examined this possibility using the now known to be flawed fail-safe N and from it concluded that there was likely no publication bias present prior to 2011. We find this hard to believe given that it is highly likely that prior to 2011, when many consider the current replication crisis in psychology (of course which sport psychology sits close to) kicked off, there were not many of the methodological reforms such as pre-registration and even registered reports, open data, materials, and code etc. in place that might help to mitigate somewhat the influence of QRPs such as publication bias. We didn't really want to end up down this route with the paper, and as noted due to it being an undergraduate project had deliberately conducted the updated systematic search to reduce the burden given the time available to complete the work. So we have not replicated the systematic search of Hatzigeorgiadis et al. for pre-2011. However, we have contacted the authors and asked for whether they still have their extracted data such that we might be able to examine this in the pre-2011 studies.]{style="color:red;"}

### Reviewer Comment

I do not understand the authors' point that all research in the meantime between the first meta-analysis and theirs was "a waste of research", simply because their meta-analysis comes to the same conclusion as the first one. To me, this statement is somewhat questionable for several reasons (at least in the way it is presented in the present form of the article).

First, the argument is only logically valid if we suppose that the *only* goal of the studies that were analyzed was to assess the effectiveness of self-talk. However, if some of the studies had additional goals, then the "waste of research" conclusion is not valid anymore. Please let me illustrate this point with a couple of examples. Suppose that a study aimed to find out whether self-talk works better for soccer players than for basketball players. The results show that it doesn't. In this case, we have learned something from the respective study, even if in a meta-analysis the study gets the same effect size like in a previous meta-analysis.

Or suppose that a study aimed to find out whether self-talk works better for handball players than for volleyball players. The results suggest that it works above average for handball players and below average for volleyball players. Again, the average effect would be the same as in the previous meta-analysis, but again I assume that we have learned something.

On a very basic level, I would like to argue that in order to decide whether a study was a waste of research and resources you have to take into account that very study's goals. Therefore, I was wondering: Was the only goal of the studies analyzed in the present meta-analysis really to assess the average effectiveness of self-talk?

### [Author Response]{style="color:red;"}

[Reviewer 1 also raised this concern and we have tried to soften the language regarding "research waste" somewhat throughout and also emphasise this limitation more in the discussion. We had considered in light of this comment whether to conduct a qualitative appraisal of the included studies to determine the extent to which they had either merely estimated the effects of self-talk interventions or explored moderators which were already well understood (though this we now question due to the possibility of publication bias in main effects) as opposed to contributing something new theoretically or methodologically. However, given the shift in the focus of the manuscript we opted not to do so but instead to highlight this as something those engaged in cumulative evidence synthesis should consider as well when determining whether research could be considered wasteful, or in the justification of a new trial by dint of the fact it might address theoretically or methodologically novel considerations.]{style="color:red;"}

### Reviewer Comment

When exactly does additional research become "a waste"? I totally agree that research is not efficient anymore when it does not add anything to established knowledge anymore. However, when is knowledge really established in psychology? Considering the average sample sizes in psychology, even 10 psychological studies might not have the sample size that might be considered necessary to yield established knowledge in other fields. Again, I am not saying that there will not eventually come a point where further research becomes unnecessary and thus inefficient. I am simply wondering: When does it come?

### [Author Response]{style="color:red;"}

[We have tried to better address this by leveraging simulating the addition a single new study, varying the underlying effect size and sample size, and explore it's effects upon the prior distribution. This is to demonstrate that such an approach can aid in determining exactly when the addition of new studies, whether small or indeed large, might be unnecessary in light of current evidence.]{style="color:red;"}

### Reviewer Comment

Third, the authors themselves write (p. 2 / 3) that research on self-talk might have matured post 2011 regarding "... efforts to improve operationalisation/measurement, and efforts to improve methodology used in studying self-talk". Quite frankly, I cannot reconcile this observation with the statement that this research was a waste. I mean, finding the same effects with better measurement and methods should increase our confidence both in self-talk per se, but also in the results prior to 2011, or not? Suppose you have a study that finds a certain effect, but this study has weaknesses. Now a study with better methods finds the same effect. Would you really want to argue that the second study was a waste, because it finds the same effect? I surely would not.

### [Author Response]{style="color:red;"}

[As noted we have tried to make it clear that such qualitative considerations should also be taken into account when determining whether research has been wasteful, or indeed further research might be. Although, for the specific example of self-talk the process of working on this project has been enlightening and left us in considerable doubt of the value of much of the research in the area (though notably that would be the case for many areas within the sport and exercise sciences).]{style="color:red;"}

### 2024-07-23 diagnostic_plots.tex
Rebuilding targets pipeline... up to motor demands up to date

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
]{report}

\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else  
    % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother

\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\makeatother
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{english}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Diagnostic Plots},
  pdfauthor={Hannah Corcoran, James Steele},
  pdflang={en},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\title{Diagnostic Plots}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{Self-talk interventions and sport/motor performance: An
updated systematic review and Bayesian meta-analysis}
\author{Hannah Corcoran, James Steele}
\date{}

\begin{document}
\maketitle
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, interior hidden, boxrule=0pt, borderline west={3pt}{0pt}{shadecolor}, breakable, sharp corners, frame hidden]}{\end{tcolorbox}}\fi

\hypertarget{main-model}{%
\chapter{Main Model}\label{main-model}}

\hypertarget{hatr}{%
\section{\texorpdfstring{\(\hat{R}\)}{\textbackslash hat\{R\}}}\label{hatr}}

\begin{figure}

{\centering \includegraphics[width=1\textwidth,height=\textheight]{diagnostic_plots_files/figure-pdf/unnamed-chunk-1-1.pdf}

}

\end{figure}

\hypertarget{trace-plots}{%
\section{Trace plots}\label{trace-plots}}

\begin{figure}

{\centering \includegraphics[width=1\textwidth,height=\textheight]{diagnostic_plots_files/figure-pdf/unnamed-chunk-2-1.pdf}

}

\end{figure}

\begin{figure}

{\centering \includegraphics[width=1\textwidth,height=\textheight]{diagnostic_plots_files/figure-pdf/unnamed-chunk-2-2.pdf}

}

\end{figure}

\begin{verbatim}
[[1]]

[[2]]
\end{verbatim}

\hypertarget{posterior-predictive-check}{%
\section{Posterior predictive check}\label{posterior-predictive-check}}

\begin{figure}

{\centering \includegraphics[width=1\textwidth,height=\textheight]{diagnostic_plots_files/figure-pdf/unnamed-chunk-3-1.pdf}

}

\end{figure}

\hypertarget{motor-demands-model}{%
\chapter{Motor Demands Model}\label{motor-demands-model}}

\hypertarget{hatr-1}{%
\section{\texorpdfstring{\(\hat{R}\)}{\textbackslash hat\{R\}}}\label{hatr-1}}

\begin{figure}

{\centering \includegraphics[width=1\textwidth,height=\textheight]{diagnostic_plots_files/figure-pdf/unnamed-chunk-4-1.pdf}

}

\end{figure}

\hypertarget{trace-plots-1}{%
\section{Trace plots}\label{trace-plots-1}}

\begin{figure}

{\centering \includegraphics[width=1\textwidth,height=\textheight]{diagnostic_plots_files/figure-pdf/unnamed-chunk-5-1.pdf}

}

\end{figure}

\begin{figure}

{\centering \includegraphics[width=1\textwidth,height=\textheight]{diagnostic_plots_files/figure-pdf/unnamed-chunk-5-2.pdf}

}

\end{figure}

\begin{verbatim}
[[1]]

[[2]]
\end{verbatim}

\hypertarget{posterior-predictive-check-1}{%
\section{Posterior predictive
check}\label{posterior-predictive-check-1}}

\begin{figure}

{\centering \includegraphics[width=1\textwidth,height=\textheight]{diagnostic_plots_files/figure-pdf/unnamed-chunk-6-1.pdf}

}

\end{figure}

\hypertarget{participant-group-model}{%
\chapter{Participant Group Model}\label{participant-group-model}}

\hypertarget{hatr-2}{%
\section{\texorpdfstring{\(\hat{R}\)}{\textbackslash hat\{R\}}}\label{hatr-2}}

\begin{figure}

{\centering \includegraphics[width=1\textwidth,height=\textheight]{diagnostic_plots_files/figure-pdf/unnamed-chunk-7-1.pdf}

}

\end{figure}

\hypertarget{trace-plots-2}{%
\section{Trace plots}\label{trace-plots-2}}

\begin{figure}

{\centering \includegraphics[width=1\textwidth,height=\textheight]{diagnostic_plots_files/figure-pdf/unnamed-chunk-8-1.pdf}

}

\end{figure}

\begin{figure}

{\centering \includegraphics[width=1\textwidth,height=\textheight]{diagnostic_plots_files/figure-pdf/unnamed-chunk-8-2.pdf}

}

\end{figure}

\begin{verbatim}
[[1]]

[[2]]
\end{verbatim}

\hypertarget{posterior-predictive-check-2}{%
\section{Posterior predictive
check}\label{posterior-predictive-check-2}}

\begin{figure}

{\centering \includegraphics[width=1\textwidth,height=\textheight]{diagnostic_plots_files/figure-pdf/unnamed-chunk-9-1.pdf}

}

\end{figure}

\hypertarget{self-talk-content-model}{%
\chapter{Self-Talk Content Model}\label{self-talk-content-model}}

\hypertarget{hatr-3}{%
\section{\texorpdfstring{\(\hat{R}\)}{\textbackslash hat\{R\}}}\label{hatr-3}}

\begin{figure}

{\centering \includegraphics[width=1\textwidth,height=\textheight]{diagnostic_plots_files/figure-pdf/unnamed-chunk-10-1.pdf}

}

\end{figure}

\hypertarget{trace-plots-3}{%
\section{Trace plots}\label{trace-plots-3}}

\begin{figure}

{\centering \includegraphics[width=1\textwidth,height=\textheight]{diagnostic_plots_files/figure-pdf/unnamed-chunk-11-1.pdf}

}

\end{figure}

\begin{figure}

{\centering \includegraphics[width=1\textwidth,height=\textheight]{diagnostic_plots_files/figure-pdf/unnamed-chunk-11-2.pdf}

}

\end{figure}

\begin{verbatim}
[[1]]

[[2]]
\end{verbatim}

\hypertarget{posterior-predictive-check-3}{%
\section{Posterior predictive
check}\label{posterior-predictive-check-3}}

\begin{figure}

{\centering \includegraphics[width=1\textwidth,height=\textheight]{diagnostic_plots_files/figure-pdf/unnamed-chunk-12-1.pdf}

}

\end{figure}

\hypertarget{matching-model}{%
\chapter{Matching Model}\label{matching-model}}

\hypertarget{hatr-4}{%
\section{\texorpdfstring{\(\hat{R}\)}{\textbackslash hat\{R\}}}\label{hatr-4}}

\begin{figure}

{\centering \includegraphics[width=1\textwidth,height=\textheight]{diagnostic_plots_files/figure-pdf/unnamed-chunk-13-1.pdf}

}

\end{figure}

\hypertarget{trace-plots-4}{%
\section{Trace plots}\label{trace-plots-4}}

\begin{figure}

{\centering \includegraphics[width=1\textwidth,height=\textheight]{diagnostic_plots_files/figure-pdf/unnamed-chunk-14-1.pdf}

}

\end{figure}

\begin{figure}

{\centering \includegraphics[width=1\textwidth,height=\textheight]{diagnostic_plots_files/figure-pdf/unnamed-chunk-14-2.pdf}

}

\end{figure}

\begin{verbatim}
[[1]]

[[2]]
\end{verbatim}

\hypertarget{posterior-predictive-check-4}{%
\section{Posterior predictive
check}\label{posterior-predictive-check-4}}

\begin{figure}

{\centering \includegraphics[width=1\textwidth,height=\textheight]{diagnostic_plots_files/figure-pdf/unnamed-chunk-15-1.pdf}

}

\end{figure}

\hypertarget{task_novelty-model}{%
\chapter{task\_novelty Model}\label{task_novelty-model}}

\hypertarget{hatr-5}{%
\section{\texorpdfstring{\(\hat{R}\)}{\textbackslash hat\{R\}}}\label{hatr-5}}

\begin{figure}

{\centering \includegraphics[width=1\textwidth,height=\textheight]{diagnostic_plots_files/figure-pdf/unnamed-chunk-16-1.pdf}

}

\end{figure}

\hypertarget{trace-plots-5}{%
\section{Trace plots}\label{trace-plots-5}}

\begin{figure}

{\centering \includegraphics[width=1\textwidth,height=\textheight]{diagnostic_plots_files/figure-pdf/unnamed-chunk-17-1.pdf}

}

\end{figure}

\begin{figure}

{\centering \includegraphics[width=1\textwidth,height=\textheight]{diagnostic_plots_files/figure-pdf/unnamed-chunk-17-2.pdf}

}

\end{figure}

\begin{verbatim}
[[1]]

[[2]]
\end{verbatim}

\hypertarget{posterior-predictive-check-5}{%
\section{Posterior predictive
check}\label{posterior-predictive-check-5}}

\begin{figure}

{\centering \includegraphics[width=1\textwidth,height=\textheight]{diagnostic_plots_files/figure-pdf/unnamed-chunk-18-1.pdf}

}

\end{figure}

\hypertarget{cue-selection-model}{%
\chapter{Cue Selection Model}\label{cue-selection-model}}

\hypertarget{hatr-6}{%
\section{\texorpdfstring{\(\hat{R}\)}{\textbackslash hat\{R\}}}\label{hatr-6}}

\begin{figure}

{\centering \includegraphics[width=1\textwidth,height=\textheight]{diagnostic_plots_files/figure-pdf/unnamed-chunk-19-1.pdf}

}

\end{figure}

\hypertarget{trace-plots-6}{%
\section{Trace plots}\label{trace-plots-6}}

\begin{figure}

{\centering \includegraphics[width=1\textwidth,height=\textheight]{diagnostic_plots_files/figure-pdf/unnamed-chunk-20-1.pdf}

}

\end{figure}

\begin{figure}

{\centering \includegraphics[width=1\textwidth,height=\textheight]{diagnostic_plots_files/figure-pdf/unnamed-chunk-20-2.pdf}

}

\end{figure}

\begin{verbatim}
[[1]]

[[2]]
\end{verbatim}

\hypertarget{posterior-predictive-check-6}{%
\section{Posterior predictive
check}\label{posterior-predictive-check-6}}

\begin{figure}

{\centering \includegraphics[width=1\textwidth,height=\textheight]{diagnostic_plots_files/figure-pdf/unnamed-chunk-21-1.pdf}

}

\end{figure}

\hypertarget{overtness-selection-model}{%
\chapter{Overtness Selection Model}\label{overtness-selection-model}}

\hypertarget{hatr-7}{%
\section{\texorpdfstring{\(\hat{R}\)}{\textbackslash hat\{R\}}}\label{hatr-7}}

\begin{figure}

{\centering \includegraphics[width=1\textwidth,height=\textheight]{diagnostic_plots_files/figure-pdf/unnamed-chunk-22-1.pdf}

}

\end{figure}

\hypertarget{trace-plots-7}{%
\section{Trace plots}\label{trace-plots-7}}

\begin{figure}

{\centering \includegraphics[width=1\textwidth,height=\textheight]{diagnostic_plots_files/figure-pdf/unnamed-chunk-23-1.pdf}

}

\end{figure}

\begin{figure}

{\centering \includegraphics[width=1\textwidth,height=\textheight]{diagnostic_plots_files/figure-pdf/unnamed-chunk-23-2.pdf}

}

\end{figure}

\begin{verbatim}
[[1]]

[[2]]
\end{verbatim}

\hypertarget{posterior-predictive-check-7}{%
\section{Posterior predictive
check}\label{posterior-predictive-check-7}}

\begin{figure}

{\centering \includegraphics[width=1\textwidth,height=\textheight]{diagnostic_plots_files/figure-pdf/unnamed-chunk-24-1.pdf}

}

\end{figure}

\hypertarget{training-model}{%
\chapter{Training Model}\label{training-model}}

\hypertarget{hatr-8}{%
\section{\texorpdfstring{\(\hat{R}\)}{\textbackslash hat\{R\}}}\label{hatr-8}}

\begin{figure}

{\centering \includegraphics[width=1\textwidth,height=\textheight]{diagnostic_plots_files/figure-pdf/unnamed-chunk-25-1.pdf}

}

\end{figure}

\hypertarget{trace-plots-8}{%
\section{Trace plots}\label{trace-plots-8}}

\begin{figure}

{\centering \includegraphics[width=1\textwidth,height=\textheight]{diagnostic_plots_files/figure-pdf/unnamed-chunk-26-1.pdf}

}

\end{figure}

\begin{figure}

{\centering \includegraphics[width=1\textwidth,height=\textheight]{diagnostic_plots_files/figure-pdf/unnamed-chunk-26-2.pdf}

}

\end{figure}

\begin{verbatim}
[[1]]

[[2]]
\end{verbatim}

\hypertarget{posterior-predictive-check-8}{%
\section{Posterior predictive
check}\label{posterior-predictive-check-8}}

\begin{figure}

{\centering \includegraphics[width=1\textwidth,height=\textheight]{diagnostic_plots_files/figure-pdf/unnamed-chunk-27-1.pdf}

}

\end{figure}

\hypertarget{study-design-model}{%
\chapter{Study Design Model}\label{study-design-model}}

\hypertarget{hatr-9}{%
\section{\texorpdfstring{\(\hat{R}\)}{\textbackslash hat\{R\}}}\label{hatr-9}}

\begin{figure}

{\centering \includegraphics[width=1\textwidth,height=\textheight]{diagnostic_plots_files/figure-pdf/unnamed-chunk-28-1.pdf}

}

\end{figure}

\hypertarget{trace-plots-9}{%
\section{Trace plots}\label{trace-plots-9}}

\begin{figure}

{\centering \includegraphics[width=1\textwidth,height=\textheight]{diagnostic_plots_files/figure-pdf/unnamed-chunk-29-1.pdf}

}

\end{figure}

\begin{figure}

{\centering \includegraphics[width=1\textwidth,height=\textheight]{diagnostic_plots_files/figure-pdf/unnamed-chunk-29-2.pdf}

}

\end{figure}

\begin{verbatim}
[[1]]

[[2]]
\end{verbatim}

\hypertarget{posterior-predictive-check-9}{%
\section{Posterior predictive
check}\label{posterior-predictive-check-9}}

\begin{figure}

{\centering \includegraphics[width=1\textwidth,height=\textheight]{diagnostic_plots_files/figure-pdf/unnamed-chunk-30-1.pdf}

}

\end{figure}

\end{document}

### 2024-07-23 pre_print_manuscript.qmd
Fix the dang "onto to" abstract typo.
Rebuilding targets pipeline... up to motor demands up to date

@@
 articletitle: |
-  Self-talk interventions and sport/motor performance: An updated systematic review and Bayesian meta-analysis
+  Cumulative evidence synthesis using Bayesian methods: An example updating a previous meta-analysis of self-talk interventions for sport/motor performance
 format: 
@@
 However, they also suggest that cumulatively the past decade and more of research has done little to further our understanding of these effects.
-Considering the limited resources and time for conducting research, it may be worth moving onto to other more pertinent questions regarding psychological constructs impact upon sport/motor performance.
+Considering the limited resources and time for conducting research, it may be worth moving onto other more pertinent questions regarding psychological constructs impact upon sport/motor performance.
 license-type: ccby # change if neccessary
@@
 
+###### STUFF TO ADD??
+https://systematicreviewsjournal.biomedcentral.com/articles/10.1186/s13643-022-02096-y
+
+https://www.thelancet.com/journals/lancet/article/PIIS0140-6736(15)00489-4/fulltext
+
+https://www.thelancet.com/journals/lancet/article/PIIS0140-6736(15)01354-9/fulltext
+
+https://academic.oup.com/biometrics/article/79/1/319/7478096?login=false
+
+https://www.researchgate.net/publication/338878953_p-Hacking_and_Publication_Bias_Interact_to_Distort_Meta-Analytic_Effect_Size_Estimates
+
+https://www.researchgate.net/publication/336963847_Toward_a_common_language_categorization_and_better_assessment_in_self-talk_research_Commentary_on_Speaking_clearly_10_years_on
+
+https://www.researchgate.net/publication/312934559_On_Investigating_Self-Talk_A_Descriptive_Experience_Sampling_Study_of_Inner_Experience_During_Golf_Performance
+
+https://www.researchgate.net/publication/337822503_Strengthening_the_Assessment_of_Self-Talk_in_Sports_Through_a_Multi-Method_Approach
+
+https://www.researchgate.net/publication/304398817_Why_Self-Talk_Is_Effective_Perspectives_on_Self-Talk_Mechanisms_in_Sport
+
 # Introduction
+## Cumulative evidence synthesis 
+Two questions that should be asked (though arguably are not often enough particularly in sport science) by researchers when planning a study of an experimental intervention is "what is the likelihood that the experimental intervention is superior to the control intervention given the evidence accumulated so far?", and "what is the likelihood that a new trial, given some design parameters and previous evidence, will demonstrate the superiority of the experimental intervention?".
+The key here is to consider the *cumulative* nature of evidence provided by research and its synthesis.
+Indeed, to not do this could lead to so called "research waste".
+Evidence synthesis methods are essential to determining whether or not there is justification for further research on a given topic, and the Cochrane-Collaboration and REWARD (Reduce Research Waste and Reward Diligence) Alliance have even established an award for efforts in the area of reducing "research waste" [@glasziouResearchWasteStill2018].
 
-Self-talk has a long history of philosophical, theoretical, and empirical work [@geurtsMakingSenseSelf2018; @brinthauptSelftalkResearchChallenges2023; @latinjakSelfTalkInterdisciplinaryReview2023].
-One area in which self-talk remains a popular topic of research up to this day is in the sport sciences [@vanraalteSelftalkReviewSportspecific2016; @hardyReflectionsMaturingResearch2018; @latinjakSelfTalkInterdisciplinaryReview2023].
+          Add about QRPs and research waste - evaluate the not only the results, but the quality of the preceding evidence in addition to whether it may have been subject to any bias
+
+Cumulative meta-analyses were proposed in the early 1990s and have since then been promoted as key tools to understand whether or not additional research is a worthwhile use of resources for addressing a particular question regarding experimental intervention [@clarkeAccumulatingResearchSystematic2014; @graingerEvidenceSynthesisTackling2020].
+Further, Bayesian approaches are well positioned to tackle this [@biauUsingBayesianStatistics2017].
+
+Within Bayesian statistical inference a prior probability distribution regarding the effect of interest is *updated* after the introduction of new evidence to a posterior probability distribution given Bayes theorem.
+In the present paper we demonstrate the application of Bayesian methods to meta-analysis in the sport and exercise sciences for the evaluation of experimental interventions using cumulative evidence synthesis.
+We assume some prior knowledge of evidence synthesis and meta-analytic methods on the part of the reader, though for those unfamiliar suggest some recent introductory papers regarding their application in the field [@gunnellQuestionsAnswersConducting2020; @haggerMetaanalysis2022; @steeleMetaanalysisVariationSport2023].
+We use the example of self-talk interventions and their effects upon motor/sport performance given a quantitative evidence synthesis has not been conducted on this topic to the best of our knowledge since 2011 when Hatzigeorgiadis et al.
+[-@hatzigeorgiadisSelfTalkSportsPerformance2011] conducted their systematic review and meta-analysis.
+
+## Self-talk interventions
 Sport psychology as a broad field has focused on the theorising of psychological constructs that might impact upon performance, and the subsequent experimental testing of theoretically informed interventions to address these constructs.
 For example, a recent umbrella review identified thirty meta-analyses exploring the effects of different sport psychology constructs upon performance, thirteen of them examining the effects of interventions, finding an overall standardised mean difference (SMD) for positive constructs of 0.51 \[95% confidence interval: 0.42, 0.58\] [@lochbaumSportPsychologyPerformance2022].
-Only one meta-analysis explored the effects of self-talk interventions; Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011].
+One construct with a long history of philosophical, theoretical, and empirical work [@geurtsMakingSenseSelf2018; @brinthauptSelftalkResearchChallenges2023; @latinjakSelfTalkInterdisciplinaryReview2023] that has been the target of considerable investigation in this field has been self-talk.
+
+As a concept self-talk has been  defined in various ways in previous work on the topic; though recent transdisciplinary review [@latinjakSelfTalkInterdisciplinaryReview2023] has agreed upon a broad conceptualisation: *"verbalizations addressed to the self, overtly or covertly, characterized by interpretative elements associated to their content; and it [self-talk] either (a) reflects dynamic interplays between organic, spontaneous and goal-directed cognitive processes or (b) conveys messages to activate responses through the use of predetermined cues developed strategically, to achieve performance-related outcomes"* [@latinjakSpeakingClearly102019].
+However as noted, whilst there has been various narrative syntheses of research on self-talk [@vanraalteSelftalkReviewSportspecific2016; @hardyReflectionsMaturingResearch2018; @latinjakSelfTalkInterdisciplinaryReview2023], only one systematic review and meta-analysis has explored the effects of self-talk interventions; Hatzigeorgiadis et al.
+[-@hatzigeorgiadisSelfTalkSportsPerformance2011].
 
 The meta-analysis by Hatzigeorgiadis et al.
-[-@hatzigeorgiadisSelfTalkSportsPerformance2011] included a total of 32 studies and 62 effect size estimates revealing an overall SMD estimate of 0.48 \[95% confidence interval: 0.38, 0.58\] and also explored the effects of various moderators of the effectiveness of self-talk interventions.
+[-@hatzigeorgiadisSelfTalkSportsPerformance2011] included a total of 32 studies and 62 effect size estimates revealing an overall SMD estimate of 0.48 \[95% confidence interval: 0.38, 0.58\] and also explored the effects of various theoretically driven moderators of the effectiveness of self-talk interventions.
+For example; characteristics of the tasks performed such as their novelty and whether they are fine or gross motor task, characteristics of the participants such as their level of experience with the task, the characteristics of the self-talk used including its content, whether it was self-selected or assigned, and whether it was used overtly or not, characteristics of the intervention and whether it included brief exposure or a training period, and testing the 'matching hypothesis' which posits that instructional self-talk should benefit fine tasks whereas motivational self-talk should benefit gross tasks to a greater degree.
+
 Around the time that Hatzigeorgiadis et al.
@@
 However in the last decade, particularly in sport psychology, there has been an increasing reliance on meta-analyses [@lochbaumSportPsychologyPerformance2022; @haggerMetaanalysis2022].
-Yet, despite the general proliferation of meta-analyses in the past decade, the effects of self-talk interventions has not been re-evaluated by means of such quantitative synthesis since 2011, when Hatzigeorgiadis et al.
+Despite the general proliferation of meta-analyses in the past decade, the effect of self-talk interventions has not been re-evaluated by means of such quantitative synthesis since 2011, when Hatzigeorgiadis et al.
 [-@hatzigeorgiadisSelfTalkSportsPerformance2011] completed their work.
@@
 Whilst self-talk as a field may have matured in the post-2011 years with theoretical advancements in conceptualisation of the construct and mediators of its effects on performance, efforts to improve operationalisation/measurement, and efforts to improve methodology used in studying self-talk [@brinthauptSelftalkResearchChallenges2023; @geurtsMakingSenseSelf2018; @hardyReflectionsMaturingResearch2018; @latinjakSelfTalkInterdisciplinaryReview2023; @vanraalteSelftalkReviewSportspecific2016; @latinjakSpeakingClearly102019], it could be argued that understanding of the effectiveness of self-talk *interventions* (referred to in modern literature as 'strategic' self-talk; @latinjakSpeakingClearly102019) was "mature" prior to 2011.
-The effect estimate from the meta-analysis of Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011] was already fairly precise, and indeed so to were many of the moderator estimates.
-Several further studies on self-talk interventions have been conducted since 2011 and it is a reasonable question to ask, given the limited time and resource for conducting research in the field of sport science, to whether and to what extent these have advanced our understanding or whether they have largely contributed to "research waste".
+The effect estimate from the meta-analysis of Hatzigeorgiadis et al.
+[-@hatzigeorgiadisSelfTalkSportsPerformance2011] might be considered by some to have been already fairly precise only spanning 0.2 SMD, and indeed aswell for many of the moderator estimates.
 
-Two questions that should (though arguably are not often enough particularly in sport science) be asked by researchers when planning a study of an experimental intervention is "what is the likelihood that the experimental intervention is superior to the control intervention given the evidence accumulated so far?", and "what is the likelihood that a new trial, given some design parameters and previous evidence, will demonstrate the superiority of the experimental intervention?".
-The key here is to consider the *cumulative* nature of evidence provided by research.
-Cumulative meta-analyses were proposed in the early 1990s and have since then been argued to be key tools to answering these questions and considering whether or not additional research is a worthwhile use of resources [@clarkeAccumulatingResearchSystematic2014; @graingerEvidenceSynthesisTackling2020].
-Bayesian approaches are well positioned to tackle this [@biauUsingBayesianStatistics2017].
-Within Bayesian statistical inference a prior probability distribution regarding the effect of interest is *updated* after the introduction of new evidence to a posterior probability distribution given Bayes theorem.
+Many additional studies on self-talk interventions have been conducted since 2011.
+It may well be that such recent work has improved our estimates of the effects of self-talk interventions and what moderates their effectiveness, or indeed contributed to other areas of understanding of the construct of self-talk.
+But, it is a reasonable question to ask, given the limited time and resource for conducting research in the field of sport science and what we already know regarding these interventions, whether and to what extent these studies have advanced our understanding of their effects, or whether they have largely contributed to so called "research waste" [@graingerEvidenceSynthesisTackling2020; @glasziouResearchWasteStill2018].
 
+## Aim of the present work
+The aim of this present work is to demonstrate the application of Bayesian methods in evidence synthesis, in particular to meta-analysis, in the sport and exercise sciences for the evaluation of experimental interventions.
 Given that there has not been, to the best of our knowledge, a meta-analytic synthesis of the effects of self-talk interventions effects upon sport/motor performance since Hatzigeorgiadis et al.
-[-@hatzigeorgiadisSelfTalkSportsPerformance2011] it is unclear the extent to which the past decade and more of research has advanced our understanding or potentially contributed to “research waste”.
+[-@hatzigeorgiadisSelfTalkSportsPerformance2011] it represents a prime topic to utilise as an example for these methods.
 Therefore, our aim was to conduct an updated systematic review and Bayesian meta-analysis replicating the search, inclusion, and models of Hatzigeorgiadis et al.
-[-@hatzigeorgiadisSelfTalkSportsPerformance2011].
+[-@hatzigeorgiadisSelfTalkSportsPerformance2011] in order to demonstrate the application of cumulative evidence synthesis methods including; consideration of the initial probability that a new study of the effects of self-talk interventions would shift our prior belief in their effectiveness, the application of priors taken from the previous meta-analysis to be updated by new studies identified to a new posterior estimate of effect, and consideration of other sources of research waste from questionable research practices such as possible publication bias.
 
@@
 [^2]: Though we feel fairly confident, given the number of studies identified and the findings of our models reported below, that any missed studies would be unlikely to qualitatively impact the overall findings and conclusions of this work.
+We should also note that we originally intended to report a PRISMA flow diagram of our search and retrieval process.
+However, for transparency, we encountered an issue where we realised that some of the searches we had conducted were not correctly recorded by the tool being used to manage the process.
+We were, despite attempting to do so, unable to exactly replicate the searches (number of hits from initial search string in databases used) at the time we realised from attempting to reproduce the searches again.
+As such, we do not present a PRISMA diagram though as noted we do feel fairly confident we have not missed any key studies nor that minor omissions would affect the overall results of our analyses.
 
@@
 The data extracted was imported into a spreadsheet in excel as a csv.
+
+ADD DETAILS ABOUT QUALITATIVE APPRAISAL OF STUDY AIMS
 
@@
 From each model we obtained draws from the posterior distributions for the intervention effects (i.e., the expectation of the value of the parameters posterior probability distribution) in order to present probability density functions visually, and also to calculate mean and 95% quantile intervals (i.e., 'credible' or 'compatibility' intervals) for each estimate.
-These gave us the most probably value of the parameter in addition to the range from 2.5% to 97.5% percentiles.
+These gave us the most probable value of the parameter in addition to the range from 2.5% to 97.5% percentiles.
 The same was done drawing samples from the prior distributions only in order to present both distributions visually for comparison of the prior to posterior updating.
@@
 
+ADD - https://www.researchgate.net/publication/338361731_Careful_what_you_say_to_yourself_Exploring_self-talk_and_youth_tennis_performance_via_hierarchical_linear_modeling
+
 # Conclusion

### 2024-07-23 R/functions.R

@@ -1,8 +1,8 @@
 # Read in and prepare data for effect size calculations and models
 read_prepare_data <- function(file) {
-  data <- read_csv(here("data", "Final data.csv")) %>%
-    mutate_at(c(2:9, 41:43, 45:48), as.factor) %>%
-    clean_names() %>%
+  data <- read_csv(here("data", "Final data.csv")) |>
+    mutate_at(c(2:9, 41:43, 45:48), as.factor) |>
+    clean_names() |>
 
     # Convert SE to SD
     mutate(
@@ -14,7 +14,7 @@ read_prepare_data <- function(file) {
                                      post_se_st * sqrt(n_st), post_sd_st)),
       post_sd_con = replace_na(if_else(is.na(post_sd_con),
                                       post_se_con * sqrt(n_con), post_sd_con))
-    ) %>%
+    ) |>
 
     # Add in pre-post correlations
     mutate(
@@ -54,7 +54,7 @@ read_prepare_data <- function(file) {
       ri_st = replace_na(ri_st, 0.7),
       ri_con = replace_na(ri_con, 0.7)
 
-    )  %>%
+    )  |>
 
     # add calculation of pooled baseline standard deviations
     mutate(pre_sd_pool = sqrt(((n_st - 1) * pre_sd_st ^ 2 +
@@ -64,19 +64,19 @@ read_prepare_data <- function(file) {
     post_sd_pool = sqrt(((n_st - 1) * post_sd_st ^ 2 +
                            (n_con - 1) * post_sd_con ^ 2
     ) /
-      (n_st + n_con - 2))) %>%
+      (n_st + n_con - 2))) |>
 
     # Formatting variables for moderator models
     unite(c("selftalk_content", "motor_demands"), col="matching", sep = "/",
-          remove = FALSE) %>%
+          remove = FALSE) |>
 
 
     separate(novelty, into=c("selftalk_novelty1", "task_novelty1"), sep = '\\s*and\\s*',
-             remove = FALSE) %>%
+             remove = FALSE) |>
     separate(novelty, into=c("selftalk_novelty2", "task_novelty2"), sep = '\\s*but\\s*',
-             remove = FALSE) %>%
-    mutate(task_novelty = if_else(task_novelty2 == "with the sport", "Learned", "Novel", missing = "Novel")) %>%
-    select(-selftalk_novelty1, -selftalk_novelty2, -task_novelty1, -task_novelty2) %>%
+             remove = FALSE) |>
[…]

### 2024-07-23 R/test_script.R

@@ -1,1074 +1,0 @@
-library(metafor)
-library(orchaRd)
-library(tidyverse)
-library(brms)
-library(modelr)
-library(tidybayes)
-library(bayesplot)
-library(rstan)
-library(ggridges)
-library(patchwork)
-
-data <- read.csv("data/Final data.csv")
-
-data <- data %>%
-  mutate(
-    # Convert p to t (Change scores)
-    delta_t_value_st = replace_na(qt(delta_p_value_st/2, df=n_st-1, lower.tail=FALSE)),
-    delta_t_value_con = replace_na(qt(delta_p_value_con/2, df=n_con-1, lower.tail=FALSE)),
-
-    # Convert t to SE (Change scores)
-    delta_se_st = replace_na(if_else(is.na(delta_m_st),
-                                    (post_m_st - pre_m_st)/delta_t_value_st, delta_m_st/delta_t_value_st)),
-    delta_se_con = replace_na(if_else(is.na(delta_m_con),
-                                    (post_m_con - pre_m_con)/delta_t_value_con, delta_m_con/delta_t_value_con)),
-
-    # Make positive
-    delta_se_st = if_else(delta_se_st < 0, delta_se_st * -1, delta_se_st),
-    delta_se_con = if_else(delta_se_con < 0, delta_se_con * -1, delta_se_con),
-
-    # Convert SE to SD (Change scores)
-    delta_sd_st = replace_na(delta_se_st * sqrt(n_st)),
-    delta_sd_con = replace_na(delta_se_con * sqrt(n_con)),
-
-    # Add missing deltas
-    delta_m_st = replace_na(post_m_st - pre_m_st),
-    delta_m_con = replace_na(post_m_con - pre_m_con),
-
-    # Calculate pre-post correlation coefficient for those with pre, post, and delta SDs
-    ri_st = replace_na((pre_sd_st^2 + post_sd_st^2 - delta_sd_st^2)/(2 * pre_sd_st * post_sd_st)),
-    ri_con = replace_na((pre_sd_con^2 + post_sd_con^2 - delta_sd_con^2)/(2 * pre_sd_con * post_sd_con)),
-
-    # Remove values outside the range of -1 to +1 as they are likely due to misreporting or miscalculations in original studies
-    ri_st = if_else(between(ri_st,-1,1) == FALSE, NA, ri_st),
-    ri_con = if_else(between(ri_con,-1,1) == FALSE, NA, ri_con),
-
[…]

### 2024-07-23 _targets.R

@@ -1,14 +1,17 @@
 # _targets.R file
 library(targets)
 library(tarchetypes)
-library(future)
-library(future.callr)
-plan(callr)
+# library(crew)
 source("R/functions.R")
 tar_option_set(
+  memory = "transient",
+  format = "qs",
+  garbage_collection = TRUE,
+  storage = "worker",
+  retrieval = "worker",
+  controller = crew::crew_controller_local(workers = 2, launch_max = 10),
   packages = c(
     "here",
-    # "readxl",
     "metafor",
     "brms",
     "modelr",
@@ -23,8 +26,11 @@ tar_option_set(
     "furrr",
     "patchwork",
     "marginaleffects",
-    "broom.mixed"
-    )
+    "broom.mixed",
+    # "RoBMA",
+    "future",
+    "faux"
+  )
 )
 
 list(
@@ -35,6 +41,10 @@ list(
 
   # Setup rstan to run chains in parallel
   tar_target(rstan, rstan_setup()),
+
+  # # Simulation of additional new study
+  # tar_target(additional_study_sims, additional_new_study_sim()),
+  # tar_target(additional_study_sims_plot, plot_additional_new_study_sims(additional_study_sims)),
 
   # Fit, check, and plot main model
   tar_target(main_prior, set_main_prior()),
@@ -50,7 +60,16 @@ list(
   tar_target(main_model_plot, plot_panel_main_model(main_model_forest_plot,main_model_update_plot,BF_curve_main_model_plot)),
   tar_target(tidy_main_model, get_tidy_model(main_model)),
 
-  # Fit, check, and plot motor demands model
+  # # # Small study/Publication bias for main model
+  # tar_target(pet_model, fit_pet_model(data_effect_sizes)),
+  # tar_target(tidy_pet_model, tidy(pet_model, conf.int = .95)),
+  # tar_target(rma.mv_model, fit_rma.mv_model(data_effect_sizes)),
+  # tar_target(tidy_rma.mv_model, tidy(rma.mv_model, conf.int = .95)),
+  # tar_target(main_model_contour_funnel_plot, plot_contour_funnel(data_effect_sizes, tidy_rma.mv_model, pet_model, tidy_pet_model)),
+  # tar_target(null_robma_model, fit_null_robma_model(data_effect_sizes)),
+  # tar_target(prior_robma_model, fit_prior_robma_model(data_effect_sizes)),
+  #
+  # # Fit, check, and plot motor demands model
   tar_target(motor_demands_prior, set_motor_demands_prior()),
[…]

### 2024-07-23 _targets_packages.R

@@ -1,25 +1,0 @@
-# Generated by targets::tar_renv(): do not edit by hand
-library(base)
-library(bayesplot)
-library(brms)
-library(bs4Dash)
-library(clustermq)
-library(future)
-library(ggridges)
-library(gt)
-library(here)
-library(janitor)
-library(markdown)
-library(metafor)
-library(modelr)
-library(orchaRd)
-library(patchwork)
-library(pingr)
-library(rstan)
-library(rstudioapi)
-library(shiny)
-library(shinyWidgets)
-library(shinybusy)
-library(tidybayes)
-library(tidyverse)
-library(visNetwork)

### 2024-07-23 R/functions.R
Delete targets and start again - chunking pipeline running bit by bit

@@ -252,7 +252,7 @@ get_logBF_curve <- function(model) {
                       BF = bayesfactor_parameters(model, null = .x)))
   })
 
-  plan(sequential)
+
 
   return(BF_curve)
 }
@@ -279,7 +279,7 @@ set_main_prior <- function() {
 
 sample_prior_main_model <- function(data, prior) {
 
-  plan(multisession, workers = 4)
+
 
   prior_main_model <-
     brm(
@@ -287,7 +287,7 @@ sample_prior_main_model <- function(data, prior) {
       data = data,
       prior = prior,
       chains = 4,
-      # cores = 4,
+      cores = 4,
       future = TRUE,
       seed = 1988,
       warmup = 2000,
@@ -296,7 +296,7 @@ sample_prior_main_model <- function(data, prior) {
       sample_prior = "only",
     )
 
-  plan(sequential)
+
 
   prior_main_model
 }
@@ -674,7 +674,7 @@ sample_prior_study_design_model <- function(data, prior) {
 #     mutate(analysis = future_pmap(., sim)) %>% # not sure why base pipe doesn't work here
 #     unnest(analysis)
 #
-#   plan(sequential)
+#
 #
 #   sims
 # }
@@ -699,7 +699,7 @@ sample_prior_study_design_model <- function(data, prior) {
 # Models
 fit_main_model <- function(data, prior) {
 
-  plan(multisession, workers = 4)
+
 
   main_model <-
     brm(
@@ -707,7 +707,7 @@ fit_main_model <- function(data, prior) {
       data = data,
       prior = prior,
       chains = 4,
-      # cores = 4,
+      cores = 4,
       future = TRUE,
       seed = 1988,
       warmup = 4000,
@@ -715,7 +715,7 @@ fit_main_model <- function(data, prior) {
       control = list(adapt_delta = 0.99)
     )
 
-  plan(sequential)
+
 
   main_model
 }

### 2024-07-23 _targets.R
Pipeline from scratch - fit, check and plot main model

@@ -1,7 +1,7 @@
 # _targets.R file
 library(targets)
 library(tarchetypes)
-# library(crew)
+library(crew)
 source("R/functions.R")
 tar_option_set(
   memory = "transient",
@@ -9,7 +9,7 @@ tar_option_set(
   garbage_collection = TRUE,
   storage = "worker",
   retrieval = "worker",
-  controller = crew::crew_controller_local(workers = 2, launch_max = 10),
+  controller = crew_controller_local(workers = 2, launch_max = 10),
   packages = c(
     "here",
     "metafor",
@@ -58,7 +58,7 @@ list(
   tar_target(main_model_update_plot, plot_main_model_update(prior_main_model, main_model)),
   tar_target(BF_curve_main_model_plot, plot_BF_curve_main_model(main_model_logBF_curve)),
   tar_target(main_model_plot, plot_panel_main_model(main_model_forest_plot,main_model_update_plot,BF_curve_main_model_plot)),
-  tar_target(tidy_main_model, get_tidy_model(main_model)),
+  tar_target(tidy_main_model, get_tidy_model(main_model))
 
   # # # Small study/Publication bias for main model
   # tar_target(pet_model, fit_pet_model(data_effect_sizes)),
@@ -69,27 +69,27 @@ list(
   # tar_target(null_robma_model, fit_null_robma_model(data_effect_sizes)),
   # tar_target(prior_robma_model, fit_prior_robma_model(data_effect_sizes)),
   #
-  # # Fit, check, and plot motor demands model
-  tar_target(motor_demands_prior, set_motor_demands_prior()),
-  tar_target(prior_motor_demands_model, sample_prior_motor_demands_model(data_effect_sizes, motor_demands_prior)),
-  tar_target(motor_demands_model, fit_motor_demands_model(data_effect_sizes, motor_demands_prior)),
-  tar_target(rhat_motor_demands_model, make_rhat_plot(motor_demands_model)),
-  tar_target(trace_plot_motor_demands_model, make_trace_plot(motor_demands_model)),
-  tar_target(pp_check_motor_demands_model, make_pp_check(motor_demands_model)),
-  tar_target(motor_demands_model_plot, plot_motor_demands_model(data_effect_sizes, prior_motor_demands_model, motor_demands_model)),
-  tar_target(motor_demands_model_logBF_curve, get_logBF_curve(motor_demands_model)),
-  tar_target(tidy_motor_demands_model, get_tidy_model(motor_demands_model)),
-
[…]

### 2024-07-23 _targets.R
Motor demands model fit, check, and plot

@@ -58,7 +58,7 @@ list(
   tar_target(main_model_update_plot, plot_main_model_update(prior_main_model, main_model)),
   tar_target(BF_curve_main_model_plot, plot_BF_curve_main_model(main_model_logBF_curve)),
   tar_target(main_model_plot, plot_panel_main_model(main_model_forest_plot,main_model_update_plot,BF_curve_main_model_plot)),
-  tar_target(tidy_main_model, get_tidy_model(main_model))
+  tar_target(tidy_main_model, get_tidy_model(main_model)),
 
   # # # Small study/Publication bias for main model
   # tar_target(pet_model, fit_pet_model(data_effect_sizes)),
@@ -68,28 +68,28 @@ list(
   # tar_target(main_model_contour_funnel_plot, plot_contour_funnel(data_effect_sizes, tidy_rma.mv_model, pet_model, tidy_pet_model)),
   # tar_target(null_robma_model, fit_null_robma_model(data_effect_sizes)),
   # tar_target(prior_robma_model, fit_prior_robma_model(data_effect_sizes)),
-  #
-  # # # Fit, check, and plot motor demands model
-  # tar_target(motor_demands_prior, set_motor_demands_prior()),
-  # tar_target(prior_motor_demands_model, sample_prior_motor_demands_model(data_effect_sizes, motor_demands_prior)),
-  # tar_target(motor_demands_model, fit_motor_demands_model(data_effect_sizes, motor_demands_prior)),
-  # tar_target(rhat_motor_demands_model, make_rhat_plot(motor_demands_model)),
-  # tar_target(trace_plot_motor_demands_model, make_trace_plot(motor_demands_model)),
-  # tar_target(pp_check_motor_demands_model, make_pp_check(motor_demands_model)),
-  # tar_target(motor_demands_model_plot, plot_motor_demands_model(data_effect_sizes, prior_motor_demands_model, motor_demands_model)),
-  # tar_target(motor_demands_model_logBF_curve, get_logBF_curve(motor_demands_model)),
-  # tar_target(tidy_motor_demands_model, get_tidy_model(motor_demands_model)),
-  #
-  # # Fit, check, and plot participant group model
-  # tar_target(participant_group_prior, set_participant_group_prior()),
-  # tar_target(prior_participant_group_model, sample_prior_participant_group_model(data_effect_sizes, participant_group_prior)),
-  # tar_target(participant_group_model, fit_participant_group_model(data_effect_sizes, participant_group_prior)),
[…]

### 2024-07-24 _targets.R
Fit, check, and plot self-talk content model

@@ -89,18 +89,18 @@ list(
   tar_target(pp_check_participant_group_model, make_pp_check(participant_group_model)),
   tar_target(participant_group_model_plot, plot_participant_group_model(data_effect_sizes, prior_participant_group_model, participant_group_model)),
   tar_target(participant_group_model_logBF_curve, get_logBF_curve(participant_group_model)),
-  tar_target(tidy_participant_group_model, get_tidy_model(participant_group_model))
+  tar_target(tidy_participant_group_model, get_tidy_model(participant_group_model)),
 
-  # # Fit, check, and plot self-talk content model
-  # tar_target(selftalk_content_prior, set_selftalk_content_prior()),
-  # tar_target(prior_selftalk_content_model, sample_prior_selftalk_content_model(data_effect_sizes, selftalk_content_prior)),
-  # tar_target(selftalk_content_model, fit_selftalk_content_model(data_effect_sizes, selftalk_content_prior)),
-  # tar_target(rhat_selftalk_content_model, make_rhat_plot(selftalk_content_model)),
-  # tar_target(trace_plot_selftalk_content_model, make_trace_plot(selftalk_content_model)),
-  # tar_target(pp_check_selftalk_content_model, make_pp_check(selftalk_content_model)),
-  # tar_target(selftalk_content_model_plot, plot_selftalk_content_model(data_effect_sizes, prior_selftalk_content_model, selftalk_content_model)),
-  # tar_target(selftalk_content_model_logBF_curve, get_logBF_curve(selftalk_content_model)),
-  # tar_target(tidy_selftalk_content_model, get_tidy_model(selftalk_content_model))
+  # Fit, check, and plot self-talk content model
+  tar_target(selftalk_content_prior, set_selftalk_content_prior()),
+  tar_target(prior_selftalk_content_model, sample_prior_selftalk_content_model(data_effect_sizes, selftalk_content_prior)),
+  tar_target(selftalk_content_model, fit_selftalk_content_model(data_effect_sizes, selftalk_content_prior)),
+  tar_target(rhat_selftalk_content_model, make_rhat_plot(selftalk_content_model)),
+  tar_target(trace_plot_selftalk_content_model, make_trace_plot(selftalk_content_model)),
+  tar_target(pp_check_selftalk_content_model, make_pp_check(selftalk_content_model)),
[…]

### 2024-07-24 _targets.R
Fit, check, and plot matching hypothesis model

@@ -100,18 +100,18 @@ list(
   tar_target(pp_check_selftalk_content_model, make_pp_check(selftalk_content_model)),
   tar_target(selftalk_content_model_plot, plot_selftalk_content_model(data_effect_sizes, prior_selftalk_content_model, selftalk_content_model)),
   tar_target(selftalk_content_model_logBF_curve, get_logBF_curve(selftalk_content_model)),
-  tar_target(tidy_selftalk_content_model, get_tidy_model(selftalk_content_model))
+  tar_target(tidy_selftalk_content_model, get_tidy_model(selftalk_content_model)),
 
-  # # Fit, check, and plot matching hypothesis model
-  # tar_target(matching_prior, set_matching_prior()),
-  # tar_target(prior_matching_model, sample_prior_matching_model(data_effect_sizes, matching_prior)),
-  # tar_target(matching_model, fit_matching_model(data_effect_sizes, matching_prior)),
-  # tar_target(rhat_matching_model, make_rhat_plot(matching_model)),
-  # tar_target(trace_plot_matching_model, make_trace_plot(matching_model)),
-  # tar_target(pp_check_matching_model, make_pp_check(matching_model)),
-  # # tar_target(matching_model_plot, plot_matching_model(data_effect_sizes, prior_matching_model, matching_model)),
-  # # tar_target(matching_model_logBF_curve, get_logBF_curve(matching_model)),
-  # tar_target(tidy_matching_model, get_tidy_model(matching_model)),
+  # Fit, check, and plot matching hypothesis model
+  tar_target(matching_prior, set_matching_prior()),
+  tar_target(prior_matching_model, sample_prior_matching_model(data_effect_sizes, matching_prior)),
+  tar_target(matching_model, fit_matching_model(data_effect_sizes, matching_prior)),
+  tar_target(rhat_matching_model, make_rhat_plot(matching_model)),
+  tar_target(trace_plot_matching_model, make_trace_plot(matching_model)),
+  tar_target(pp_check_matching_model, make_pp_check(matching_model)),
+  tar_target(matching_model_plot, plot_matching_model(data_effect_sizes, prior_matching_model, matching_model)),
+  tar_target(matching_model_logBF_curve, get_logBF_curve(matching_model)),
+  tar_target(tidy_matching_model, get_tidy_model(matching_model))
   #
   # # Fit, check, and plot task_novelty model
   # tar_target(task_novelty_prior, set_task_novelty_prior()),

### 2024-07-24 _targets.R
Fit, check, and plot task_novelty model

@@ -111,18 +111,18 @@ list(
   tar_target(pp_check_matching_model, make_pp_check(matching_model)),
   tar_target(matching_model_plot, plot_matching_model(data_effect_sizes, prior_matching_model, matching_model)),
   tar_target(matching_model_logBF_curve, get_logBF_curve(matching_model)),
-  tar_target(tidy_matching_model, get_tidy_model(matching_model))
-  #
-  # # Fit, check, and plot task_novelty model
-  # tar_target(task_novelty_prior, set_task_novelty_prior()),
-  # tar_target(prior_task_novelty_model, sample_prior_task_novelty_model(data_effect_sizes, task_novelty_prior)),
-  # tar_target(task_novelty_model, fit_task_novelty_model(data_effect_sizes, task_novelty_prior)),
-  # tar_target(rhat_task_novelty_model, make_rhat_plot(task_novelty_model)),
-  # tar_target(trace_plot_task_novelty_model, make_trace_plot(task_novelty_model)),
-  # tar_target(pp_check_task_novelty_model, make_pp_check(task_novelty_model)),
-  # # tar_target(task_novelty_model_plot, plot_task_novelty_model(data_effect_sizes, prior_task_novelty_model, task_novelty_model)),
-  # # tar_target(task_novelty_model_logBF_curve, get_logBF_curve(task_novelty_model)),
-  # tar_target(tidy_task_novelty_model, get_tidy_model(task_novelty_model)),
+  tar_target(tidy_matching_model, get_tidy_model(matching_model)),
+
+  # Fit, check, and plot task_novelty model
+  tar_target(task_novelty_prior, set_task_novelty_prior()),
+  tar_target(prior_task_novelty_model, sample_prior_task_novelty_model(data_effect_sizes, task_novelty_prior)),
+  tar_target(task_novelty_model, fit_task_novelty_model(data_effect_sizes, task_novelty_prior)),
+  tar_target(rhat_task_novelty_model, make_rhat_plot(task_novelty_model)),
+  tar_target(trace_plot_task_novelty_model, make_trace_plot(task_novelty_model)),
+  tar_target(pp_check_task_novelty_model, make_pp_check(task_novelty_model)),
+  tar_target(task_novelty_model_plot, plot_task_novelty_model(data_effect_sizes, prior_task_novelty_model, task_novelty_model)),
+  tar_target(task_novelty_model_logBF_curve, get_logBF_curve(task_novelty_model)),
[…]

### 2024-07-24 _targets.R
Fit, check, and plot cue_selection model

@@ -122,18 +122,18 @@ list(
   tar_target(pp_check_task_novelty_model, make_pp_check(task_novelty_model)),
   tar_target(task_novelty_model_plot, plot_task_novelty_model(data_effect_sizes, prior_task_novelty_model, task_novelty_model)),
   tar_target(task_novelty_model_logBF_curve, get_logBF_curve(task_novelty_model)),
-  tar_target(tidy_task_novelty_model, get_tidy_model(task_novelty_model))
-  #
-  # # Fit, check, and plot cue_selection model
-  # tar_target(cue_selection_prior, set_cue_selection_prior()),
-  # tar_target(prior_cue_selection_model, sample_prior_cue_selection_model(data_effect_sizes, cue_selection_prior)),
-  # tar_target(cue_selection_model, fit_cue_selection_model(data_effect_sizes, cue_selection_prior)),
-  # tar_target(rhat_cue_selection_model, make_rhat_plot(cue_selection_model)),
-  # tar_target(trace_plot_cue_selection_model, make_trace_plot(cue_selection_model)),
-  # tar_target(pp_check_cue_selection_model, make_pp_check(cue_selection_model)),
-  # # tar_target(cue_selection_model_plot, plot_cue_selection_model(data_effect_sizes, prior_cue_selection_model, cue_selection_model)),
-  # # tar_target(cue_selection_model_logBF_curve, get_logBF_curve(cue_selection_model)),
-  # tar_target(tidy_cue_selection_model, get_tidy_model(cue_selection_model)),
+  tar_target(tidy_task_novelty_model, get_tidy_model(task_novelty_model)),
+
+  # Fit, check, and plot cue_selection model
+  tar_target(cue_selection_prior, set_cue_selection_prior()),
+  tar_target(prior_cue_selection_model, sample_prior_cue_selection_model(data_effect_sizes, cue_selection_prior)),
+  tar_target(cue_selection_model, fit_cue_selection_model(data_effect_sizes, cue_selection_prior)),
+  tar_target(rhat_cue_selection_model, make_rhat_plot(cue_selection_model)),
+  tar_target(trace_plot_cue_selection_model, make_trace_plot(cue_selection_model)),
+  tar_target(pp_check_cue_selection_model, make_pp_check(cue_selection_model)),
+  tar_target(cue_selection_model_plot, plot_cue_selection_model(data_effect_sizes, prior_cue_selection_model, cue_selection_model)),
[…]

### 2024-07-24 _targets.R
Fit, check, and plot overtness_selection model

@@ -133,18 +133,18 @@ list(
   tar_target(pp_check_cue_selection_model, make_pp_check(cue_selection_model)),
   tar_target(cue_selection_model_plot, plot_cue_selection_model(data_effect_sizes, prior_cue_selection_model, cue_selection_model)),
   tar_target(cue_selection_model_logBF_curve, get_logBF_curve(cue_selection_model)),
-  tar_target(tidy_cue_selection_model, get_tidy_model(cue_selection_model))
-  #
-  # # Fit, check, and plot overtness_selection model
-  # tar_target(overtness_selection_prior, set_overtness_selection_prior()),
-  # tar_target(prior_overtness_selection_model, sample_prior_overtness_selection_model(data_effect_sizes, overtness_selection_prior)),
-  # tar_target(overtness_selection_model, fit_overtness_selection_model(data_effect_sizes, overtness_selection_prior)),
-  # tar_target(rhat_overtness_selection_model, make_rhat_plot(overtness_selection_model)),
-  # tar_target(trace_plot_overtness_selection_model, make_trace_plot(overtness_selection_model)),
-  # tar_target(pp_check_overtness_selection_model, make_pp_check(overtness_selection_model)),
-  # # tar_target(overtness_selection_model_plot, plot_overtness_selection_model(data_effect_sizes, prior_overtness_selection_model, overtness_selection_model)),
-  # # tar_target(overtness_selection_model_logBF_curve, get_logBF_curve(overtness_selection_model)),
-  # tar_target(tidy_overtness_selection_model, get_tidy_model(overtness_selection_model)),
+  tar_target(tidy_cue_selection_model, get_tidy_model(cue_selection_model)),
+
+  # Fit, check, and plot overtness_selection model
+  tar_target(overtness_selection_prior, set_overtness_selection_prior()),
+  tar_target(prior_overtness_selection_model, sample_prior_overtness_selection_model(data_effect_sizes, overtness_selection_prior)),
+  tar_target(overtness_selection_model, fit_overtness_selection_model(data_effect_sizes, overtness_selection_prior)),
+  tar_target(rhat_overtness_selection_model, make_rhat_plot(overtness_selection_model)),
+  tar_target(trace_plot_overtness_selection_model, make_trace_plot(overtness_selection_model)),
+  tar_target(pp_check_overtness_selection_model, make_pp_check(overtness_selection_model)),
[…]

### 2024-07-24 _targets.R
Fit, check, and plot training model

@@ -144,18 +144,18 @@ list(
   tar_target(pp_check_overtness_selection_model, make_pp_check(overtness_selection_model)),
   tar_target(overtness_selection_model_plot, plot_overtness_selection_model(data_effect_sizes, prior_overtness_selection_model, overtness_selection_model)),
   tar_target(overtness_selection_model_logBF_curve, get_logBF_curve(overtness_selection_model)),
-  tar_target(tidy_overtness_selection_model, get_tidy_model(overtness_selection_model))
-  #
-  # # Fit, check, and plot training model
-  # tar_target(training_prior, set_training_prior()),
-  # tar_target(prior_training_model, sample_prior_training_model(data_effect_sizes, training_prior)),
-  # tar_target(training_model, fit_training_model(data_effect_sizes, training_prior)),
-  # tar_target(rhat_training_model, make_rhat_plot(training_model)),
-  # tar_target(trace_plot_training_model, make_trace_plot(training_model)),
-  # tar_target(pp_check_training_model, make_pp_check(training_model)),
-  # # tar_target(training_model_plot, plot_training_model(data_effect_sizes, prior_training_model, training_model)),
-  # # tar_target(training_model_logBF_curve, get_logBF_curve(training_model)),
-  # tar_target(tidy_training_model, get_tidy_model(training_model)),
+  tar_target(tidy_overtness_selection_model, get_tidy_model(overtness_selection_model)),
+
+  # Fit, check, and plot training model
+  tar_target(training_prior, set_training_prior()),
+  tar_target(prior_training_model, sample_prior_training_model(data_effect_sizes, training_prior)),
+  tar_target(training_model, fit_training_model(data_effect_sizes, training_prior)),
+  tar_target(rhat_training_model, make_rhat_plot(training_model)),
+  tar_target(trace_plot_training_model, make_trace_plot(training_model)),
+  tar_target(pp_check_training_model, make_pp_check(training_model)),
+  tar_target(training_model_plot, plot_training_model(data_effect_sizes, prior_training_model, training_model)),
+  tar_target(training_model_logBF_curve, get_logBF_curve(training_model)),
+  tar_target(tidy_training_model, get_tidy_model(training_model))
   #
   # # Fit, check, and plot study_design model
   # tar_target(study_design_prior, set_study_design_prior()),

### 2024-07-25 _targets.R
Fit, check, and plot study_design model

@@ -155,18 +155,18 @@ list(
   tar_target(pp_check_training_model, make_pp_check(training_model)),
   tar_target(training_model_plot, plot_training_model(data_effect_sizes, prior_training_model, training_model)),
   tar_target(training_model_logBF_curve, get_logBF_curve(training_model)),
-  tar_target(tidy_training_model, get_tidy_model(training_model))
-  #
-  # # Fit, check, and plot study_design model
-  # tar_target(study_design_prior, set_study_design_prior()),
-  # tar_target(prior_study_design_model, sample_prior_study_design_model(data_effect_sizes, study_design_prior)),
-  # tar_target(study_design_model, fit_study_design_model(data_effect_sizes, study_design_prior)),
-  # tar_target(rhat_study_design_model, make_rhat_plot(study_design_model)),
-  # tar_target(trace_plot_study_design_model, make_trace_plot(study_design_model)),
-  # tar_target(pp_check_study_design_model, make_pp_check(study_design_model)),
-  # # tar_target(study_design_model_plot, plot_study_design_model(data_effect_sizes, prior_study_design_model, study_design_model)),
-  # # tar_target(study_design_model_logBF_curve, get_logBF_curve(study_design_model)),
-  # tar_target(tidy_study_design_model, get_tidy_model(study_design_model))
+  tar_target(tidy_training_model, get_tidy_model(training_model)),
+
+  # Fit, check, and plot study_design model
+  tar_target(study_design_prior, set_study_design_prior()),
+  tar_target(prior_study_design_model, sample_prior_study_design_model(data_effect_sizes, study_design_prior)),
+  tar_target(study_design_model, fit_study_design_model(data_effect_sizes, study_design_prior)),
+  tar_target(rhat_study_design_model, make_rhat_plot(study_design_model)),
+  tar_target(trace_plot_study_design_model, make_trace_plot(study_design_model)),
+  tar_target(pp_check_study_design_model, make_pp_check(study_design_model)),
+  tar_target(study_design_model_plot, plot_study_design_model(data_effect_sizes, prior_study_design_model, study_design_model)),
+  tar_target(study_design_model_logBF_curve, get_logBF_curve(study_design_model)),
+  tar_target(tidy_study_design_model, get_tidy_model(study_design_model))
 
   # # Make panel plot of moderators
   # tar_target(moderators_panel_plot, plot_panel_moderators(

### 2024-07-25 _targets.R
PET-PEESE, contour plot, main model plot, and BF curve plots

@@ -60,12 +60,12 @@ list(
   tar_target(main_model_plot, plot_panel_main_model(main_model_forest_plot,main_model_update_plot,BF_curve_main_model_plot)),
   tar_target(tidy_main_model, get_tidy_model(main_model)),
 
-  # # # Small study/Publication bias for main model
-  # tar_target(pet_model, fit_pet_model(data_effect_sizes)),
-  # tar_target(tidy_pet_model, tidy(pet_model, conf.int = .95)),
-  # tar_target(rma.mv_model, fit_rma.mv_model(data_effect_sizes)),
-  # tar_target(tidy_rma.mv_model, tidy(rma.mv_model, conf.int = .95)),
-  # tar_target(main_model_contour_funnel_plot, plot_contour_funnel(data_effect_sizes, tidy_rma.mv_model, pet_model, tidy_pet_model)),
+  # # Small study/Publication bias for main model
+  tar_target(pet_model, fit_pet_model(data_effect_sizes)),
+  tar_target(tidy_pet_model, tidy(pet_model, conf.int = .95)),
+  tar_target(rma.mv_model, fit_rma.mv_model(data_effect_sizes)),
+  tar_target(tidy_rma.mv_model, tidy(rma.mv_model, conf.int = .95)),
+  tar_target(main_model_contour_funnel_plot, plot_contour_funnel(data_effect_sizes, tidy_rma.mv_model, pet_model, tidy_pet_model)),
   # tar_target(null_robma_model, fit_null_robma_model(data_effect_sizes)),
   # tar_target(prior_robma_model, fit_prior_robma_model(data_effect_sizes)),
 
@@ -166,7 +166,7 @@ list(
   tar_target(pp_check_study_design_model, make_pp_check(study_design_model)),
   tar_target(study_design_model_plot, plot_study_design_model(data_effect_sizes, prior_study_design_model, study_design_model)),
   tar_target(study_design_model_logBF_curve, get_logBF_curve(study_design_model)),
-  tar_target(tidy_study_design_model, get_tidy_model(study_design_model))
+  tar_target(tidy_study_design_model, get_tidy_model(study_design_model)),
 
   # # Make panel plot of moderators
   # tar_target(moderators_panel_plot, plot_panel_moderators(
@@ -174,36 +174,36 @@ list(
[…]

### 2024-07-25 R/functions.R
Cumulative models and plot

@@ -878,7 +878,7 @@ fit_cumulative_main_model <- function(data) {
 
   # Create empty data frame for draws
   cumulative_draws <- data.frame(year = as.numeric(),
-                                  b_Intercept = as.numeric,
+                                  b_Intercept = as.numeric(),
                                  prior = as.character())
 
   # Initial posterior as prior

### 2024-07-25 _targets.R

@@ -186,10 +186,10 @@ list(
   tar_target(BF_curve_training_plot, plot_BF_curve_training(training_model_logBF_curve)),
   tar_target(BF_curve_study_design_plot, plot_BF_curve_study_design(study_design_model_logBF_curve)),
 
-  # # Make cumulative model and plot
-  # tar_target(cumulative_draws, fit_cumulative_main_model(data_effect_sizes)),
-  # tar_target(cumulative_main_model_plot, plot_cumulative_main_model(data_effect_sizes, prior_main_model, cumulative_draws)),
-  #
+  # Make cumulative model and plot
+  tar_target(cumulative_draws, fit_cumulative_main_model(data_effect_sizes)),
+  tar_target(cumulative_main_model_plot, plot_cumulative_main_model(data_effect_sizes, prior_main_model, cumulative_draws)),
+
   # Make plots tiffs
   # tar_target(additional_study_sims_plot_tiff, make_plot_tiff(additional_study_sims_plot, 7.5, 13.33, "plots/additional_study_sims_plot.tiff")),
   tar_target(main_model_plot_tiff, make_plot_tiff(main_model_plot, 7.5, 13.33, "plots/main_model_plot.tiff")),
@@ -203,7 +203,7 @@ list(
   tar_target(BF_curve_cue_selection_plot_tiff, make_plot_tiff(BF_curve_cue_selection_plot, 7.5, 5, "plots/BF_curve_cue_selection_plot.tiff")),
   tar_target(BF_curve_overtness_selection_plot_tiff, make_plot_tiff(BF_curve_overtness_selection_plot, 7.5, 5, "plots/BF_curve_overtness_selection_plot.tiff")),
   tar_target(BF_curve_training_plot_tiff, make_plot_tiff(BF_curve_training_plot, 7.5, 5, "plots/BF_curve_training_plot.tiff")),
-  tar_target(BF_curve_study_design_plot_tiff, make_plot_tiff(BF_curve_study_design_plot, 7.5, 5, "plots/BF_curve_study_design_plot.tiff"))
-  # tar_target(cumulative_main_model_plot_tiff, make_plot_tiff(cumulative_main_model_plot, 7.5, 5, "plots/cumulative_main_model_plot.tiff"))
+  tar_target(BF_curve_study_design_plot_tiff, make_plot_tiff(BF_curve_study_design_plot, 7.5, 5, "plots/BF_curve_study_design_plot.tiff")),
[…]

### 2024-07-25 _targets.R
null_robma_model

@@ -66,7 +66,7 @@ list(
   tar_target(rma.mv_model, fit_rma.mv_model(data_effect_sizes)),
   tar_target(tidy_rma.mv_model, tidy(rma.mv_model, conf.int = .95)),
   tar_target(main_model_contour_funnel_plot, plot_contour_funnel(data_effect_sizes, tidy_rma.mv_model, pet_model, tidy_pet_model)),
-  # tar_target(null_robma_model, fit_null_robma_model(data_effect_sizes)),
+  tar_target(null_robma_model, fit_null_robma_model(data_effect_sizes)),
   # tar_target(prior_robma_model, fit_prior_robma_model(data_effect_sizes)),
 
   # # Fit, check, and plot motor demands model

### 2024-07-25 _targets.R
prior_robma_model

@@ -67,7 +67,7 @@ list(
   tar_target(tidy_rma.mv_model, tidy(rma.mv_model, conf.int = .95)),
   tar_target(main_model_contour_funnel_plot, plot_contour_funnel(data_effect_sizes, tidy_rma.mv_model, pet_model, tidy_pet_model)),
   tar_target(null_robma_model, fit_null_robma_model(data_effect_sizes)),
-  # tar_target(prior_robma_model, fit_prior_robma_model(data_effect_sizes)),
+  tar_target(prior_robma_model, fit_prior_robma_model(data_effect_sizes)),
 
   # # Fit, check, and plot motor demands model
   tar_target(motor_demands_prior, set_motor_demands_prior()),

### 2024-07-29 pre_print_manuscript.qmd
Additional study sims

@@
 
-https://www.thelancet.com/journals/lancet/article/PIIS0140-6736(15)00489-4/fulltext
-
-https://www.thelancet.com/journals/lancet/article/PIIS0140-6736(15)01354-9/fulltext
-
 https://academic.oup.com/biometrics/article/79/1/319/7478096?login=false
@@
 ## Cumulative evidence synthesis 
-Two questions that should be asked (though arguably are not often enough particularly in sport science) by researchers when planning a study of an experimental intervention is "what is the likelihood that the experimental intervention is superior to the control intervention given the evidence accumulated so far?", and "what is the likelihood that a new trial, given some design parameters and previous evidence, will demonstrate the superiority of the experimental intervention?".
+Two questions that should be asked (though arguably are not asked often enough particularly in sport science) by researchers when planning a study of an experimental intervention is "what is the likelihood that the experimental intervention is superior to the control intervention given the evidence accumulated so far?", and "what is the likelihood that a new trial, given some design parameters and previous evidence, will demonstrate the superiority of the experimental intervention?".
 The key here is to consider the *cumulative* nature of evidence provided by research and its synthesis.
-Indeed, to not do this could lead to so called "research waste".
+Indeed, to not do this could lead to redundancy or so called "research waste".
 Evidence synthesis methods are essential to determining whether or not there is justification for further research on a given topic, and the Cochrane-Collaboration and REWARD (Reduce Research Waste and Reward Diligence) Alliance have even established an award for efforts in the area of reducing "research waste" [@glasziouResearchWasteStill2018].
-
-          Add about QRPs and research waste - evaluate the not only the results, but the quality of the preceding evidence in addition to whether it may have been subject to any bias
+However, across many domains there remains a high prevalence of redundancy and a low prevalence of attempts to minimise or reduce it [@lundMetaresearchEvaluatingRedundancy2022].
 
@@
 Further, Bayesian approaches are well positioned to tackle this [@biauUsingBayesianStatistics2017].
+Within Bayesian statistical inference a prior probability distribution regarding the effect of interest is *updated* after the introduction of new evidence to a posterior probability distribution given Bayes theorem.
 
-Within Bayesian statistical inference a prior probability distribution regarding the effect of interest is *updated* after the introduction of new evidence to a posterior probability distribution given Bayes theorem.
-In the present paper we demonstrate the application of Bayesian methods to meta-analysis in the sport and exercise sciences for the evaluation of experimental interventions using cumulative evidence synthesis.
+The trustworthiness of prior data should also be considered in evidence synthesis.
+Meta-analyses rely on the assumption that the sample of studies included is not based on a biased selection procedure either on the part of the systematic reviewer(s) or with regards to the studies present in the literature to sample from.
+For the latter, publication bias and *p*-hacking are the two most common phenomena that violate this assumption and can substantial influence cumulative evidence [@friesePHackingPublicationBias2020].
+Publication bias is typically explored using methods such as selection models based on significance thresholds for *p*-values [@mcshaneAdjustingPublicationBias2016], funnel plot based regression methods [@stanleyMetaregressionApproximationsReduce2014], or methods which combine these approaches and leverage the uncertainty in the underlying true data generating process such as Robust Bayesian Meta-Analysis with model averaging [@bartosAdjustingPublicationBias2022; @bartosRobustBayesianMetaanalysis2023].
+For *p*-hacking mixture models have recently been proposed [@mossModellingPublicationBias2023].
+The existence of evidence suggesting prior questionable research practices such as publication bias or *p*-hacking in previous literature might be cause for an evaluation of whether a research program regarding an experimental intervention is worth building upon, or starting afresh incorporating safe-guards for such issues e.g., pre-registration/registered-reports [@chambersPresentFutureRegistered2022].
+
+In the present paper we demonstrate the application of methods for cumulative evidence synthesis including Bayesian meta-analysis, and exploration of questionable research practices such as publication bias or *p*-hacking, in the sport and exercise sciences for the evaluation of experimental interventions.
 We assume some prior knowledge of evidence synthesis and meta-analytic methods on the part of the reader, though for those unfamiliar suggest some recent introductory papers regarding their application in the field [@gunnellQuestionsAnswersConducting2020; @haggerMetaanalysis2022; @steeleMetaanalysisVariationSport2023].
 We use the example of self-talk interventions and their effects upon motor/sport performance given a quantitative evidence synthesis has not been conducted on this topic to the best of our knowledge since 2011 when Hatzigeorgiadis et al.
-[-@hatzigeorgiadisSelfTalkSportsPerformance2011] conducted their systematic review and meta-analysis.
+[-@hatzigeorgiadisSelfTalkSportsPerformance2011] conducted their systematic review and meta-analysis, and thus is ripe to use in demonstrating cumulative methods such as Bayesian updating.
+Note, we do not intend to present this paper as a comprehensive systematic review and meta-analysis of self-talk interventions in sport/motor performance nor a thorough theoretical review of the construct.
+We do however present a brief overview of the topic below for context of this as an example.
 
 ## Self-talk interventions
-Sport psychology as a broad field has focused on the theorising of psychological constructs that might impact upon performance, and the subsequent experimental testing of theoretically informed interventions to address these constructs.
+Sport psychology as a broad field has focused on the theorising of psychological constructs that might impact upon performance, and the subsequent experimental testing of theoretically informed interventions to address these constructs and subsequent performance.
 For example, a recent umbrella review identified thirty meta-analyses exploring the effects of different sport psychology constructs upon performance, thirteen of them examining the effects of interventions, finding an overall standardised mean difference (SMD) for positive constructs of 0.51 \[95% confidence interval: 0.42, 0.58\] [@lochbaumSportPsychologyPerformance2022].
@@
 [-@hatzigeorgiadisSelfTalkSportsPerformance2011] might be considered by some to have been already fairly precise only spanning 0.2 SMD, and indeed aswell for many of the moderator estimates.
+Indeed, some authors had moved onto to attempting to explain *why* self-talk interventions are effective, exploring possible mechanisms with the starting assumption that these interventions had been proven as effective for enhancing performance [@galanisChapterWhySelfTalk2016].
 
-Many additional studies on self-talk interventions have been conducted since 2011.
-It may well be that such recent work has improved our estimates of the effects of self-talk interventions and what moderates their effectiveness, or indeed contributed to other areas of understanding of the construct of self-talk.
-But, it is a reasonable question to ask, given the limited time and resource for conducting research in the field of sport science and what we already know regarding these interventions, whether and to what extent these studies have advanced our understanding of their effects, or whether they have largely contributed to so called "research waste" [@graingerEvidenceSynthesisTackling2020; @glasziouResearchWasteStill2018].
+Despite this, many additional studies on self-talk interventions have been conducted since 2011.
+It may well be that such recent work has further improved our estimates of the effects of self-talk interventions and what moderates their effectiveness, or indeed contributed to other areas of understanding of the construct of self-talk.
+But, it is a reasonable question to ask, given the limited time and resource for conducting research in the field of sport science and what we might claim to have already known regarding these interventions, whether and to what extent these studies have advanced our understanding of their effects, or whether they have largely contributed to so called "research waste" [@graingerEvidenceSynthesisTackling2020; @glasziouResearchWasteStill2018].
 
 ## Aim of the present work
-The aim of this present work is to demonstrate the application of Bayesian methods in evidence synthesis, in particular to meta-analysis, in the sport and exercise sciences for the evaluation of experimental interventions.
+The aim of this present work is to demonstrate the application of methods for cumulative evidence synthesis including Bayesian meta-analysis, and exploration of questionable research practices such as publication bias or *p*-hacking, in the sport and exercise sciences for the evaluation of experimental interventions.
 Given that there has not been, to the best of our knowledge, a meta-analytic synthesis of the effects of self-talk interventions effects upon sport/motor performance since Hatzigeorgiadis et al.
@@
 Therefore, our aim was to conduct an updated systematic review and Bayesian meta-analysis replicating the search, inclusion, and models of Hatzigeorgiadis et al.
-[-@hatzigeorgiadisSelfTalkSportsPerformance2011] in order to demonstrate the application of cumulative evidence synthesis methods including; consideration of the initial probability that a new study of the effects of self-talk interventions would shift our prior belief in their effectiveness, the application of priors taken from the previous meta-analysis to be updated by new studies identified to a new posterior estimate of effect, and consideration of other sources of research waste from questionable research practices such as possible publication bias.
+[-@hatzigeorgiadisSelfTalkSportsPerformance2011] in order to demonstrate the application of cumulative evidence synthesis methods including; consideration of the initial probability that a new study of the effects of self-talk interventions would shift our prior belief in their effectiveness, the application of priors taken from the previous meta-analysis to be updated by new studies identified to a new posterior estimate of effect, and consideration of other sources of research waste from questionable research practices such as possible publication bias and *p*-hacking.
 
@@
 
-Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011] did not explicitly state a process or strategy to formulating their research question and search methods.
+Hatzigeorgiadis et al.
+[-@hatzigeorgiadisSelfTalkSportsPerformance2011] did not explicitly state a process or strategy to formulating their research question and search methods.
 However, we assumed that the PICO (Participants, Intervention, Comparator and Outcome) framework was implicitly used and, with that assumption, we adopted the following inclusion criteria based on their description.
@@
 Outcomes were sport or motor task performance.
-We included both between and within group experimental designs with either pre-post, or post-only measurements of performance as well as within group pre-post trials.
+We included both between and within group experimental designs with either pre-post, or post-only measurements of performance as well as within group pre-post trials similarly to Hatzigeorgiadis et al.
+[-@hatzigeorgiadisSelfTalkSportsPerformance2011].
 
@@
 The following databases -- Sport Discus, PsycINFO, PsycARTICLES and Medline -- were selected through the EBSCO database to search for the keywords.
-The SCOPUS database, used by Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011], was not used as it was not accessible through Solent University[^2].
+The SCOPUS database, used by Hatzigeorgiadis et al.
+[-@hatzigeorgiadisSelfTalkSportsPerformance2011], was not used as it was not accessible through Solent University[^2].
 These keywords were searched in the format of, with the application of the Boolean commands, (self-talk OR self-instruction OR self-statements OR self-verbalizations OR verbal cues OR stimulus cueing OR thought content instructions) AND (sport OR performance OR motor performance OR task performance).
@@
 An initial search took place from October 2022-November 2022 as this project was completed as part of the lead authors undergraduate thesis.
-We subsequently updated the search from November 2022-November 2023 prior to preparing this manuscript for publication.
+We subsequently updated the search from November 2022-November 2023 prior to initially preparing this manuscript for publication.
 
@@
 However, for transparency, we encountered an issue where we realised that some of the searches we had conducted were not correctly recorded by the tool being used to manage the process.
-We were, despite attempting to do so, unable to exactly replicate the searches (number of hits from initial search string in databases used) at the time we realised from attempting to reproduce the searches again.
-As such, we do not present a PRISMA diagram though as noted we do feel fairly confident we have not missed any key studies nor that minor omissions would affect the overall results of our analyses.
+We were, despite attempting to do so after realising this, unable to exactly replicate the searches (number of hits from initial search string in databases used) at the time we realised from attempting to reproduce the searches again.
+As such, we do not present a PRISMA diagram though as noted we do feel fairly confident we have not missed any key studies nor that minor omissions would affect the overall results of our analyses anyway.
+Further, as noted we have chosen this as an example to demonstrate the methods moreso than to conduct a comprehensive systematic review of the topic.
 
@@
 The data extracted was imported into a spreadsheet in excel as a csv.
-
-ADD DETAILS ABOUT QUALITATIVE APPRAISAL OF STUDY AIMS
 
@@
 Statistical analysis of the data extracted was performed in R, (v 4.2.2; R Core Team, https://www.r-project.org/) and RStudio (v 2023.06.1; Posit, https://posit.co/).
-As noted, we adopted a Bayesian approach to the present meta-analysis.
-Specifically, we adopted informative priors from the models reported by Hatzigeorgiadis et al.
-[-@hatzigeorgiadisSelfTalkSportsPerformance2011] and replicated their analyses using appropriate model specifications given the structure of the data.
 All code utilised for data preparation and analyses are available in either the Open Science Framework page for this project [https://osf.io/dqwh5/](https://osf.io/dqwh5/) or the corresponding GitHub repository [https://github.com/jamessteeleii/self_talk_meta_analysis_update](https://github.com/jamessteeleii/self_talk_meta_analysis_update).
+
+ADD grateful citation report
+
     The `renv` package [@usheyRenvProjectEnvironments2023] was used for package version reproducibility and a function based analysis pipeline using the `targets` package [@landauTargetsDynamicFunctionOriented2023] was employed (the analysis pipeline can be viewed by downloading the R Project and running the function `targets::tar_visnetwork()`).
@@
 
-Effect sizes were calculated as SMDs dependent on the design of the study.
+### Examining the effects of a new trial upon belief in the effects of self-talk interventions
+To begin with we examined through simulation what impact a single new trial might have had upon shifting belief in the prior estimate yielded by the meta-analysis of Hatzigeorgiadis et al.
+[-@hatzigeorgiadisSelfTalkSportsPerformance2011].
+Sample size was simulated as 10, 20, 40, 80, 160, 320, 640, 1282, 2560, and 5120[^6] with a 50:50 allocation to either self-talk intervention or control conditions, and we varied the sample effect size as an SMD of 0, 0.2, 0.4, 0.6, 0.8, and 1.0 reflecting a range from no effect of self-talk interventions to a large  effect.
+In each combination of sample size and true effect size we set the sample parameters to  the SMD and its corresponding sampling variance was calculated and then included as a single observation in a Bayesian random effects meta-analysis where the priors was set informatively for the intervention effects, and were set to be default weakly regularising for the heterogeneity (i.e., $\tau$)[^7].
+Intervention effects were set with priors based on the effect estimates from Hatzigeorgiadis et al.
+[-@hatzigeorgiadisSelfTalkSportsPerformance2011], reported in their Table 1, using a $t$-distribution ($t(k,\mu,\sigma)$) with $k-2$ degrees of freedom [@higginsReevaluationRandomeffectsMetaanalysis2009].
+We assumed $k$ to be the number of effects included in the models reported by Hatzigeorgiadis et al.
+[-@hatzigeorgiadisSelfTalkSportsPerformance2011].
+The prior for the intervention effect was set directly on the model intercept i.e., $t(60, 0.48, 0.05)$.
+The prior for heterogeneity was set as the default weakly regularising prior in `brms`; a half-$t$-distribution with $\mu=0$, $\sigma=2.5$, and $k=3$.
+This constrained the prior to only allow positively signed values for $\tau$ though over a wide range of possible values.
+We fit each model using four Monte Carlo Markov Chains each with 2000 warmup and 6000 sampling iterations.
+
+From each model we obtained draws from the posterior distributions for the intervention effects (i.e., the expectation of the value of the parameters posterior probability distribution) in order to present probability density functions visually.
+The same was done drawing samples from the prior distributions only in order to present both distributions visually for comparison of the prior to posterior updating.
+As a means of examining the extent to which the posterior distribution for the self-talk intervention effect estimate was shifted from the prior distribution as a result of introducing each new trial we calculated the proportion of the full posterior distribution within the 95% quantile interval of the prior distribution i.e., the most probable value of the parameter in addition to the range from 2.5% to 97.5% percentiles (equivalent to the 95% confidence interval of the estimate from Hatzigeorgiadis et al.
+[-@hatzigeorgiadisSelfTalkSportsPerformance2011]), using the a Region of Practical Equivalence approach [@kruschkeBayesianNewStatistics2018a].
+In essence, where the proportion of the posterior distribution that was within the 95% quantile interval from the prior distribution was ~95% then we would conclude that the new trial had little impact on shifting our prior belief in the intervention effect.
+This helps understand whether it might be worthwhile to conduct the kind of study that would need to be conducted in terms of sample size, and assuming what the true effect might be, or whether doing so might be a waste of resources given the precision of existing estimates of the intervention effect.
+
+[^6]: Sample sizes were doubled up to roughly a similar sample size as the largest study post-2011 that we identified in our updated searches [@laneBriefOnlineTraining2016].
+
+[^7]: Though Hatzigeorgiadis et al.
+[-@hatzigeorgiadisSelfTalkSportsPerformance2011] report on $\tau$ it is not clear what level this applies to (and as noted it is not clear if they employed a hierachical model) and they do not report any interval estimate for this making it difficult to specify an informative prior distribution.
+As such, and given suggestions regarding heterogeneity priors [@williamsBayesianMetaAnalysisWeakly2018; @roverWeaklyInformativePrior2021], we opted for a weakly regularising distribution at all levels including the updated multilevel meta-analysis described further in these methods and in the random effects meta-analysis used in these simulations.
+
+### Updating the prior esitmate from Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011] with newer studies
+For all the groups/conditions in studies identified in our updated searches effect sizes were calculated as SMDs dependent on the design of the study.
 Firstly, all were signed such that a positive effect indicated that the self-talk intervention was favoured.
-For studies utilising a pretest-posttest-control comparison design we calculated the SMD between groups/conditions using the pooled pre-test standard deviation as per Morris [@morrisEstimatingEffectSizes2008].
+For studies utilising a pretest-posttest-control comparison design we calculated the SMD between groups/conditions using the pooled pre-test standard deviation as per Morris [-@morrisEstimatingEffectSizes2008].
 For post-test only control comparison designs we calculated the SMD between groups/conditions based upon the pooled post-test standard deviation.
 Lastly, for single arm within group pre-post (or control-intervention) designs we calculated the SMD from pre- to post-intervention using the pre-test standard deviation.
-Effect sizes were all calculated using the `escalc` function from the `metafor` package.
 
@@
 [-@hatzigeorgiadisSelfTalkSportsPerformance2011], whereby their overall estimate reflected the fixed model intercept.
-In addition, we produced models for each of the aforementioned categorical moderators where we excluded the model intercept in order to set priors for each category directly based on the estimates and their precision reported[^6] by Hatzigeorgiadis et al.
+In addition, we produced models for each of the aforementioned categorical moderators where we excluded the model intercept in order to set priors for each category directly based on the estimates and their precision reported (see footnote$^7$) by Hatzigeorgiadis et al.
 [-@hatzigeorgiadisSelfTalkSportsPerformance2011].
 
-[^6]: It is not clear exactly from the reporting by Hatzigeorgiadis et al.
-[-@hatzigeorgiadisSelfTalkSportsPerformance2011] as to whether their moderator analyses involved fitting their models to datasets constructed separately, whereby they were filtered to only include the relevant category for the moderator, or if they were fit together including all categories.
-We opted to fit them together for parsimony here.
-
-Priors for each model were set informatively for the intervention effects, and were set to be weakly regularising for the heterogeneity (i.e., $\tau$) at all levels of the model[^7].
+Priors for each model were again set informatively for the intervention effects, and were set to be weakly regularising for the heterogeneity (i.e., $\tau$) at all levels of the model.
 Intervention effects were set with priors based on the effect estimates from Hatzigeorgiadis et al.
@@
 
-[^7]: Though Hatzigeorgiadis et al.
-[-@hatzigeorgiadisSelfTalkSportsPerformance2011] report on $\tau$ it is not clear what level this applies to (and as noted it is not clear if they employed a hierachical model) and they do not report any interval estimate for this making it difficult to specify an informative prior distribution.
-As such, and given suggestions regarding heterogeneity priors [@williamsBayesianMetaAnalysisWeakly2018; @roverWeaklyInformativePrior2021], we opted for a weakly regularising distribution at all levels.
-
 As we were interested in determining how much the new evidence produced since Hatzigeorgiadis et al.
-[-@hatzigeorgiadisSelfTalkSportsPerformance2011] had updated our understanding of the effects of self-talk interventions, we fit each model using four Monte Carlo Markov Chains each with 4000 warmup and 40000 sampling iterations.
+[-@hatzigeorgiadisSelfTalkSportsPerformance2011] had updated our belief in the effects of self-talk interventions, we fit each model using four Monte Carlo Markov Chains each with 4000 warmup and 40000 sampling iterations.
 This was in order to obtain precise Bayes Factors using the Savage-Dickey ratio [@gronauBridgesamplingPackageEstimating2020].
@@
 We also calculated the 95% prediction intervals providing the range over which we can expect 95% of future effect estimates to fall and present each individual effect size on the forest plot.
-To compliment the visual inspection of prior to posterior updating we also present log10 Bayes Factors (log10[BF]) calculated *against* 100 effects ranging from a SMD of 0 through to 1 and plot these log10(BF) curves for each model intervention effect estimate i.e.., the Savage-Dickey ratio was calculated for each of 100 point effects in the interval (0,1) equally spaced.
+
+To compliment the visual inspection of prior to posterior updating we also present log10 Bayes Factors (log10[BF]) calculated *against* 100 effects ranging from a SMD of 0 through to 1 and plot these log10(BF) curves for each model intervention effect estimate i.e., the Savage-Dickey ratio was calculated for each of 100 point effects in the interval (0,1) equally spaced.
 These were compared to Jeffreys [-@jeffreysTheoryProbability1998] scale regarding evidence *against* (i.e., 0 to 0.5 = weak evidence; 0.5 to 1 = substantial evidence; 1 to 1.5 = strong evidence; 1.5 to 2 = very strong evidence; 2 or greater = decisive evidence).
 Thus, a positive log10(BF) value indicated that, compared to the prior distribution (meaning the estimates of Hatzigeorgiadis et al.
-[-@hatzigeorgiadisSelfTalkSportsPerformance2011]), there was now greater evidence against the SMD for which the log10(BF) was calculated.
-A loess smooth was then applied to these 100 values.
+[-@hatzigeorgiadisSelfTalkSportsPerformance2011]), there was now greater evidence *against* the SMD for which the log10(BF) was calculated.
+A loess smooth was then applied to these 100 values for visual presentation.
 
@@
 Note, for each of these models we employed four Monte Carlo Markov Chains each with 2000 warmup and 6000 sampling iterations given the focus was on presenting the updated estimates and to reduce the time required for cumulative models to be fit.
+
+### Examining the quality of the evidence and potential questionable research practices
+Both simulating the impact of a new trial to determine if it is worth performing, or updating a prior meta-analysis estimate with new evidence from subsequent trials, entail the assumption that the previous estimate is not biased by questionable research practices such as publication bias or *p*-hacking [@friesePHackingPublicationBias2020].
+The latter (i.e., updating a prior estimate) also relies on the assumption that the subsequent evidence to be included is also not biased by such influences.
+Hatzigeorgiadis et al.
+[-@hatzigeorgiadisSelfTalkSportsPerformance2011] did employ the fail-safe *N* approach which determines the number of unpublished *null* studies that would reduce the meta-analytic effect estimate non-significant and concluded that publication bias was unlikely ($K_0=102$).
+However, fail-safe *N*, whilst previously widely used in meta-analyses around the time [@heeneBriefHistoryFail2010], was known to be flawed and other methods such as funnel plot based regression techniques instead recommended [@beckerFailsafeFileDrawerNumber2005].
+Given this project was deliberately initiated as part of an undergraduate thesis with the intention of limiting the systematic review component to post 2011 due to time constraints and conduct an updated Bayesian meta-analysis, and that the purpose of the present manuscript is to demonstrate various cumulative evidence synthesis methods using the self-talk literature as an example, we did not ourselves acquire the data for studies from Hatzigeorgiadis et al.
+[-@hatzigeorgiadisSelfTalkSportsPerformance2011] to enable us to examine the possible presence of questionable research practices that might impact the prior estimate[^8].
+Instead we limit our examination to the subsequent post-2011 literature and make the reasonable assumption that, given the replication crisis and subsequent methodological reform efforts kicked off proper in the early 2010s, the presence of questionable research practices was likely as bad if not worse in the literature included in Hatzigeorgiadis et al.
+[-@hatzigeorgiadisSelfTalkSportsPerformance2011].
+
+[^8]: We did however contact Hatzigeorgiadis et al.
+[-@hatzigeorgiadisSelfTalkSportsPerformance2011] to ask if they could share the extracted data, given it was not openly available, so we could examine this.
+We did not however receive a response.
+
+Examining the presence of questionable research practices such as publication bias and *p*-hacking in the presences of data with a hierarchical structure such as we have in the present example is not simple.
+The methods noted in the introduction have primarily been developed for cases of fixed or random effects meta-analyses were each study contributes only a single effect in the model.
+However, some approaches have been extended to the hierarchical case such as funnel plot based regression methods [@rodgersEvaluatingMetaanalyticMethods2021] and Robust Bayesian Meta-Analysis (RoBMA) with model averaging [@bartosRobustBayesianMetaanalysis2023].
+However the latter, and in particular the selection methods incorporated, are very computationally intensive making them in most regards practically unfeasible.
+
+As such, we utilised the multilevel precision-effect test (PET) and precision-effect estimate with standard errors (PEESE) to estimate the adjusted effect size accounting for small study effects such as publication bias [@rodgersEvaluatingMetaanalyticMethods2021].
+The PET-PEESE respectively model a linear and quadratic relationship between standard error and effect size, the latter assuming that studies with very small standard errors, and thus large samples, are likely to be reported regardless of results whereas small studies with large standard errors required increasingly larger effects to be selected for publication.
+This approach is a conditional two-step estimator of the two models whereby if the test of the adjusted effect size with an $\alpha=0.10$ (for model selection only) is not significant (i.e., $p>\alpha$) then PET is reported whereas if it is significant (i.e., $p<\alpha$) then PEESE is reported.
+The adjusted estimate was compared to the estimate generated from a multilevel meta-analysis model of the included studies.
+Note, the adjusted PET-PEESE estimate of the intervention effects and the comparative estimate from the multilevel meta-analysis model where both conducted using Frequentist models.
+
+In addition to this we also examined both the mixture model for *p*-hacking [@mossModellingPublicationBias2023] and RoBMA [@@bartosRobustBayesianMetaanalysis2023] (both with, and without, the inclusion of an informative prior on the intervention effect from Hatzigeorgiadis et al.
+[-@hatzigeorgiadisSelfTalkSportsPerformance2011]) though ignored the hierarchical structure to the data.
+The mixture model for for *p*-hacking provides an adjusted estimate of the intervention effect under the assumption that *p*-hacking such as excluding observations, collecting new data *ex-post*, or selectively including covariates has occured to produce the effects we see in the literature.
+The RoBMA fits a total of 36 different models with varying assumptions regarding the true data generating process underlying the included studies/effects and thus reflecting our uncertainty in it: selection models varying sidedness of the tests (one- or two-sided) and the specific *p*-value cutoffs used (combinations of 0.025, 0.05, 0.10, and 0.50), the PET-PEESE regression based models, assuming there is/is not an intervention effect, assuming there is/is not heterogeneity, and assuming there is/is not publication bias.
+These models are then combined using Bayesian model-averaging and weighted based on how well the model fit the data.
+Bayes Factors were then calculated to examine the evidence in favour of there being an effect, the presence of heterogeneity, and publication bias.
 
@@
 Reflecting this, Hatzigeorgiadis et al.
-[-@hatzigeorgiadisSelfTalkSportsPerformance2011] reported $\tau$ = 0.27 (though as noted in footnote[^7] it is not clear which level this pertains to) for the self-talk intervention studies they explored, and our study level estimate was not dissimilar to this ($\tau$ = `r round(tidy_main_model$estimate[2],2)` [95% quantile interval: `r round(tidy_main_model$conf.low[2],2)`, `r round(tidy_main_model$conf.high[2],2)`]).
+[-@hatzigeorgiadisSelfTalkSportsPerformance2011] reported $\tau$ = 0.27 (though as noted in footnote$^7$ it is not clear which level this pertains to) for the self-talk intervention studies they explored, and our study level estimate was not dissimilar to this ($\tau$ = `r round(tidy_main_model$estimate[2],2)` [95% quantile interval: `r round(tidy_main_model$conf.low[2],2)`, `r round(tidy_main_model$conf.high[2],2)`]).
 Indeed, our prediction interval ranged from `r round(pred_int_data$ymin,2)` to `r round(pred_int_data$ymax,2)`.

### 2024-07-29 R/functions.R

@@ -561,140 +561,215 @@ sample_prior_study_design_model <- function(data, prior) {
     )
 }
 
-# # Simulation of additional new study
-# additional_new_study_sim <- function() {
-#
-#   sim <- function(participant_n = as.double(),
-#                   b0 = as.double(), b_time = as.double(), b_cond = as.double(), b_cond_time = as.double(),         # fixed effects
-#                   u_participant = as.double(), # random intercepts
-#                   sigma = as.double(),       # measurement error
-#                   ... # helps the function work with pmap() below
-#   ) {
-#
-#     # Taken fromm Hatsigeorgiadis et al. (2011) overall estimate
-#     main_model_prior <-
-#       c(
-#         brms::prior("student_t(60, 0.48, 0.05)", class = "Intercept")
-#       )
-#
-#     # set up data structure
-#     dat <- add_random(participant = 100) |>
-#       add_between("participant", cond = c("control", "self_talk")) |>
-#       add_recode("cond", "cond_dummy", control = 0, self_talk = 1) |>
-#       add_within("participant", time = seq(0,1)) |>
-#       add_ranef("participant", u_participant = 1) |>
-#       add_ranef(sigma = 0.5) |>
-#       mutate(dv = (0 + u_participant) + (1 * time) + (0 * cond_dummy) + (0.5 * cond_dummy * time) + sigma)
-#
-#     ri_self_talk <- cor(filter(dat, cond == "self_talk" & time == 0)$dv,
-#                         filter(dat, cond == "self_talk" & time == 1)$dv)
-#
-#     ri_control <- cor(filter(dat, cond == "control" & time == 0)$dv,
-#                       filter(dat, cond == "control" & time == 1)$dv)
-#
-#     summary_dat <- dat |>
-#       group_by(time, cond) |>
-#       add_count() |>
-#       summarise(n = first(n),
-#                 mean = mean(dv),
-#                 sd = sd(dv)) |>
-#       pivot_wider(names_from = c(time,cond),
-#                   values_from = c(mean, sd, n)) |>
-#       mutate(pre_sd_pool = sqrt(((n_0_self_talk - 1) * sd_0_self_talk  ^ 2 +
-#                                    (n_0_control - 1) * sd_0_control ^ 2
-#       ) /
-#         (n_0_self_talk + n_0_control - 2)),
[…]

### 2024-07-29 _targets.R

@@ -42,9 +42,9 @@ list(
   # Setup rstan to run chains in parallel
   tar_target(rstan, rstan_setup()),
 
-  # # Simulation of additional new study
-  # tar_target(additional_study_sims, additional_new_study_sim()),
-  # tar_target(additional_study_sims_plot, plot_additional_new_study_sims(additional_study_sims)),
+  # Simulation of additional new study
+  tar_target(additional_study_sims, additional_new_study_sim(prior_main_model)),
+  tar_target(additional_study_sims_plot, plot_additional_new_study_sims(additional_study_sims)),
 
   # Fit, check, and plot main model
   tar_target(main_prior, set_main_prior()),
@@ -191,7 +191,7 @@ list(
   tar_target(cumulative_main_model_plot, plot_cumulative_main_model(data_effect_sizes, prior_main_model, cumulative_draws)),
 
   # Make plots tiffs
-  # tar_target(additional_study_sims_plot_tiff, make_plot_tiff(additional_study_sims_plot, 7.5, 13.33, "plots/additional_study_sims_plot.tiff")),
+  tar_target(additional_study_sims_plot_tiff, make_plot_tiff(additional_study_sims_plot, 13.33, 7.5, "plots/additional_study_sims_plot.tiff")),
   tar_target(main_model_plot_tiff, make_plot_tiff(main_model_plot, 7.5, 13.33, "plots/main_model_plot.tiff")),
   tar_target(main_model_contour_funnel_plot_tiff, make_plot_tiff(main_model_contour_funnel_plot, 5, 5, "plots/main_model_contour_funnel_plot.tiff")),
   # tar_target(moderators_panel_plot_tiff, make_plot_tiff(moderators_panel_plot, 21, 9, "plots/moderators_panel_plot.tiff")),

### 2024-07-29 pre_print_manuscript.qmd
Moderators plots converted to grobs to reduce file size

@@
 
-### Examining the effects of a new trial upon belief in the effects of self-talk interventions
 To begin with we examined through simulation what impact a single new trial might have had upon shifting belief in the prior estimate yielded by the meta-analysis of Hatzigeorgiadis et al.
@@
 
-### Updating the prior esitmate from Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011] with newer studies
+### Updating the prior estimate from Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011] with newer studies
 For all the groups/conditions in studies identified in our updated searches effect sizes were calculated as SMDs dependent on the design of the study.
@@
 
-## Main model
+## Examining the effects of a new trial upon belief in the effects of self-talk interventions
+
+## Updating the prior estimate from Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011] with newer studies
+
+### Main model
 ```{r}
@@
 
-## Moderators
+### Moderators
 ```{r}
@@
 \elandscape
+
+## Examining the quality of the evidence and potential questionable research practices
 

### 2024-07-29 R/functions.R

@@ -243,6 +243,18 @@ make_plot_tiff <- function(plot, width, height, path) {
 
 }
 
+ggplot_2_grob_nback <- function(plot) {
+  plot_grob <- ggplot2::ggplotGrob(plot)
+  plot_new <- ggpubr::as_ggplot(plot_grob)
+
+  remove(plot)
+  remove(plot_grob)
+
+  gc()
+
+  return(plot_new)
+}
+
 get_logBF_curve <- function(model) {
 
   plan(multisession, workers = 5)
@@ -1401,6 +1413,16 @@ plot_motor_demands_model <- function(data, prior_model, model) {
     theme(legend.position = "bottom",
           panel.border = element_rect(fill = NA),
           title = element_text(size=8))
+
+  plot_grob <- ggplot2::ggplotGrob(posterior_update)
+  plot_new <- ggpubr::as_ggplot(plot_grob)
+
+  remove(posterior_update)
+  remove(plot_grob)
+
+  gc()
+
+  return(plot_new)
 }
 
 plot_participant_group_model <- function(data, prior_model, model) {
@@ -1490,6 +1512,17 @@ plot_participant_group_model <- function(data, prior_model, model) {
     theme(legend.position = "bottom",
           panel.border = element_rect(fill = NA),
           title = element_text(size=8))
+
+
+  plot_grob <- ggplot2::ggplotGrob(posterior_update)
+  plot_new <- ggpubr::as_ggplot(plot_grob)
+
+  remove(posterior_update)
+  remove(plot_grob)
+
+  gc()
+
+  return(plot_new)
 }
 
 plot_selftalk_content_model <- function(data, prior_model, model) {
@@ -1580,6 +1613,17 @@ plot_selftalk_content_model <- function(data, prior_model, model) {
     theme(legend.position = "bottom",
           panel.border = element_rect(fill = NA),
           title = element_text(size=8))
+
+
+  plot_grob <- ggplot2::ggplotGrob(posterior_update)
+  plot_new <- ggpubr::as_ggplot(plot_grob)
+
+  remove(posterior_update)
+  remove(plot_grob)
+
+  gc()
+
+  return(plot_new)
 }
 
 plot_matching_model <- function(data, prior_model, model) {
@@ -1670,6 +1714,17 @@ plot_matching_model <- function(data, prior_model, model) {
     theme(legend.position = "bottom",
           panel.border = element_rect(fill = NA),
           title = element_text(size=8))
+
+
[…]

### 2024-07-29 _targets.R

@@ -168,12 +168,25 @@ list(
   tar_target(study_design_model_logBF_curve, get_logBF_curve(study_design_model)),
   tar_target(tidy_study_design_model, get_tidy_model(study_design_model)),
 
-  # # Make panel plot of moderators
-  # tar_target(moderators_panel_plot, plot_panel_moderators(
-  #   motor_demands_model_plot, participant_group_model_plot, selftalk_content_model_plot,
-  #     matching_model_plot, task_novelty_model_plot, cue_selection_model_plot,
-  #   overtness_selection_model_plot, training_model_plot, study_design_model_plot
-  # )),
+  # Make panel plot of moderators
+
+  # ## First convert plots to grob and back to reduce file sizes
+  # tar_target(motor_demands_model_plot_new, ggplot_2_grob_nback(motor_demands_model_plot)),
+  # tar_target(participant_group_model_plot_new, ggplot_2_grob_nback(participant_group_model_plot)),
+  # tar_target(selftalk_content_model_plot_new, ggplot_2_grob_nback(selftalk_content_model_plot)),
+  # tar_target(matching_model_plot_new, ggplot_2_grob_nback(matching_model_plot)),
+  # tar_target(task_novelty_model_plot_new, ggplot_2_grob_nback(task_novelty_model_plot)),
+  # tar_target(cue_selection_model_plot_new, ggplot_2_grob_nback(cue_selection_model_plot)),
+  # tar_target(overtness_selection_model_plot_new, ggplot_2_grob_nback(overtness_selection_model_plot)),
+  # tar_target(training_model_plot_new, ggplot_2_grob_nback(training_model_plot)),
+  # tar_target(study_design_model_plot_new, ggplot_2_grob_nback(study_design_model_plot)),
+
+  ## Patchwork of new plots
+  tar_target(moderators_panel_plot, plot_panel_moderators(
+    motor_demands_model_plot, participant_group_model_plot, selftalk_content_model_plot,
+      matching_model_plot, task_novelty_model_plot, cue_selection_model_plot,
+    overtness_selection_model_plot, training_model_plot, study_design_model_plot
+  )),
 
   # Make supplemental plots of evidence change for moderators
[…]

### 2024-08-11 R/functions.R
Changed back to gather_draws for moderator plots

@@ -1330,33 +1330,26 @@ plot_BF_curve_main_model <- function(BF_curve) {
 
 plot_motor_demands_model <- function(data, prior_model, model) {
 
-  # Prior distribution samples
-  nd <- datagrid(model = model,
-                 motor_demands = c("Fine", "Gross"),
-                 vi = model$data$vi
-  )
+  prior_preds <- prior_model |>
+    gather_draws(b_motor_demandsFine, b_motor_demandsGross) |>
+    mutate(motor_demands = case_when(
+      .variable == "b_motor_demandsFine" ~ "Fine",
+      .variable == "b_motor_demandsGross" ~ "Gross"
 
-  # Prior distribution samples
-  prior_preds <- predictions(prior_model, type = "response",
-                             newdata = nd,
-                             re_formula = NA) |>
-    posterior_draws() |>
-    transform(type = "Response") |>
-    mutate(label = "Prior (Hatzigeorgiadis et al., 2011)")
+    ),
+    label = "Prior (Hatzigeorgiadis et al., 2011)")
 
-  # Posterior distribution samples
-  posterior_preds <- predictions(model, type = "response",
-                                 newdata = nd,
-                                 re_formula = NA) |>
-    posterior_draws() |>
-    transform(type = "Response") |>
-    mutate(label = "Posterior Pooled Estimate")
+  posterior_preds <- model |>
+    gather_draws(b_motor_demandsFine, b_motor_demandsGross) |>
+    mutate(motor_demands = case_when(
+      .variable == "b_motor_demandsFine" ~ "Fine",
+      .variable == "b_motor_demandsGross" ~ "Gross"
+
+    ),
+    label = "Posterior Pooled Estimate")
 
   posterior_summary <- group_by(posterior_preds, motor_demands, label) |>
-    mean_qi(draw) |>
-    mutate(draw = draw,
-           .lower = .lower,
-           .upper = .upper)
+    mean_qi(.value)
 
   # Combine prior and posterior samples for plot
   prior_posterior <- rbind(prior_preds, posterior_preds) |>
@@ -1365,7 +1358,7 @@ plot_motor_demands_model <- function(data, prior_model, model) {
     )))
 
   posterior_update <- ggplot(data = prior_posterior,
-                             aes(x = draw, y = motor_demands,
+                             aes(x = .value, y = motor_demands,
                                  color = label, fill = label)
   ) +
     # Add reference line at zero
@@ -1388,7 +1381,7 @@ plot_motor_demands_model <- function(data, prior_model, model) {
[…]

### 2024-08-11 _targets.R

@@ -169,19 +169,6 @@ list(
   tar_target(tidy_study_design_model, get_tidy_model(study_design_model)),
 
   # Make panel plot of moderators
-
-  # ## First convert plots to grob and back to reduce file sizes
-  # tar_target(motor_demands_model_plot_new, ggplot_2_grob_nback(motor_demands_model_plot)),
-  # tar_target(participant_group_model_plot_new, ggplot_2_grob_nback(participant_group_model_plot)),
-  # tar_target(selftalk_content_model_plot_new, ggplot_2_grob_nback(selftalk_content_model_plot)),
-  # tar_target(matching_model_plot_new, ggplot_2_grob_nback(matching_model_plot)),
-  # tar_target(task_novelty_model_plot_new, ggplot_2_grob_nback(task_novelty_model_plot)),
-  # tar_target(cue_selection_model_plot_new, ggplot_2_grob_nback(cue_selection_model_plot)),
-  # tar_target(overtness_selection_model_plot_new, ggplot_2_grob_nback(overtness_selection_model_plot)),
-  # tar_target(training_model_plot_new, ggplot_2_grob_nback(training_model_plot)),
-  # tar_target(study_design_model_plot_new, ggplot_2_grob_nback(study_design_model_plot)),
-
-  ## Patchwork of new plots
   tar_target(moderators_panel_plot, plot_panel_moderators(
     motor_demands_model_plot, participant_group_model_plot, selftalk_content_model_plot,
       matching_model_plot, task_novelty_model_plot, cue_selection_model_plot,

### 2024-08-11 R/functions.R
Remove old sim code chunk for raw data

@@ -587,63 +587,6 @@ additional_new_study_sim <- function(prior_model) {
         brms::prior("student_t(60, 0.48, 0.05)", class = "Intercept")
       )
 
-    # # set up data structure
-    # dat <- add_random(participant = participant_n) |>
-    #   add_between("participant", cond = c("control", "self_talk")) |>
-    #   add_recode("cond", "cond_dummy", control = 0, self_talk = 1) |>
-    #   add_within("participant", time = seq(0,1)) |>
-    #   add_ranef("participant", u_participant = u_participant) |>
-    #   add_ranef(e = sigma) |>
-    #   mutate(dv = (b0 + u_participant) + (b_time * time) + (b_cond * cond_dummy) + (b_cond_time * cond_dummy * time) + e)
-    #
-    # ri_self_talk <- cor(filter(dat, cond == "self_talk" & time == 0)$dv,
-    #                     filter(dat, cond == "self_talk" & time == 1)$dv)
-    #
-    # ri_control <- cor(filter(dat, cond == "control" & time == 0)$dv,
-    #                   filter(dat, cond == "control" & time == 1)$dv)
-    #
-    # summary_dat <- dat |>
-    #   group_by(time, cond) |>
-    #   add_count() |>
-    #   summarise(n = first(n),
-    #             mean = mean(dv),
-    #             sd = sd(dv)) |>
-    #   pivot_wider(names_from = c(time,cond),
-    #               values_from = c(mean, sd, n)) |>
-    #   mutate(pre_sd_pool = sqrt(((n_0_self_talk - 1) * sd_0_self_talk  ^ 2 +
-    #                                (n_0_control - 1) * sd_0_control ^ 2
-    #   ) /
-    #     (n_0_self_talk + n_0_control - 2)),
-    #   ri_self_talk = ri_self_talk,
-    #   ri_control = ri_control
-    #   )
-    #
-    # ppc_dat_st <- escalc(
-    #   measure = "SMCR",
-    #   m1i = mean_1_self_talk,
-    #   m2i = mean_0_self_talk,
-    #   sd1i = pre_sd_pool,
-    #   ni = n_0_self_talk,
-    #   ri = ri_self_talk,
-    #   data = summary_dat
-    # )
-    # ppc_dat_con <- escalc(
-    #   measure = "SMCR",
-    #   m1i = mean_1_control,
-    #   m2i = mean_0_control,
-    #   sd1i = pre_sd_pool,
[…]

### 2024-08-11 pre_print_manuscript.qmd
Add mixture models for p-hacking

@@
 [-@hatzigeorgiadisSelfTalkSportsPerformance2011]) though ignored the hierarchical structure to the data.
-The mixture model for for *p*-hacking provides an adjusted estimate of the intervention effect under the assumption that *p*-hacking such as excluding observations, collecting new data *ex-post*, or selectively including covariates has occured to produce the effects we see in the literature.
+The mixture model for for *p*-hacking provides an adjusted estimate of the intervention effect under the assumption that *p*-hacking such as excluding observations, collecting new data *ex-post*, or selectively including covariates has occurred to produce the effects we see in the literature.
 The RoBMA fits a total of 36 different models with varying assumptions regarding the true data generating process underlying the included studies/effects and thus reflecting our uncertainty in it: selection models varying sidedness of the tests (one- or two-sided) and the specific *p*-value cutoffs used (combinations of 0.025, 0.05, 0.10, and 0.50), the PET-PEESE regression based models, assuming there is/is not an intervention effect, assuming there is/is not heterogeneity, and assuming there is/is not publication bias.

### 2024-08-11 R/functions.R

@@ -1000,6 +1000,26 @@ fit_prior_robma_model <- function(data) {
   )
 }
 
+# P-hacking effects
+fit_p_hack_model <- function(data) {
+  p_hack_model <- phma(yi, vi, filter(data, !is.na(yi)))
+}
+
+fit_classic_model <- function(data) {
+  classic_model <- cma(yi, vi, filter(data, !is.na(yi)))
+}
+
+fit_p_hack_model_prior <- function(data) {
+  p_hack_model_prior <- phma(yi, vi, filter(data, !is.na(yi)),
+                             prior = list(theta0_mean = 0.48, theta0_sd = 0.05))
+}
+
+fit_classic_model_prior <- function(data) {
+  classic_model_prior <- cma(yi, vi, filter(data, !is.na(yi)),
+                             prior = list(theta0_mean = 0.48, theta0_sd = 0.05))
+}
+
+
 # Plots
 plot_main_model_forest <- function(data, model) {
 
@@ -1155,6 +1175,164 @@ plot_contour_funnel <- function(data, tidy_model, pet_model, tidy_pet_model) {
     theme_classic() +
     theme(panel.border = element_rect(fill = NA),
           plot.subtitle = element_text(size = 6))
+
+}
+
+plot_p_hack_models <- function(p_hack_model, classic_model) {
+  samples_p_hack_model <- tibble(
+    draws = rstan::extract(p_hack_model)$theta0,
+    model = "p-hacking model"
+  )
+
+  posterior_summary_p_hack_model <- samples_p_hack_model |>
+    mean_qi(draws) |>
+    mutate(model = "p-hacking model")
+
+  samples_classic_model <- tibble(
+    draws = rstan::extract(classic_model)$theta0,
+    model = "Classic model"
+  )
+
+  posterior_summary_classic_model <- samples_classic_model |>
+    mean_qi(draws) |>
+    mutate(model = "Classic model")
+
+  samples_models <- rbind(
+    samples_classic_model, samples_p_hack_model
+  )
+
+  plot_p_hack_classic <- samples_models |>
+    ggplot(aes(x = draws,
+               color = model, fill = model)
+    ) +
+    # Add reference line at zero
+    geom_vline(xintercept = 0, linetype = 2) +
+
+    stat_slab(alpha = 0.6, linewidth = 0) +
+
+    # Add text and labels
+    geom_text(
+      data = mutate_if(posterior_summary_classic_model,
+                       is.numeric, round, 2),
+      aes(
[…]

### 2024-08-11 _targets.R

@@ -28,6 +28,7 @@ tar_option_set(
     "marginaleffects",
     "broom.mixed",
     # "RoBMA",
+    "publipha",
     "future",
     "faux"
   )
@@ -60,7 +61,7 @@ list(
   tar_target(main_model_plot, plot_panel_main_model(main_model_forest_plot,main_model_update_plot,BF_curve_main_model_plot)),
   tar_target(tidy_main_model, get_tidy_model(main_model)),
 
-  # # Small study/Publication bias for main model
+  # Small study/Publication bias for main model
   tar_target(pet_model, fit_pet_model(data_effect_sizes)),
   tar_target(tidy_pet_model, tidy(pet_model, conf.int = .95)),
   tar_target(rma.mv_model, fit_rma.mv_model(data_effect_sizes)),
@@ -69,7 +70,16 @@ list(
   tar_target(null_robma_model, fit_null_robma_model(data_effect_sizes)),
   tar_target(prior_robma_model, fit_prior_robma_model(data_effect_sizes)),
 
-  # # Fit, check, and plot motor demands model
+  # p-hacking models
+  tar_target(p_hack_model, fit_p_hack_model(data_effect_sizes)),
+  tar_target(classic_model, fit_classic_model(data_effect_sizes)),
+  tar_target(p_hack_models_plot, plot_p_hack_models(p_hack_model, classic_model)),
+  tar_target(p_hack_model_prior, fit_p_hack_model_prior(data_effect_sizes)),
+  tar_target(classic_model_prior, fit_classic_model_prior(data_effect_sizes)),
+  tar_target(p_hack_models_prior_plot, plot_p_hack_models_prior(p_hack_model_prior, classic_model_prior)),
+  tar_target(p_hack_models_plots, plot_panel_p_hack(p_hack_models_plot, p_hack_models_prior_plot)),
+
+  # Fit, check, and plot motor demands model
   tar_target(motor_demands_prior, set_motor_demands_prior()),
   tar_target(prior_motor_demands_model, sample_prior_motor_demands_model(data_effect_sizes, motor_demands_prior)),
   tar_target(motor_demands_model, fit_motor_demands_model(data_effect_sizes, motor_demands_prior)),
@@ -194,6 +204,7 @@ list(
[…]

### 2024-08-12 R/functions.R
Change colours on p-hack estimates so as to not confuse with colours used in prior to posterior updates

@@ -1239,8 +1239,8 @@ plot_p_hack_models <- function(p_hack_model, classic_model) {
       position = position_nudge(y=0.1)
     ) +
 
-    scale_color_manual(values = c("#009E73", "#E69F00")) +
-    scale_fill_manual(values = c("#009E73", "#E69F00")) +
+    scale_color_manual(values = c("#0072B2", "#D55E00")) +
+    scale_fill_manual(values = c("#0072B2", "#D55E00")) +
 
     labs(x = "Standardised Mean Difference", # summary measure
          y = element_blank(),
@@ -1318,8 +1318,8 @@ plot_p_hack_models_prior <- function(p_hack_model_prior, classic_model_prior) {
       position = position_nudge(y=0.1)
     ) +
 
-    scale_color_manual(values = c("#009E73", "#E69F00")) +
-    scale_fill_manual(values = c("#009E73", "#E69F00")) +
+    scale_color_manual(values = c("#0072B2", "#D55E00")) +
+    scale_fill_manual(values = c("#0072B2", "#D55E00")) +
 
     labs(x = "Standardised Mean Difference", # summary measure
          y = element_blank(),

### 2024-08-12 pre_print_manuscript.qmd
Revised results section complete - adding study simulations and also pub bias/QRP models.

--- 2024-07-29 pre_print_manuscript.qmd
@@
 
+### Examining the effects of a new trial upon belief in the effects of self-talk interventions
 To begin with we examined through simulation what impact a single new trial might have had upon shifting belief in the prior estimate yielded by the meta-analysis of Hatzigeorgiadis et al.
@@
 
-In addition to this we also examined both the mixture model for *p*-hacking [@mossModellingPublicationBias2023] and RoBMA [@@bartosRobustBayesianMetaanalysis2023] (both with, and without, the inclusion of an informative prior on the intervention effect from Hatzigeorgiadis et al.
-[-@hatzigeorgiadisSelfTalkSportsPerformance2011]) though ignored the hierarchical structure to the data.
-The mixture model for for *p*-hacking provides an adjusted estimate of the intervention effect under the assumption that *p*-hacking such as excluding observations, collecting new data *ex-post*, or selectively including covariates has occured to produce the effects we see in the literature.
-The RoBMA fits a total of 36 different models with varying assumptions regarding the true data generating process underlying the included studies/effects and thus reflecting our uncertainty in it: selection models varying sidedness of the tests (one- or two-sided) and the specific *p*-value cutoffs used (combinations of 0.025, 0.05, 0.10, and 0.50), the PET-PEESE regression based models, assuming there is/is not an intervention effect, assuming there is/is not heterogeneity, and assuming there is/is not publication bias.
+In addition to this we also examined both the random effects mixture model for *p*-hacking [@mossModellingPublicationBias2023] and RoBMA [@@bartosRobustBayesianMetaanalysis2023] (both with, and without, the inclusion of an informative prior[^9] on the intervention effect from Hatzigeorgiadis et al.
+[-@hatzigeorgiadisSelfTalkSportsPerformance2011], yet with default priors for all other parameters) though ignored the hierarchical structure to the data as these models respectively have not been extended to the multilevel case or are too computationally intractable at present.
+The random effects mixture model for for *p*-hacking provides an adjusted estimate of the intervention effect under the assumption that questionable research practices such as excluding observations, collecting new data *ex-post*, or selectively including covariates has occurred to produce a one-sided $\alpha\leq0.05$ (to reflect the fact that typically it is effects in a particular direction that are of interest) or $\alpha\leq0.025$ to account for reporting of two-sided tests.
+The adjusted estimate assuming the presence of *p*-hacking was then compared to a classical random effects model estimate.
+Both the *p*-hacking and classical models were fit using Bayesian estimation.
+The RoBMA fits a total of 36 different models with varying assumptions regarding the true data generating process underlying the included studies/effects and thus reflecting our uncertainty in it: selection models for publication varying sidedness of the tests (one- or two-sided) and the specific *p*-value cutoffs used (combinations of 0.025, 0.05, 0.10, and 0.50), the PET-PEESE regression based models, models assuming there is/is not an intervention effect, models assuming there is/is not heterogeneity, and models assuming there is/is not publication bias.
 These models are then combined using Bayesian model-averaging and weighted based on how well the model fit the data.
 Bayes Factors were then calculated to examine the evidence in favour of there being an effect, the presence of heterogeneity, and publication bias.
+
+[^9]: Note that for the mixture model of *p*-hacking the `publipha` package used does not allow for specification of a prior based upon the $t$ distribution for that function.
+As such, instead of the $t(60, 0.48, 0.05)$ prior taken from Hatzigeorgiadis et al.
+[-@hatzigeorgiadisSelfTalkSportsPerformance2011] for these models we used a normal prior with the same location and scale parameters.
+Given the the $t$ distribution approaches the normal distribution with high degrees of freedom, and the prior for other models had a high number of degrees of freedom (i.e., $k=60$), the choice of a normal distribution here very closely approximates the $t$ distribution based prior anyway.
 
@@
 sample_sizes_st <- data %>%
-  select(group, n_st) %>%
-  group_by(group) %>%
+  select(group_code, n_st) %>%
+  group_by(group_code) %>%
   summarise(n_st = max(n_st)) %>%
@@
 sample_sizes_con <- data %>%
-  select(study, n_con) %>%
-  group_by(study) %>%
+  select(study_code, n_con) %>%
+  group_by(study_code) %>%
   summarise(n_con = max(n_con)) %>%
@@
 
-We identified `r length(unique(data$study))` new studies published from November 2011 up to November 2023 [@abdoliCloserLookHow2018; @hatzigeorgiadisSelftalkCompetitiveSport2014; @panteliAcquisitionLongJump2013; @hongEmpiricalTestSelfTalk2020; @hatzigeorgiadisBeatHeatEffects2018; @laneBriefOnlineTraining2016; @latinjakCombiningSelfTalk2011; @gregersenCounteringConsequencesEgo2017; @mccormickEffectsMotivationalSelfTalk2018; @galanisEffectsStrategicSelftalk2022; @benekaEffectsInstructionalMotivational2013; @wallaceEffectsMotivationalSelfTalk2017; @walterEffectsSelfTalkTraining2019; @galanisLabFieldEffects2018; @youngHowMuchDoes2023; @raalteWillUseDeclarative2018; @liuInteractiveEffectsMotor2022; @dematosMotivationalSelftalkImproves2021; @barwoodImprovement10kmTimetrial2015; @cabralMotivationalSelftalkMitigates2023; @changSelftalkSoftballPerformance2014; @raalteSelfTalkSCUBADiving2018; @galanisStrategicSelfTalkAssists2022; @blanchfieldTalkingYourselfOut2014; @turnerTeeingSuccessEffects2018; @naderiradEffectInstructionalMotivational2023; @zetouEffectSelftalkTaekwondo2014; @zourbanosEffectsSelftalkIntervention2013; @osmanEffectsInstructionalMotivational2022; @kolovelonisEffectsInstructionalMotivational2011; @sarigEffectsInstructionalSelfTalk2023; @marshallEffectsSelfTalkCues2016; @zourbanosEffectsSelfTalkDominant2013; @galanisEffectsStrategicSelftalk2023; @weinbergInfluenceSelftalkIntervention2012].
-These included `r length(unique(data$effect))` effects nested in `r length(unique(data$group))` groups nested in `r length(unique(data$experiment))` experiments.
+Since Hatzigeorgiadis et al.
+[-@hatzigeorgiadisSelfTalkSportsPerformance2011] meta-analysis the number of studies conducted examining the effects of self-talk interventions on sport/motor performance has roughly doubled.
+We identified `r length(unique(data$study_code))` new studies published from November 2011 up to November 2023 [@abdoliCloserLookHow2018; @hatzigeorgiadisSelftalkCompetitiveSport2014; @panteliAcquisitionLongJump2013; @hongEmpiricalTestSelfTalk2020; @hatzigeorgiadisBeatHeatEffects2018; @laneBriefOnlineTraining2016; @latinjakCombiningSelfTalk2011; @gregersenCounteringConsequencesEgo2017; @mccormickEffectsMotivationalSelfTalk2018; @galanisEffectsStrategicSelftalk2022; @benekaEffectsInstructionalMotivational2013; @wallaceEffectsMotivationalSelfTalk2017; @walterEffectsSelfTalkTraining2019; @galanisLabFieldEffects2018; @youngHowMuchDoes2023; @raalteWillUseDeclarative2018; @liuInteractiveEffectsMotor2022; @dematosMotivationalSelftalkImproves2021; @barwoodImprovement10kmTimetrial2015; @cabralMotivationalSelftalkMitigates2023; @changSelftalkSoftballPerformance2014; @raalteSelfTalkSCUBADiving2018; @galanisStrategicSelfTalkAssists2022; @blanchfieldTalkingYourselfOut2014; @turnerTeeingSuccessEffects2018; @naderiradEffectInstructionalMotivational2023; @zetouEffectSelftalkTaekwondo2014; @zourbanosEffectsSelftalkIntervention2013; @osmanEffectsInstructionalMotivational2022; @kolovelonisEffectsInstructionalMotivational2011; @sarigEffectsInstructionalSelfTalk2023; @marshallEffectsSelfTalkCues2016; @zourbanosEffectsSelfTalkDominant2013; @galanisEffectsStrategicSelftalk2023; @weinbergInfluenceSelftalkIntervention2012].
+These included `r length(unique(data$effect_code))` effects nested in `r length(unique(data$group_code))` groups nested in `r length(unique(data$experiment_code))` experiments.
 The included studies contained a total of `r sample_sizes[1,2] + sample_sizes[5,2]` participants (see @tbl-sample-sizes).
@@
 ## Examining the effects of a new trial upon belief in the effects of self-talk interventions
+```{r}
+#| label: fig-additional-study 
+#| fig-width: 13.33
+#| fig-height: 7.5
+#| fig-cap: Prior and posterior distributions after the addition of a single new study yielding a single new effect varying in magnitude of standardised mean difference (null through to SMD=1 favouring self-talk interventions) and varying sample size of the new study (from n=10 to 5120).
+targets::tar_load(additional_study_sims_plot)
+
+additional_study_sims_plot
+```
+Given the precision of the prior distribution taken from Hatzigeorgiadis et al.
+[-@hatzigeorgiadisSelfTalkSportsPerformance2011] it is highly unlikely that any further study would have shifted belief in the effect estimate.
+As can be seen in @fig-additional-study, irrespective of the sample size or magnitude of effect and the extent to which it disagreed with the prior estimate, no single new study could shift the posterior distribution to an extent that it didn't still have ~95% of its mass within the 95% quantile interval of the prior distribution.
+As such, if we were to take the prior estimate from Hatzigeorgiadis et al.
+[-@hatzigeorgiadisSelfTalkSportsPerformance2011] at face value in the process of deciding whether to conduct a new study of self-talk interventions, at least with respect to their main effects on sport/motor performance, we should likely conclude that it would be a waste of resources given the precision of this existing estimate of the intervention effect.
+Of course, this only considers the addition of a single study and as noted since 2011 the number of studies examining self-talk interventions has roughly doubled.
+As such, it is worth considering the extent to which this volume of additional evidence might have updated belief in the estimate of their effects.
 
@@
 "Weak" or "Negative" evidence was indicated against effect sizes ranging from `r round(Jeffreys_scales$min_effect[9],2)` to `r round(Jeffreys_scales$max_effect[10],2)`.
-This suggested that the newly acquired evidence generally decreased our belief in effect sizes that would likely already have been ruled out by the analysis of Hatzigeorgiadis et al.
+This suggested that the newly acquired evidence generally decreased our belief only in effect sizes that would likely already have been ruled out by the analysis of Hatzigeorgiadis et al.
 [-@hatzigeorgiadisSelfTalkSportsPerformance2011].
@@
 @fig-moderators-models shows each of the prior and posterior distributions for the moderators estimates and the log10(BF) results for each are available in the supplementary materials (see 'plots' folder [https://osf.io/dqwh5/](https://osf.io/dqwh5/)).
-Where there were more substantial changes from prior to posterior these typically revealed a reduction in the magnitude of SMD estimate e.g., for fine tasks in the motor demands model (Hatzigeorgiadis et al.
+Where there were more substantial changes from prior to posterior these typically revealed a shift in the magnitude of SMD estimate towards the overall pooled estimate from the main model e.g., for fine tasks in the motor demands model (Hatzigeorgiadis et al.
 [-@hatzigeorgiadisSelfTalkSportsPerformance2011] = 0.67 [95% confidence interval: 0.53, 0.82]; posterior pooled estimate = `r round(tidy_motor_demands_model$estimate[1],2)` [95% quantile interval: `r round(tidy_motor_demands_model$conf.low[1],2)`, `r round(tidy_motor_demands_model$conf.high[1],2)`]), instructional in the self-talk content model (Hatzigeorgiadis et al.
@@
 ## Examining the quality of the evidence and potential questionable research practices
+```{r}
+targets::tar_load(tidy_pet_model)
+targets::tar_load(tidy_rma.mv_model)
+targets::tar_load(null_robma_model)
+targets::tar_load(prior_robma_model)
+targets::tar_load(tidy_p_hack_model)
+targets::tar_load(tidy_classic_model)
+targets::tar_load(tidy_p_hack_model_prior)
+targets::tar_load(tidy_classic_model_prior)
+
+targets::tar_load(p_hack_models_plots)
+
+```
+
+```{r}
+#| label: fig-contour-plot 
+#| fig-width: 5
+#| fig-height: 5
+#| fig-cap: Countour enhanced funnel plot showing effect sizes (scaled in size by inverse sampling variance), thresholds for *p* < 0.05 and 0.01, and both PET-PEESE estimate (in this case it is the PET estimate from the conditional estimator; regression line and ribbon plus "Multilevel PET Estimate" labelled point and interval) and frequentist multilevel model estimate ("Main Model Estimate" labelled point and interval).
+targets::tar_load(main_model_contour_funnel_plot)
+
+main_model_contour_funnel_plot
+
+```
+
+When considering only the new studies published since Hatzigeorgiadis et al.
+[-@hatzigeorgiadisSelfTalkSportsPerformance2011] the frequentist multilevel model estimate (`r round(tidy_rma.mv_model$estimate[1],2)` [95% confidence interval: `r round(tidy_rma.mv_model$conf.low[1],2)`, `r round(tidy_rma.mv_model$conf.high[1],2)`]) was very similar to both their prior estimate, and also the posterior Bayesian estimate from our updated model (see section above).
+For the conditional PET-PEESE estimator however the PET estimate was not statistically significant at the $\alpha=0.10$ level and this adjusted estimate was compatible with a range of estimates from negative effects of similar magnitude to the previosly reported positive effect in Hatzigeorgiadis et al.
+[-@hatzigeorgiadisSelfTalkSportsPerformance2011], through to null and trivial positive(`r round(tidy_pet_model$estimate[1],2)` [95% confidence interval: `r round(tidy_pet_model$conf.low[1],2)`, `r round(tidy_pet_model$conf.high[1],2)`]) suggesting that publication bias/small study effects may be present in this literature.
+These estimates can be seen in the contour enhanced funnel plot in @fig-contour-plot.
+
+```{r}
+#| label: fig-phack-plot 
+#| fig-width: 5
+#| fig-height: 5
+#| fig-cap: Countour enhanced funnel plot showing effect sizes (scaled in size by inverse sampling variance), thresholds for *p* < 0.05 and 0.01, and both PET-PEESE estimate (in this case it is the PET estimate from the conditional estimator; regression line and ribbon plus "Multilevel PET Estimate" labelled point and interval) and frequentist multilevel model estimate ("Main Model Estimate" labelled point and interval).
+targets::tar_load(main_model_contour_funnel_plot)
+
+main_model_contour_funnel_plot
+
+```
+The Bayesian mixture models assuming the presence of *p*-hacking (note, recall these models ignore the multilevel structure of the effects) also provided reduced adjusted effect estimates, though not to the same magnitude as seen in the PET estimate, with this reduction more prominent when only considering the post-2011 studies and not incorporating the prior from Hatzigeorgiadis et al.
+[-@hatzigeorgiadisSelfTalkSportsPerformance2011].
+Without the prior the estimate from a classic random effects model was `r round(tidy_classic_model$estimate[1],2)` [95% quantile interval: `r round(tidy_classic_model$conf.low[1],2)`, `r round(tidy_classic_model$conf.high[1],2)`] and was reduced to `r round(tidy_p_hack_model$estimate[1],2)` [95% quantile interval: `r round(tidy_p_hack_model$conf.low[1],2)`, `r round(tidy_p_hack_model$conf.high[1],2)`] assuming the presence of *p*-hacking.
+When incorporating the prior from Hatzigeorgiadis et al.
+[-@hatzigeorgiadisSelfTalkSportsPerformance2011] the estimate from a classic random effects model was `r round(tidy_classic_model_prior$estimate[1],2)` [95% quantile interval: `r round(tidy_classic_model_prior$conf.low[1],2)`, `r round(tidy_classic_model_prior$conf.high[1],2)`] and was reduced to `r round(tidy_p_hack_model_prior$estimate[1],2)` [95% quantile interval: `r round(tidy_p_hack_model_prior$conf.low[1],2)`, `r round(tidy_p_hack_model_prior$conf.high[1],2)`] assuming the presence of *p*-hacking.
+These estimates and the posterior distributions can be seen in @fig-phack-plot.
+
+When considering only the post-2011 studies and utilising default prior distributions, robust Bayesian meta-analysis found strong evidence against the effect, $BF_{10}=$`r round(summary(null_robma_model)$components$inclusion_BF[1],3)` with mean model-averaged estimate of `r round(summary(null_robma_model)$estimates$Mean[1],2)` [95% quantile interval: `r round(summary(null_robma_model)$estimates[1,3],2)`, `r round(summary(null_robma_model)$estimates[1,3],2)`, strong evidence in favor of the heterogeneity, $BF_{rf}$ = `r round(summary(null_robma_model)$components$inclusion_BF[2],3)` with mean model-averaged estimate $\tau=$`r round(summary(null_robma_model)$estimates$Mean[2],2)` [95% quantile interval: `r round(summary(null_robma_model)$estimates[2,3],2)`, `r round(summary(null_robma_model)$estimates[2,3],2)`.
+Robust Bayesian meta-analysis found strong evidence in favor of the publication bias, BF_pb = `r round(summary(null_robma_model)$components$inclusion_BF[3],3)`.
+When including the prior from Hatzigeorgiadis et al.
+[-@hatzigeorgiadisSelfTalkSportsPerformance2011] results were similar with robust Bayesian meta-analysis finding strong evidence against the effect, $BF_{10}=$`r round(summary(prior_robma_model)$components$inclusion_BF[1],3)` with mean model-averaged estimate of `r round(summary(prior_robma_model)$estimates$Mean[1],2)` [95% quantile interval: `r round(summary(prior_robma_model)$estimates[1,3],2)`, `r round(summary(prior_robma_model)$estimates[1,3],2)`, strong evidence in favor of the heterogeneity, $BF_{rf}$ = `r round(summary(prior_robma_model)$components$inclusion_BF[2],3)` with mean model-averaged estimate $\tau=$`r round(summary(prior_robma_model)$estimates$Mean[2],2)` [95% quantile interval: `r round(summary(prior_robma_model)$estimates[2,3],2)`, `r round(summary(prior_robma_model)$estimates[2,3],2)`.
+Robust Bayesian meta-analysis found strong evidence in favor of the publication bias, BF_pb = `r round(summary(prior_robma_model)$components$inclusion_BF[3],3)`.
 

### 2024-08-12 _targets.R

@@ -72,10 +72,14 @@ list(
 
   # p-hacking models
   tar_target(p_hack_model, fit_p_hack_model(data_effect_sizes)),
+  tar_target(tidy_p_hack_model, tidy(p_hack_model, conf.int = .95)),
   tar_target(classic_model, fit_classic_model(data_effect_sizes)),
+  tar_target(tidy_classic_model, tidy(classic_model, conf.int = .95)),
   tar_target(p_hack_models_plot, plot_p_hack_models(p_hack_model, classic_model)),
   tar_target(p_hack_model_prior, fit_p_hack_model_prior(data_effect_sizes)),
+  tar_target(tidy_p_hack_model_prior, tidy(p_hack_model_prior, conf.int = .95)),
   tar_target(classic_model_prior, fit_classic_model_prior(data_effect_sizes)),
+  tar_target(tidy_classic_model_prior, tidy(classic_model_prior, conf.int = .95)),
   tar_target(p_hack_models_prior_plot, plot_p_hack_models_prior(p_hack_model_prior, classic_model_prior)),
   tar_target(p_hack_models_plots, plot_panel_p_hack(p_hack_models_plot, p_hack_models_prior_plot)),
 

### 2024-08-15 plots/diagnostic_plots.qmd
Moved diagnostics plots to plots folder

--- 2023-11-25 diagnostic_plots.qmd
@@
 title: "Diagnostic Plots"
-subtitle: "Self-talk interventions and sport/motor performance: An updated systematic review and Bayesian meta-analysis"
+subtitle: "Cumulative evidence synthesis and consideration of 'research waste' using Bayesian methods: An example updating a previous meta-analysis of self-talk interventions for sport/motor performance"
 author: "Hannah Corcoran, James Steele"
@@
 ---
+```{r,message=FALSE,warning=FALSE,echo=FALSE}
+targets::tar_config_set(store = here::here('_targets'))
+
+```
+
 # Main Model

### 2024-08-15 pre_print/response_to_reviewers.qmd
All revisions to preprint finished

--- 2024-07-23 response_to_reviewers.qmd
@@
 title: "Response to Reviewers"
-subtitle: "Updating meta-analyses cumulatively using Bayesian methods: An example updating a previous meta-analysis of self-talks interventions for sport/motor performance"
+subtitle: "Cumulative evidence synthesis and consideration of 'research waste' using Bayesian methods: An example updating a previous meta-analysis of self-talk interventions for sport/motor performance"
 format: pdf
@@
 
-Dear \[insert editor name\],
+Dear Professor Wolff,
 
-Many thanks for considering our manuscript and placing it under review with \[insert journal name\].
+Many thanks for considering our manuscript and placing it under review with *Peer Community in Health and Movement Sciences*.
 We are very grateful for your efforts in obtaining reviews.
@@
 
-Note, because of the extensive rewrite of the manuscript due to the shift in focus we have not used track changes or highlighting throughout, though changes can be viewed in the GitHub repository versions.
+Note, because of the extensive rewrite of the manuscript due to the shift in focus we have not used track changes or highlighting throughout, though changes can be viewed in the GitHub repository commits and versions.
 However, please see below for our comments in response to some of the key points raised by the reviewers.
@@
 
-# Reviewer Comments and [Author Responses]{style="color:red;"}
+# Reviewer Comments and Author Responses
 
@@
 
-### [Author Response]{style="color:red;"}
+### Author Response
 
-[Thank you for your suggestion.
+Thank you for your suggestion.
 It is actually a point which in retrospect after submitting the manuscript we realised more ourselves and so it is gratifying to have this reinforced by both reviewers.
@@
 as closely as possible.
-As this was an undergraduate project being completed in a short period of time we opted to try to replicate to make the project more efficient under such constraints.
+As this was an undergraduate project being completed in a short period of time we opted to try to replicate and update to make the project more efficient under such constraints.
 We did initially intend though to include a PRISMA flow diagram to describe our updated searches, however we encountered an issue and realised that some of the searches we had conducted were not correctly recorded by the tool being used to manage the process.
-Unfortunately we were unable to exactly replicate it from attempting to reproduce the searches again.
-We have added this detail to footnote 2 for transparency.]{style="color:red;"}
+Unfortunately we were unable to exactly replicate the searches despite attempting to reproduce the searches again.
+We have added this detail to footnote 2 for transparency.
 
-[We do agree though that positioning this paper instead as an example of using Bayesian meta-analytic methods for cumulative science, whilst using the self-talk literature as an exemplar case-study given how long it has been since a quantitative evidence synthesis was conducted, is perhaps more suitable.
-As such we have attempted to rewrite the manuscript with this in mind, and have also changed the title to: *Cumulative evidence synthesis using Bayesian methods: An example updating a previous meta-analysis of self-talks interventions for sport/motor performance*]{style="color:red;"}
+We do agree though that positioning this paper instead as an example of using Bayesian meta-analytic methods for cumulative science, whilst using the self-talk literature as an exemplar case-study given how long it has been since a quantitative evidence synthesis was conducted, is perhaps more suitable.
+As such we have attempted to rewrite the manuscript with this in mind, and have also changed the title to: *Cumulative evidence synthesis and consideration of "research waste" using Bayesian methods: An example updating a previous meta-analysis of self-talk interventions for sport/motor performance*
 
@@
 
-### [Author Response]{style="color:red;"}
+### Author Response
 
-[Given the reframing of the paper, we have now subsectioned the introduction and include a section more explicitly introducing self-talk.]{style="color:red;"}
+[Given the reframing of the paper, we have now subsectioned the introduction and include a section more explicitly introducing self-talk.
 
@@
 
-### [Author Response]{style="color:red;"}
+### Author Response
 
-[This is an interesting, and somewhat counterintuitive result of our analysis.
-From the additional work we have conducted whereby we have utilised simulation to add a single new study and explore it's effects upon the prior distribution we were surprised that even a study simulated with one millions participants and a null effect had next to no impact in updating the prior estimate.
-As a result we conducted a little additional exploration regarding how the prior distribution was set.
+This is an interesting, and somewhat counterintuitive result of our analysis.
+From the additional work we have conducted whereby we have utilised simulation to add a single new study and explore it's effects upon the prior distribution we were surprised that even a study simulated with a large sample of participants and either a null or large effect had next to no impact in updating the prior estimate.
+These simulations have been added into the manuscript as an example of what can be done in determining whether a prior estimate is already precise enough.
+
+However, we conducted a little additional exploration regarding how the prior distribution was set to better understand this.
 We utilised a $t$-distribution ($t(k,\mu,\sigma)$) with $k-2$ degrees of freedom as suggested by Higgins et al.
@@
 To our interpretation this goes to show how certain the estimate from Hatzigeorgiadis et al.
-already was and highlights that further intervention research could be considered wasteful (assuming it has not contributed anything else to our understanding).
-However, as we explain in response to reviewer 2, we have now examined using various methods the possibility of small sample and publication bias in the studies included since 2011.
-This paints a concerning picture to our interpretation, though one that is perhaps not that surprising given that there is widespread evidence of such questionable research practices across many fields including the sport and exercise sciences.
+already was and highlights that further intervention research could be considered wasteful (assuming it has not contributed anything additional to our understanding).
+But, as we explain in response to reviewer 2, we have now examined using various methods the possibility of small sample and publication bias in the studies included since 2011.
+We think this paints a concerning picture, though one that is perhaps not that surprising given that there is widespread evidence of such questionable research practices across many fields including the sport and exercise sciences.
 Hatzigeorgiadis et al.
@@
 for pre-2011.
-However, we have contacted the authors and asked for whether they still have their extracted data such that we might be able to examine this in the pre-2011 studies.]{style="color:red;"}
+However, we have contacted the authors and asked for whether they still have their extracted data such that we might be able to examine this in the pre-2011 studies.
+We will be happy to update the manuscript with this if the authors make it available to us.
 
-```         
 ### Reviewer Comment
@@
 
-    ### [Author Response]{style="color:red;"}
-    []{style="color:red;"}
-```
+### Author Response
+
+We have now noted this shift towards the overall pooled effect and also included additional commentary on it in the discussion.
+We also relate this to the comments regarding whether or not the goals of studies were to examine self-talk interventions or more specific questions regarding mediators to highlight that even in this regard the newer evidence has not added a great deal to update our beliefs.
 
@@
 
-### [Author Response]{style="color:red;"}
+### Author Response
 
-[This is certainly a possibility and we have tried to soften the language regarding "research waste" somewhat throughout and also emphasise this limitation more in the discussion.
-We had considered in light of this comment whether to conduct a qualitative appraisal of the included studies to determine the extent to which they had either merely estimated the effects of self-talk interventions or explored moderators which were already well understood (though this we now question due to the possibility of publication bias in main effects) as opposed to contributing something new theoretically or methodologically.
-However, given the shift in the focus of the manuscript we opted not to do so but instead to highlight this as something those engaged in cumulative evidence synthesis should consider as well when determining whether research could be considered wasteful, or in the justification of a new trial by dint of the fact it might address theoretically or methodologically novel considerations.]{style="color:red;"}
+This is certainly a possibility and we initially in revising tried to soften the language regarding "research waste" somewhat throughout.
+But, given the minimal impact upon estimates of theoretically informed moderators and the concerns we have now raised regarding publication bias and QRPs we do still find it difficult to conclude anything other than that a lot of the research could indeed be considered wasteful.
+We had considered in light of this comment whether to conduct a qualitative appraisal of the included studies to determine the extent to which they had either merely estimated the effects of self-talk interventions or explored moderators which were already well understood (though this we now question due to the possibility of bias in prior estimates of main effects anyway) as opposed to contributing something new theoretically or methodologically.
+However, given the shift in the focus of the manuscript we opted not to do so but instead to highlight this as something those engaged in cumulative evidence synthesis should consider as well when determining whether research could be considered wasteful, or in the justification of a new trial by dint of the fact it might address theoretically or methodologically novel considerations.
 
@@
 
-### [Author Response]{style="color:red;"}
+### Author Response
 
-[We have now attempted to address this concern through the addition of simulations of the effects that a new study might have had post the meta-analysis of Hatzigeorgiadis et al.
+We have now attempted to address this concern through the addition of simulations of the effects that a new study might have had post the meta-analysis of Hatzigeorgiadis et al.
 in terms of changing our conclusions regarding the effect.
-This lends some quantitative precision the the claim that it was already fairly precise adn that further research may have been unwarranted.
-Of course there may be other reasons to continue further research attempting to replicate an effect, though in this case we'd be skeptical that it is warranted.]{style="color:red;"}
+This lends some quantitative precision the the claim that it was already fairly precise and that further research may have been unwarranted.
+Of course there may be other reasons to continue further research attempting to replicate an effect, and indeed in this case it could be argued that further research might be needed following more modern open research practices including pre-registration and sufficient power/precision for effect estimation in order to actually establish in light of the presences of publication bias and QRPs whether self-talk interventions actually have an effect at all anyway.
 
@@
 
-### [Author Response]{style="color:red;"}
+### Author Response
 
-[Given the reframing we instead have added discussion of the benefits of engaging with the kinds of methods demonstrated, but have also noted that supplementing this with qualitative appraisal is of value in determining wwhether addtional research is warranted.]{style="color:red;"}
+Given the reframing we instead have added discussion of the benefits of engaging with the kinds of methods demonstrated, but have also noted that supplementing this with qualitative appraisal is of value in determining whether additional research is warranted.
 
@@
 
-### [Author Response]{style="color:red;"}
+### Author Response
 
-[This is a good question and one which we encounter often.
+This is a good question and one which we encounter often.
 Specifically in a random effects meta-analysis the overall main estimate is the weighted average of the effect*s* that each study has estimated.
@@
 In addition, the moderator analyses allow for us to explore whether or not study, experiment, or group level factors might be influences of the effects that each study estimates within the overarching distribution of effects.
-So, we would argue that in the case of asking the question about the effects of an intervention, such as self-talk upon an outcome, such as sport/motor performance, meta-analysis can be appropriate if conducted appropriately.]{style="color:red;"}
+So, we would argue that in the case of asking the question about the effects of an intervention, such as self-talk upon an outcome, such as sport/motor performance, meta-analysis can be appropriate if conducted appropriately.
 
@@
 
-### [Author Response]{style="color:red;"}
+### Author Response
 
-[Thank you for this suggestion.
+Thank you for this suggestion.
 Somewhat in our haste and our focus on the updating aspect of the novel approach taken, we failed to consider this.
 However, we have now examined using various methods the possibility of small sample and publication bias in the studies included since 2011.
-The PET-PEESE and Robust Bayesian Model Averaging methods reveal evidence of publication bias and that the adjusted effect may in fact be null.
+The PET-PEESE, mixture model for *p*-hacking, and robust Bayesian meta-analysis model averaging methods reveal evidence of publication bias and *p*-hacking and that the adjusted effect may in fact be null considering the former.
 This paints a concerning picture to our interpretation, though one that is perhaps not that surprising given that there is widespread evidence of such questionable research practices across many fields including the sport and exercise sciences.
@@
 for pre-2011.
-However, we have contacted the authors and asked for whether they still have their extracted data such that we might be able to examine this in the pre-2011 studies.]{style="color:red;"}
+However, we have contacted the authors and asked for whether they still have their extracted data such that we might be able to examine this in the pre-2011 studies.
+We will be happy to update the manuscript with this if the authors make it available to us.
 
@@
 
-### [Author Response]{style="color:red;"}
+### Author Response
 
-[Reviewer 1 also raised this concern and we have tried to soften the language regarding "research waste" somewhat throughout and also emphasise this limitation more in the discussion.
-We had considered in light of this comment whether to conduct a qualitative appraisal of the included studies to determine the extent to which they had either merely estimated the effects of self-talk interventions or explored moderators which were already well understood (though this we now question due to the possibility of publication bias in main effects) as opposed to contributing something new theoretically or methodologically.
-However, given the shift in the focus of the manuscript we opted not to do so but instead to highlight this as something those engaged in cumulative evidence synthesis should consider as well when determining whether research could be considered wasteful, or in the justification of a new trial by dint of the fact it might address theoretically or methodologically novel considerations.]{style="color:red;"}
+Reviewer 1 also raised this concern and as mentioned we orginally in revising this work tried to soften the language regarding "research waste" somewhat throughout and also emphasise this limitation more in the discussion.
+We had considered in light of this comment whether to conduct a qualitative appraisal of the included studies to determine the extent to which they had either merely estimated the effects of self-talk interventions or explored moderators which were already well understood (though this we now question due to the possibility of bias in prior estimates of main effects anyway) as opposed to contributing something new theoretically or methodologically.
+However, given the shift in the focus of the manuscript we opted not to do so but instead to highlight this as something those engaged in cumulative evidence synthesis should consider as well when determining whether research could be considered wasteful, or in the justification of a new trial by dint of the fact it might address theoretically or methodologically novel considerations.
 
@@
 
-### [Author Response]{style="color:red;"}
+### Author Response
 
-[We have tried to better address this by leveraging simulating the addition a single new study, varying the underlying effect size and sample size, and explore it's effects upon the prior distribution.
-This is to demonstrate that such an approach can aid in determining exactly when the addition of new studies, whether small or indeed large, might be unnecessary in light of current evidence.]{style="color:red;"}
+We have tried to better address this by leveraging simulating the addition a single new study, varying the underlying effect size and sample size, and explore it's effects upon the prior distribution.
+This is to demonstrate that such an approach can aid in determining exactly when the addition of new studies, whether small or indeed large, might be unnecessary in light of current evidence.
 
@@
 
-### [Author Response]{style="color:red;"}
+### Author Response
 
-[As noted we have tried to make it clear that such qualitative considerations should also be taken into account when determining whether research has been wasteful, or indeed further research might be.
-Although, for the specific example of self-talk the process of working on this project has been enlightening and left us in considerable doubt of the value of much of the research in the area (though notably that would be the case for many areas within the sport and exercise sciences).]{style="color:red;"}
+As noted we have tried to make it clear that such qualitative considerations should also be taken into account when determining whether research has been wasteful, or indeed further research might be.
+Although, for the specific example of self-talk the process of working on this project has been enlightening and left us in considerable doubt of the value of much of the research in the area (though notably that would be the case for many areas within the sport and exercise sciences...
+unfortunately we've become somewhat cynical).

### 2024-08-15 pre_print/_extensions/smnnlt/sportrxiv/partials/before-body.tex
All revisions to preprint finished

$-- Implements the frontmatter, title page, and abstract.
$--
$-- %%%% TODO %%%%%
$-- Customize is needed, otherwise remove this partials to use Quarto default one
$-- %%%%%%%%%%%%%%%%

% set short author name
\newcounter{nauthor}
$for(by-author)$\stepcounter{nauthor}$endfor$
\ifnum\thenauthor>2
\renewcommand{\shortauthor}{$author/first$ et al. }
\else 
\renewcommand{\shortauthor}{${ for(by-author) }${ by-author.name.family }${ sep } \& ${ endfor } }
\fi

\pagestyle{fancy}
\fancyhead[L]{$if(shorttitle)$$shorttitle$$else$\shortauthor$ if(year)$($year$)$else$(\the\year)$endif$$endif$}
\fancyhead[R]{}
\fancypagestyle{firstpage}{
  \fancyhf{}% clear default for head and foot
  \lhead{\href{https://sportrxiv.org}{\includegraphics[width = 40mm]{logo.png}}}
  \chead{$printnote$}
  \rhead{\$license-type$\vspace{0.2mm}}
  \lfoot{\color{gray}All authors have read and approved  this version  of the manuscript. \linebreak The manuscript was last updated on \today}
}
\begin{flushleft}
\begin{spacing}{2.5}
\thispagestyle{firstpage}
\vspace*{0.1cm}
{\huge{\textbf{$articletitle$}}}
\end{spacing}
\vspace*{0.1cm}
$by-author:_authors.tex()[, ]$
\\
\bigskip
$by-affiliation:_affiliations.tex()[\\ ]$
\\
\bigskip
*Correspondence: 
$for(by-author)$
$if(by-author.attributes.corresponding)$
\href{mailto:$by-author.email$}{\color{black}$by-author.email$}
$endif$
$endfor$
\\
\bigskip
\begin{spacing}{1}
Cite as: \shortauthor$if(year)$($year$)$else$(\the\year)$endif$. $articletitle$. \emph{SportRxiv.} \\
\end{spacing}
$if(suppl-link)$
  \vspace{1mm} Supplementary Materials: \href{$suppl-link$}{$suppl-link$} \\
$endif$
\vspace*{1cm}
\end{flushleft}

\newenvironment{abstractbox}
  {}

\surroundwithmdframed[
  backgroundcolor=SRXIVgreen,
  innertopmargin=10pt,
  innerbottommargin=10pt,
  linewidth=2pt,
  linecolor=gray!30,
  leftmargin=20pt,
  rightmargin=20pt,
  frametitle={\large{Abstract}},
]{abstractbox}

\begin{abstractbox}
  $abstract$ 
  $if(keywords)$
  \\ \\
  Keywords: \emph{${for(keywords)}${keywords}${sep}; ${endfor}}
  $endif$ 
\end{abstractbox}

### 2024-08-15 pre_print/pre_print_v2.qmd
All revisions to preprint finished

--- 2024-08-12 pre_print_manuscript.qmd
@@
 articletitle: |
-  Cumulative evidence synthesis using Bayesian methods: An example updating a previous meta-analysis of self-talk interventions for sport/motor performance
+  Cumulative evidence synthesis and consideration of "research waste" using Bayesian methods: An example updating a previous meta-analysis of self-talk interventions for sport/motor performance
 format: 
@@
 abstract: |
-  Self-talk has been researched as an aspect of mental preparation for performance in sports and other motor tasks since the late 1980s.
-In 2011, Hatzigeorgiadis and colleagues systematically reviewed and meta-analysed three decades of self-talk intervention research including 32 studies.
-Yet, despite the general proliferation of meta-analyses, this topic has not been meta-analysed in the decade since their review which, at least for the main effect, provided a reasonably precise standardised mean difference estimate (0.48 [95% confidence interval: 0.38, 0.58]).
-Several further studies on self-talk interventions have been conducted in that time and it is of interest to explore what additional evidence they offer regarding the effects of self-talk interventions on sport/motor performance.
-Bayesian approaches are well positioned to explore how additional evidence changes our understanding of an effect; to see whether it has changed in sign, magnitude, or precision, or whether further research has largely been a ‘waste’.
+  In the present paper we demonstrate the application of methods for cumulative evidence synthesis including Bayesian meta-analysis, and exploration of questionable research practices such as publication bias or *p*-hacking, in the sport and exercise sciences for the evaluation of experimental interventions.
+The use of such methods can aid in study planning and avoid "research waste".
+In demonstrating and discussing these methods we use the example of self-talk interventions and their effects upon sport/motor performance given a quantitative evidence synthesis has not been conducted on this topic, to the best of our knowledge, since 2011 when Hatzigeorgiadis et al.
+[-@hatzigeorgiadisSelfTalkSportsPerformance2011] conducted their systematic review and meta-analysis.
+As such, this topic is ripe to use in demonstrating cumulative methods such as Bayesian updating.
 Therefore, our aim was to conduct an updated systematic review and Bayesian meta-analysis replicating the search, inclusion, and models of Hatzigeorgiadis et al.
-(2011).
-Informative priors were taken directly from Hatzigeorgiadis et al.
-A total of 34 studies providing 128 effects nested in 64 groups across experiments 42 were included in the final updated meta-analysis representing data from 18761 participants.
-The overall posterior pooled estimate for the standardised mean difference was almost exactly the same as the prior: 0.47 [95% quantile interval: 0.39, 0.56].
-Bayes factors were calculated for a range of effect sizes and indicated that the included studies largely reflected ‘Weak’ evidence against effects ranging from 0.30 to 0.59, and only provided ‘Decisive’ evidence or greater against more extreme effects: either very small (i.e., <0.02) or large (i.e., >0.81).
-Results were largely similar for all moderator analyses which were updated too; either providing relatively weak evidence against effects found in the previous meta-analysis or evidence suggesting smaller effects for certain moderators.
-The findings of our updated Bayesian meta-analyses reiterate the positive effect of self-talk interventions on sport/motor performance.
-However, they also suggest that cumulatively the past decade and more of research has done little to further our understanding of these effects.
-Considering the limited resources and time for conducting research, it may be worth moving onto other more pertinent questions regarding psychological constructs impact upon sport/motor performance.
+[-@hatzigeorgiadisSelfTalkSportsPerformance2011] and demonstrate the application of cumulative evidence synthesis methods including; consideration of the initial probability that a new study of the effects of self-talk interventions would shift our prior belief in their effectiveness, the application of priors taken from the previous meta-analysis to be updated by new studies identified to a new posterior estimate of effect, and consideration of other possible sources of research waste from questionable research practices such as publication bias and *p*-hacking.
+Such methods as those demonstrated here, when used prospectively, can aid researchers in determining whether further research of a particular experimental intervention is in fact warranted.
+Considering the limited resources and time for conducting research we hope that highlighting the application of these methods might help researchers in the field to avoid research waste and more productively direct their research efforts.
 license-type: ccby # change if neccessary
@@
 printnote: "PREPRINT - NOT PEER REVIEWED" # if post print, include "POSTPRINT" then link to the published article
-bibliography: references.bib  
+bibliography: 
+  - references.bib
 pdf-engine: xelatex
@@
 library(kableExtra)
+
+targets::tar_config_set(store = here::here('_targets'))
 ```
-
-###### STUFF TO ADD??
-https://systematicreviewsjournal.biomedcentral.com/articles/10.1186/s13643-022-02096-y
-
-https://academic.oup.com/biometrics/article/79/1/319/7478096?login=false
-
-https://www.researchgate.net/publication/338878953_p-Hacking_and_Publication_Bias_Interact_to_Distort_Meta-Analytic_Effect_Size_Estimates
-
-https://www.researchgate.net/publication/336963847_Toward_a_common_language_categorization_and_better_assessment_in_self-talk_research_Commentary_on_Speaking_clearly_10_years_on
-
-https://www.researchgate.net/publication/312934559_On_Investigating_Self-Talk_A_Descriptive_Experience_Sampling_Study_of_Inner_Experience_During_Golf_Performance
-
-https://www.researchgate.net/publication/337822503_Strengthening_the_Assessment_of_Self-Talk_in_Sports_Through_a_Multi-Method_Approach
-
-https://www.researchgate.net/publication/304398817_Why_Self-Talk_Is_Effective_Perspectives_on_Self-Talk_Mechanisms_in_Sport
-
 # Introduction
 ## Cumulative evidence synthesis 
-Two questions that should be asked (though arguably are not asked often enough particularly in sport science) by researchers when planning a study of an experimental intervention is "what is the likelihood that the experimental intervention is superior to the control intervention given the evidence accumulated so far?", and "what is the likelihood that a new trial, given some design parameters and previous evidence, will demonstrate the superiority of the experimental intervention?".
+Two questions that should be asked (though arguably are not asked often enough particularly in sport and and exercise science) by researchers when planning a study of an experimental intervention is *"what is the likelihood that the experimental intervention is superior to the control intervention given the evidence accumulated so far?"*, and *"what is the likelihood that a new trial, given some design parameters and previous evidence, will demonstrate the superiority of the experimental intervention?"*.
 The key here is to consider the *cumulative* nature of evidence provided by research and its synthesis.
 Indeed, to not do this could lead to redundancy or so called "research waste".
-Evidence synthesis methods are essential to determining whether or not there is justification for further research on a given topic, and the Cochrane-Collaboration and REWARD (Reduce Research Waste and Reward Diligence) Alliance have even established an award for efforts in the area of reducing "research waste" [@glasziouResearchWasteStill2018].
+Evidence synthesis methods are essential to determining whether or not there is justification for further research on a given topic, and the Cochrane-Collaboration and REWARD (Reduce Research Waste and Reward Diligence) Alliance have even established an award for efforts in the area of reducing "research waste" [@glasziouResearchWasteStill2018a].
 However, across many domains there remains a high prevalence of redundancy and a low prevalence of attempts to minimise or reduce it [@lundMetaresearchEvaluatingRedundancy2022].
@@
 Meta-analyses rely on the assumption that the sample of studies included is not based on a biased selection procedure either on the part of the systematic reviewer(s) or with regards to the studies present in the literature to sample from.
-For the latter, publication bias and *p*-hacking are the two most common phenomena that violate this assumption and can substantial influence cumulative evidence [@friesePHackingPublicationBias2020].
-Publication bias is typically explored using methods such as selection models based on significance thresholds for *p*-values [@mcshaneAdjustingPublicationBias2016], funnel plot based regression methods [@stanleyMetaregressionApproximationsReduce2014], or methods which combine these approaches and leverage the uncertainty in the underlying true data generating process such as Robust Bayesian Meta-Analysis with model averaging [@bartosAdjustingPublicationBias2022; @bartosRobustBayesianMetaanalysis2023].
-For *p*-hacking mixture models have recently been proposed [@mossModellingPublicationBias2023].
-The existence of evidence suggesting prior questionable research practices such as publication bias or *p*-hacking in previous literature might be cause for an evaluation of whether a research program regarding an experimental intervention is worth building upon, or starting afresh incorporating safe-guards for such issues e.g., pre-registration/registered-reports [@chambersPresentFutureRegistered2022].
+For the latter, publication bias and *p*-hacking are the two most common phenomena that violate this assumption and can substantially influence cumulative evidence [@friesePHackingPublicationBias2020].
+Publication bias is typically explored using methods such as selection models based on significance thresholds for *p*-values [@mcshaneAdjustingPublicationBias2016], funnel plot based regression methods [@stanleyMetaregressionApproximationsReduce2014], or methods which combine these approaches and leverage the uncertainty in the underlying true data generating process such as robust Bayesian meta-analysis (RoBMA) with model averaging [@bartosAdjustingPublicationBias2022; @bartosRobustBayesianMetaanalysis2023].
+For *p*-hacking, mixture models have recently been proposed [@mossModellingPublicationBias2023].
+The existence of evidence suggesting prior questionable research practices such as publication bias or *p*-hacking in previous literature might be cause for an evaluation of whether a research program regarding an experimental intervention is worth building upon, or starting afresh to determine if there really is an intervention effect whilst incorporating safe-guards for such issues e.g., pre-registration/registered-reports [@chambersPresentFutureRegistered2022].
 
 In the present paper we demonstrate the application of methods for cumulative evidence synthesis including Bayesian meta-analysis, and exploration of questionable research practices such as publication bias or *p*-hacking, in the sport and exercise sciences for the evaluation of experimental interventions.
-We assume some prior knowledge of evidence synthesis and meta-analytic methods on the part of the reader, though for those unfamiliar suggest some recent introductory papers regarding their application in the field [@gunnellQuestionsAnswersConducting2020; @haggerMetaanalysis2022; @steeleMetaanalysisVariationSport2023].
-We use the example of self-talk interventions and their effects upon motor/sport performance given a quantitative evidence synthesis has not been conducted on this topic to the best of our knowledge since 2011 when Hatzigeorgiadis et al.
-[-@hatzigeorgiadisSelfTalkSportsPerformance2011] conducted their systematic review and meta-analysis, and thus is ripe to use in demonstrating cumulative methods such as Bayesian updating.
+We assume some prior knowledge of evidence synthesis and meta-analytic methods on the part of the reader, though for those unfamiliar suggest some recent introductory papers regarding their application in the field [@gunnellQuestionsAnswersConducting2020a; @haggerMetaanalysis2022; @steeleMetaanalysisVariationSport2023a].
+We use the example of self-talk interventions and their effects upon sport/motor performance given a quantitative evidence synthesis has not been conducted on this topic, to the best of our knowledge, since 2011 when Hatzigeorgiadis et al.
+[-@hatzigeorgiadisSelfTalkSportsPerformance2011] conducted their systematic review and meta-analysis.
+As such, it is a ripe topic to use in demonstrating cumulative methods such as Bayesian updating.
 Note, we do not intend to present this paper as a comprehensive systematic review and meta-analysis of self-talk interventions in sport/motor performance nor a thorough theoretical review of the construct.
@@
 For example, a recent umbrella review identified thirty meta-analyses exploring the effects of different sport psychology constructs upon performance, thirteen of them examining the effects of interventions, finding an overall standardised mean difference (SMD) for positive constructs of 0.51 \[95% confidence interval: 0.42, 0.58\] [@lochbaumSportPsychologyPerformance2022].
-One construct with a long history of philosophical, theoretical, and empirical work [@geurtsMakingSenseSelf2018; @brinthauptSelftalkResearchChallenges2023; @latinjakSelfTalkInterdisciplinaryReview2023] that has been the target of considerable investigation in this field has been self-talk.
+One construct with a long history of philosophical, theoretical, and empirical work that has been the target of considerable investigation in this field has been self-talk [@geurtsMakingSenseSelf2018; @brinthauptSelftalkResearchChallenges2023; @latinjakSelfTalkInterdisciplinaryReview2023].
 
 As a concept self-talk has been  defined in various ways in previous work on the topic; though recent transdisciplinary review [@latinjakSelfTalkInterdisciplinaryReview2023] has agreed upon a broad conceptualisation: *"verbalizations addressed to the self, overtly or covertly, characterized by interpretative elements associated to their content; and it [self-talk] either (a) reflects dynamic interplays between organic, spontaneous and goal-directed cognitive processes or (b) conveys messages to activate responses through the use of predetermined cues developed strategically, to achieve performance-related outcomes"* [@latinjakSpeakingClearly102019].
-However as noted, whilst there has been various narrative syntheses of research on self-talk [@vanraalteSelftalkReviewSportspecific2016; @hardyReflectionsMaturingResearch2018; @latinjakSelfTalkInterdisciplinaryReview2023], only one systematic review and meta-analysis has explored the effects of self-talk interventions; Hatzigeorgiadis et al.
+Whilst there has been various narrative syntheses of research on self-talk in the past decade [@vanraalteSelftalkReviewSportspecific2016; @hardyReflectionsMaturingResearch2018; @latinjakSelfTalkInterdisciplinaryReview2023], only one systematic review and meta-analysis has explored the effects of self-talk interventions; Hatzigeorgiadis et al.
 [-@hatzigeorgiadisSelfTalkSportsPerformance2011].
@@
 
-Whilst self-talk as a field may have matured in the post-2011 years with theoretical advancements in conceptualisation of the construct and mediators of its effects on performance, efforts to improve operationalisation/measurement, and efforts to improve methodology used in studying self-talk [@brinthauptSelftalkResearchChallenges2023; @geurtsMakingSenseSelf2018; @hardyReflectionsMaturingResearch2018; @latinjakSelfTalkInterdisciplinaryReview2023; @vanraalteSelftalkReviewSportspecific2016; @latinjakSpeakingClearly102019], it could be argued that understanding of the effectiveness of self-talk *interventions* (referred to in modern literature as 'strategic' self-talk; @latinjakSpeakingClearly102019) was "mature" prior to 2011.
+Whilst self-talk as a field may have matured in the post-2011 years with theoretical advancements in conceptualisation of the construct and proposed mediators of its effects on performance, efforts to improve operationalisation, and efforts to improve methodology used in studying self-talk [@brinthauptSelftalkResearchChallenges2023; @geurtsMakingSenseSelf2018; @hardyReflectionsMaturingResearch2018; @latinjakSelfTalkInterdisciplinaryReview2023; @vanraalteSelftalkReviewSportspecific2016; @latinjakSpeakingClearly102019; @vanraalteCommonLanguageCategorization2019], it could be argued that understanding of the effectiveness of self-talk *interventions* (referred to in modern literature as 'strategic' self-talk; @latinjakSpeakingClearly102019) was "mature" prior to 2011.
 The effect estimate from the meta-analysis of Hatzigeorgiadis et al.
-[-@hatzigeorgiadisSelfTalkSportsPerformance2011] might be considered by some to have been already fairly precise only spanning 0.2 SMD, and indeed aswell for many of the moderator estimates.
+[-@hatzigeorgiadisSelfTalkSportsPerformance2011] might be considered by some to have been already fairly precise only spanning 0.2 SMD, and also for many of the moderator estimates.
 Indeed, some authors had moved onto to attempting to explain *why* self-talk interventions are effective, exploring possible mechanisms with the starting assumption that these interventions had been proven as effective for enhancing performance [@galanisChapterWhySelfTalk2016].
@@
 It may well be that such recent work has further improved our estimates of the effects of self-talk interventions and what moderates their effectiveness, or indeed contributed to other areas of understanding of the construct of self-talk.
-But, it is a reasonable question to ask, given the limited time and resource for conducting research in the field of sport science and what we might claim to have already known regarding these interventions, whether and to what extent these studies have advanced our understanding of their effects, or whether they have largely contributed to so called "research waste" [@graingerEvidenceSynthesisTackling2020; @glasziouResearchWasteStill2018].
+But, it is a reasonable question to ask, given the limited time and resource for conducting research in the field of sport science and what we might claim to have already known regarding these interventions, whether and to what extent these studies have advanced our understanding of their effects, or whether they have largely contributed to so called "research waste" [@graingerEvidenceSynthesisTackling2020; @glasziouResearchWasteStill2018a].
 
@@
 Given that there has not been, to the best of our knowledge, a meta-analytic synthesis of the effects of self-talk interventions effects upon sport/motor performance since Hatzigeorgiadis et al.
-[-@hatzigeorgiadisSelfTalkSportsPerformance2011] it represents a prime topic to utilise as an example for these methods.
+[-@hatzigeorgiadisSelfTalkSportsPerformance2011] it represents a ripe topic to utilise as an example for these methods.
 Therefore, our aim was to conduct an updated systematic review and Bayesian meta-analysis replicating the search, inclusion, and models of Hatzigeorgiadis et al.
@@
 
-Statistical analysis of the data extracted was performed in R, (v 4.2.2; R Core Team, https://www.r-project.org/) and RStudio (v 2023.06.1; Posit, https://posit.co/).
 All code utilised for data preparation and analyses are available in either the Open Science Framework page for this project [https://osf.io/dqwh5/](https://osf.io/dqwh5/) or the corresponding GitHub repository [https://github.com/jamessteeleii/self_talk_meta_analysis_update](https://github.com/jamessteeleii/self_talk_meta_analysis_update).
-
-ADD grateful citation report
-
-    The `renv` package [@usheyRenvProjectEnvironments2023] was used for package version reproducibility and a function based analysis pipeline using the `targets` package [@landauTargetsDynamicFunctionOriented2023] was employed (the analysis pipeline can be viewed by downloading the R Project and running the function `targets::tar_visnetwork()`).
-Standardised effect sizes were all calculated using the `metafor` package [@viechtbauerMetaforMetaAnalysisPackage2023].
-The main package `brms` [@burknerBrmsBayesianRegression2023] was used in fitting all the Bayesian meta-analysis models.
-Prior and posterior draws were taken using `tidybayes` [@kayTidybayesTidyData2023] and `marginaleffects` [@arel-bundockMarginaleffectsPredictionsComparisons2023] packages.
-Bayes factors were calculated using the `bayestestR` package [@makowskiBayestestRUnderstandDescribe2023].
-All visualisations were created using `ggplot2` [@wickhamGgplot2CreateElegant2023], `tidybayes`, and the `patchwork` [@pedersenPatchworkComposerPlots2023] packages.
+We cite all software and packages used in the analysis pipeline using the `grateful` package [@rodriguez-sanchezGratefulFacilitateCitation2023] which can be seen here: [https://osf.io/ftajc](https://osf.io/ftajc).
 
@@
 The same was done drawing samples from the prior distributions only in order to present both distributions visually for comparison of the prior to posterior updating.
-As a means of examining the extent to which the posterior distribution for the self-talk intervention effect estimate was shifted from the prior distribution as a result of introducing each new trial we calculated the proportion of the full posterior distribution within the 95% quantile interval of the prior distribution i.e., the most probable value of the parameter in addition to the range from 2.5% to 97.5% percentiles (equivalent to the 95% confidence interval of the estimate from Hatzigeorgiadis et al.
+As a means of examining the extent to which the posterior distribution for the self-talk intervention effect estimate was shifted from the prior distribution as a result of introducing each new trial we calculated the proportion of the full posterior distribution within the 95% quantile interval of the prior distribution i.e., the range from 2.5% to 97.5% percentiles (equivalent to the 95% confidence interval of the estimate from Hatzigeorgiadis et al.
 [-@hatzigeorgiadisSelfTalkSportsPerformance2011]), using the a Region of Practical Equivalence approach [@kruschkeBayesianNewStatistics2018a].
@@
 Trace plots were produced along with $\hat{R}$ values to examine whether chains had converged, and posterior predictive checks for each model were also examined to understand the model implied distributions.
-These all showed good convergence with all $\hat{R}$ values close to 1 and  posterior predictive checks seemed appropriate distributions for the observed data (all diagnostic plots can be seen in the supplementary materials: [https://osf.io/xbcw8](https://osf.io/xbcw8)).
+These all showed good convergence with all $\hat{R}$ values close to 1 and  posterior predictive checks seemed appropriate distributions for the observed data (all diagnostic plots can be seen in the supplementary materials: [https://osf.io/ag6re](https://osf.io/ag6re)).
 
@@
 [-@hatzigeorgiadisSelfTalkSportsPerformance2011] to enable us to examine the possible presence of questionable research practices that might impact the prior estimate[^8].
-Instead we limit our examination to the subsequent post-2011 literature and make the reasonable assumption that, given the replication crisis and subsequent methodological reform efforts kicked off proper in the early 2010s, the presence of questionable research practices was likely as bad if not worse in the literature included in Hatzigeorgiadis et al.
+Instead we limit our examination to the subsequent post-2011 literature and make the reasonable assumption that, given the current replication crisis and subsequent methodological reform efforts kicked off proper in the early 2010s [@lakensConcernsReplicabilityTheorizing2023], the presence of questionable research practices was likely as bad if not worse in the literature included in Hatzigeorgiadis et al.
 [-@hatzigeorgiadisSelfTalkSportsPerformance2011].
@@
 [-@hatzigeorgiadisSelfTalkSportsPerformance2011] to ask if they could share the extracted data, given it was not openly available, so we could examine this.
-We did not however receive a response.
+We received a responde and are awaiting confirmation as to whether they have the data available still and can share it with us to examine.
+This manuscript will be updated with this if we do receive the extracted data from pre-2011 studies.
 
-Examining the presence of questionable research practices such as publication bias and *p*-hacking in the presences of data with a hierarchical structure such as we have in the present example is not simple.
+Examining the presence of questionable research practices such as publication bias and *p*-hacking in the presence of data with a hierarchical structure such as we have in the present example is not simple.
 The methods noted in the introduction have primarily been developed for cases of fixed or random effects meta-analyses were each study contributes only a single effect in the model.
-However, some approaches have been extended to the hierarchical case such as funnel plot based regression methods [@rodgersEvaluatingMetaanalyticMethods2021] and Robust Bayesian Meta-Analysis (RoBMA) with model averaging [@bartosRobustBayesianMetaanalysis2023].
+However, some approaches have been extended to the hierarchical case such as funnel plot based regression methods [@rodgersEvaluatingMetaanalyticMethods2021] and robust Bayesian meta-analysis (RoBMA) with model averaging [@bartosRobustBayesianMetaanalysis2023].
 However the latter, and in particular the selection methods incorporated, are very computationally intensive making them in most regards practically unfeasible.
@@
 The adjusted estimate was compared to the estimate generated from a multilevel meta-analysis model of the included studies.
-Note, the adjusted PET-PEESE estimate of the intervention effects and the comparative estimate from the multilevel meta-analysis model where both conducted using Frequentist models.
+Note, the adjusted PET-PEESE estimate of the intervention effects and the comparative estimate from the multilevel meta-analysis model where both conducted using frequentist models.
 
-In addition to this we also examined both the random effects mixture model for *p*-hacking [@mossModellingPublicationBias2023] and RoBMA [@@bartosRobustBayesianMetaanalysis2023] (both with, and without, the inclusion of an informative prior[^9] on the intervention effect from Hatzigeorgiadis et al.
+In addition to this we also examined both the random effects mixture model for *p*-hacking [@mossModellingPublicationBias2023] and RoBMA [@bartosRobustBayesianMetaanalysis2023] (both with, and without, the inclusion of an informative prior[^9] on the intervention effect from Hatzigeorgiadis et al.
 [-@hatzigeorgiadisSelfTalkSportsPerformance2011], yet with default priors for all other parameters) though ignored the hierarchical structure to the data as these models respectively have not been extended to the multilevel case or are too computationally intractable at present.
@@
 Bayes Factors were then calculated to examine the evidence in favour of there being an effect, the presence of heterogeneity, and publication bias.
+Bayes factors were interpreted according to Lee and Wagenmakers [-@leeBayesianCognitiveModeling2014] adaptation of Jeffreys [-@jeffreysTheoryProbability1998] scale where between 1 and 3 (between 1 and 1/3) are regarded as anecdotal evidence, Bayes factors between 3 and 10 (between 1/3 and 1/10) are regarded as moderate evidence, and Bayes factors larger than 10 (smaller than 1/10) are regarded as strong evidence in favor of (against) a hypothesis.
 
@@
 [-@hatzigeorgiadisSelfTalkSportsPerformance2011] for these models we used a normal prior with the same location and scale parameters.
-Given the the $t$ distribution approaches the normal distribution with high degrees of freedom, and the prior for other models had a high number of degrees of freedom (i.e., $k=60$), the choice of a normal distribution here very closely approximates the $t$ distribution based prior anyway.
+Given the the $t$ distribution approaches the normal distribution with high degrees of freedom, and the prior for other models had a high number of degrees of freedom (i.e., $k=60$), the choice of a normal distribution here very closely approximates the $t$ distribution based prior anyway and if anything is conservative in examining an adjusted estimate for *p*-hacking.
 
@@
 ## Examining the effects of a new trial upon belief in the effects of self-talk interventions
+
+Given the precision of the prior distribution taken from Hatzigeorgiadis et al.
+[-@hatzigeorgiadisSelfTalkSportsPerformance2011] it is highly unlikely that any further study would have shifted belief in the effect estimate.
+As can be seen in @fig-additional-study, irrespective of the sample size or magnitude of effect and the extent to which it disagreed with the prior estimate, no single new study could shift the posterior distribution to an extent that it didn't still have ~95% of its mass within the 95% quantile interval of the prior distribution.
+As such, if we were to take the prior estimate from Hatzigeorgiadis et al.
+[-@hatzigeorgiadisSelfTalkSportsPerformance2011] at face value in the process of deciding whether to conduct a new study of self-talk interventions, at least with respect to their main effects on sport/motor performance, we should likely conclude that it would be a waste of resources given the precision of this existing estimate of the intervention effect.
+Of course, this only considers the addition of a single study and as noted since 2011 the number of studies examining self-talk interventions has roughly doubled.
+As such, it is worth considering the extent to which this volume of additional evidence might have updated belief in the estimate of their effects.
 ```{r}
@@
 ```
-Given the precision of the prior distribution taken from Hatzigeorgiadis et al.
-[-@hatzigeorgiadisSelfTalkSportsPerformance2011] it is highly unlikely that any further study would have shifted belief in the effect estimate.
-As can be seen in @fig-additional-study, irrespective of the sample size or magnitude of effect and the extent to which it disagreed with the prior estimate, no single new study could shift the posterior distribution to an extent that it didn't still have ~95% of its mass within the 95% quantile interval of the prior distribution.
-As such, if we were to take the prior estimate from Hatzigeorgiadis et al.
-[-@hatzigeorgiadisSelfTalkSportsPerformance2011] at face value in the process of deciding whether to conduct a new study of self-talk interventions, at least with respect to their main effects on sport/motor performance, we should likely conclude that it would be a waste of resources given the precision of this existing estimate of the intervention effect.
-Of course, this only considers the addition of a single study and as noted since 2011 the number of studies examining self-talk interventions has roughly doubled.
-As such, it is worth considering the extent to which this volume of additional evidence might have updated belief in the estimate of their effects.
 
@@
 
-Considering the log10(BF) values calculated against the range of SMD effect sizes from 0 to 1 compared to Jeffreys scale (see @fig-main-model panel [C]), the newly added evidence suggested that there was only "Decisive" evidence updating the prior against effect sizes ranging from 0 to `r round(Jeffreys_scales$max_effect[1],2)` and from `r round(Jeffreys_scales$min_effect[2],2)` to `r round(Jeffreys_scales$max_effect[2],2)`.
-"Very Strong" evidence was indicated against effect sizes ranging from `r round(Jeffreys_scales$min_effect[7],2)` to `r round(Jeffreys_scales$max_effect[7],2)` and from `r round(Jeffreys_scales$min_effect[8],2)` to `r round(Jeffreys_scales$max_effect[8],2)`.
+Considering the log10(BF) values calculated against the range of SMD effect sizes from 0 to 1 compared to Jeffreys scale (see @fig-main-model panel [C]), the newly added evidence suggested that there was only "decisive" evidence updating the prior against effect sizes ranging from 0 to `r round(Jeffreys_scales$max_effect[1],2)` and from `r round(Jeffreys_scales$min_effect[2],2)` to `r round(Jeffreys_scales$max_effect[2],2)`.
+"Very strong" evidence was indicated against effect sizes ranging from `r round(Jeffreys_scales$min_effect[7],2)` to `r round(Jeffreys_scales$max_effect[7],2)` and from `r round(Jeffreys_scales$min_effect[8],2)` to `r round(Jeffreys_scales$max_effect[8],2)`.
 "Strong" evidence was indicated against effect sizes ranging from `r round(Jeffreys_scales$min_effect[3],2)` to `r round(Jeffreys_scales$max_effect[3],2)` and from `r round(Jeffreys_scales$min_effect[4],2)` to `r round(Jeffreys_scales$max_effect[4],2)`.
 "Substantial" evidence was indicated against effect sizes ranging from `r round(Jeffreys_scales$min_effect[5],2)` to `r round(Jeffreys_scales$max_effect[5],2)` and from `r round(Jeffreys_scales$min_effect[6],2)` to `r round(Jeffreys_scales$max_effect[6],2)`.
-"Weak" or "Negative" evidence was indicated against effect sizes ranging from `r round(Jeffreys_scales$min_effect[9],2)` to `r round(Jeffreys_scales$max_effect[10],2)`.
+"Weak" or "negative" evidence was indicated against effect sizes ranging from `r round(Jeffreys_scales$min_effect[9],2)` to `r round(Jeffreys_scales$max_effect[10],2)`.
 This suggested that the newly acquired evidence generally decreased our belief only in effect sizes that would likely already have been ruled out by the analysis of Hatzigeorgiadis et al.
@@
 targets::tar_load(tidy_classic_model_prior)
+```
 
-targets::tar_load(p_hack_models_plots)
-
-```
+When considering only the new studies published since Hatzigeorgiadis et al.
+[-@hatzigeorgiadisSelfTalkSportsPerformance2011] the frequentist multilevel model estimate (`r round(tidy_rma.mv_model$estimate[1],2)` [95% confidence interval: `r round(tidy_rma.mv_model$conf.low[1],2)`, `r round(tidy_rma.mv_model$conf.high[1],2)`]) was very similar to both their prior estimate, and also the posterior Bayesian estimate from our updated model (see section above).
+For the conditional PET-PEESE estimator however the PET estimate was not statistically significant at the $\alpha=0.10$ level and this adjusted estimate was compatible with a range of estimates from negative effects of similar magnitude to the previously reported positive effect in Hatzigeorgiadis et al.
+[-@hatzigeorgiadisSelfTalkSportsPerformance2011], through to null and trivially positive effects (`r round(tidy_pet_model$estimate[1],2)` [95% confidence interval: `r round(tidy_pet_model$conf.low[1],2)`, `r round(tidy_pet_model$conf.high[1],2)`]) suggesting that publication bias/small study effects may be present in this post-2011 literature.
+These estimates can be seen in the contour enhanced funnel plot in @fig-contour-plot.
 
@@
 
-When considering only the new studies published since Hatzigeorgiadis et al.
-[-@hatzigeorgiadisSelfTalkSportsPerformance2011] the frequentist multilevel model estimate (`r round(tidy_rma.mv_model$estimate[1],2)` [95% confidence interval: `r round(tidy_rma.mv_model$conf.low[1],2)`, `r round(tidy_rma.mv_model$conf.high[1],2)`]) was very similar to both their prior estimate, and also the posterior Bayesian estimate from our updated model (see section above).
-For the conditional PET-PEESE estimator however the PET estimate was not statistically significant at the $\alpha=0.10$ level and this adjusted estimate was compatible with a range of estimates from negative effects of similar magnitude to the previosly reported positive effect in Hatzigeorgiadis et al.
-[-@hatzigeorgiadisSelfTalkSportsPerformance2011], through to null and trivial positive(`r round(tidy_pet_model$estimate[1],2)` [95% confidence interval: `r round(tidy_pet_model$conf.low[1],2)`, `r round(tidy_pet_model$conf.high[1],2)`]) suggesting that publication bias/small study effects may be present in this literature.
-These estimates can be seen in the contour enhanced funnel plot in @fig-contour-plot.
-
-```{r}
-#| label: fig-phack-plot 
-#| fig-width: 5
-#| fig-height: 5
-#| fig-cap: Countour enhanced funnel plot showing effect sizes (scaled in size by inverse sampling variance), thresholds for *p* < 0.05 and 0.01, and both PET-PEESE estimate (in this case it is the PET estimate from the conditional estimator; regression line and ribbon plus "Multilevel PET Estimate" labelled point and interval) and frequentist multilevel model estimate ("Main Model Estimate" labelled point and interval).
-targets::tar_load(main_model_contour_funnel_plot)
-
-main_model_contour_funnel_plot
-
-```
 The Bayesian mixture models assuming the presence of *p*-hacking (note, recall these models ignore the multilevel structure of the effects) also provided reduced adjusted effect estimates, though not to the same magnitude as seen in the PET estimate, with this reduction more prominent when only considering the post-2011 studies and not incorporating the prior from Hatzigeorgiadis et al.
@@
 
-When considering only the post-2011 studies and utilising default prior distributions, robust Bayesian meta-analysis found strong evidence against the effect, $BF_{10}=$`r round(summary(null_robma_model)$components$inclusion_BF[1],3)` with mean model-averaged estimate of `r round(summary(null_robma_model)$estimates$Mean[1],2)` [95% quantile interval: `r round(summary(null_robma_model)$estimates[1,3],2)`, `r round(summary(null_robma_model)$estimates[1,3],2)`, strong evidence in favor of the heterogeneity, $BF_{rf}$ = `r round(summary(null_robma_model)$components$inclusion_BF[2],3)` with mean model-averaged estimate $\tau=$`r round(summary(null_robma_model)$estimates$Mean[2],2)` [95% quantile interval: `r round(summary(null_robma_model)$estimates[2,3],2)`, `r round(summary(null_robma_model)$estimates[2,3],2)`.
-Robust Bayesian meta-analysis found strong evidence in favor of the publication bias, BF_pb = `r round(summary(null_robma_model)$components$inclusion_BF[3],3)`.
+```{r}
+#| label: fig-phack-plot 
+#| fig-width: 7.5
+#| fig-height: 5
+#| fig-cap: Posterior distributions for Bayesian random effects main model (classic model) and mixture model for *p*-hacking both with (B) and without (A) using the prior from Hatzigeorgiadis et al.
+[-@hatzigeorgiadisSelfTalkSportsPerformance2011].
+targets::tar_load(p_hack_models_plot)
+targets::tar_load(p_hack_models_prior_plot)
+
+(p_hack_models_plot / p_hack_models_prior_plot) +
+    plot_annotation(tag_levels = "A",
+                    title = "Adjusted estimates assuming possible presence of p-hacking",
+                    subtitle = "Estimates from Bayesian random effects main model and mixture model for p-hacking both with, and without, using prior\nNote, models ignore multilevel structure",
+                    theme = theme(plot.subtitle = element_text(size = 8))) +
+    plot_layout(guides = "collect") & theme(legend.position = "bottom")
+
+```
+
+```{r}
+library(RoBMA)
+
+sum_null_robma_model <- summary(null_robma_model)
+sum_prior_robma_model <-  summary(prior_robma_model)
+
+```
+
+When considering only the post-2011 studies and utilising default prior distributions, RoBMA found "strong" evidence against the effect, $BF_{10}$ = `r round(sum_null_robma_model$components$inclusion_BF[1],3)` with mean model-averaged estimate of `r round(sum_null_robma_model$estimates$Mean[1],2)` [95% quantile interval: `r round(sum_null_robma_model$estimates[1,3],2)`, `r round(sum_null_robma_model$estimates[1,4],2)`], "strong" evidence in favor of the heterogeneity, $BF_{rf}$ = `r round(sum_null_robma_model$components$inclusion_BF[2],3)` with mean model-averaged estimate $\tau$ = `r round(sum_null_robma_model$estimates$Mean[2],2)` [95% quantile interval: `r round(sum_null_robma_model$estimates[2,3],2)`, `r round(sum_null_robma_model$estimates[2,4],2)`].
+RoBMA without an informative prior also found "strong" evidence in favor of the publication bias, $BF_{pb}$ = `r round(sum_null_robma_model$components$inclusion_BF[3],3)`.
 When including the prior from Hatzigeorgiadis et al.
-[-@hatzigeorgiadisSelfTalkSportsPerformance2011] results were similar with robust Bayesian meta-analysis finding strong evidence against the effect, $BF_{10}=$`r round(summary(prior_robma_model)$components$inclusion_BF[1],3)` with mean model-averaged estimate of `r round(summary(prior_robma_model)$estimates$Mean[1],2)` [95% quantile interval: `r round(summary(prior_robma_model)$estimates[1,3],2)`, `r round(summary(prior_robma_model)$estimates[1,3],2)`, strong evidence in favor of the heterogeneity, $BF_{rf}$ = `r round(summary(prior_robma_model)$components$inclusion_BF[2],3)` with mean model-averaged estimate $\tau=$`r round(summary(prior_robma_model)$estimates$Mean[2],2)` [95% quantile interval: `r round(summary(prior_robma_model)$estimates[2,3],2)`, `r round(summary(prior_robma_model)$estimates[2,3],2)`.
-Robust Bayesian meta-analysis found strong evidence in favor of the publication bias, BF_pb = `r round(summary(prior_robma_model)$components$inclusion_BF[3],3)`.
+[-@hatzigeorgiadisSelfTalkSportsPerformance2011] results were similar with RoBMA finding "strong" evidence against the effect, $BF_{10}$ = `r round(sum_prior_robma_model$components$inclusion_BF[1],3)` with mean model-averaged estimate of `r round(sum_prior_robma_model$estimates$Mean[1],2)` [95% quantile interval: `r round(sum_prior_robma_model$estimates[1,3],2)`, `r round(sum_prior_robma_model$estimates[1,4],2)`], "strong" evidence in favor of the heterogeneity, $BF_{rf}$ = `r round(sum_prior_robma_model$components$inclusion_BF[2],3)` with mean model-averaged estimate $\tau$ = `r round(sum_prior_robma_model$estimates$Mean[2],2)` [95% quantile interval: `r round(sum_prior_robma_model$estimates[2,3],2)`, `r round(sum_prior_robma_model$estimates[2,4],2)`].
+RoBMA with an informative prior also found "strong" evidence in favor of the publication bias, $BF_{pb}$ = `r round(sum_prior_robma_model$components$inclusion_BF[3],3)`.
 
 # Discussion
-The aim of this systematic review and meta-analysis was to update, using Bayesian methods, the results of Hatzigeorgiadis et al.
+The aim of this work was to demonstrate the application of cumulative evidence synthesis methods including; consideration of the initial probability that a new study of the effects of self-talk interventions would shift our prior belief in their effectiveness, the application of priors taken from the previous meta-analysis to be updated by new studies identified to a new posterior estimate of effect, and consideration of other sources of research waste from questionable research practices such as possible publication bias and *p*-hacking.
+Such methods, when used prospectively, can aid researchers in determining whether further research of a particular experimental intervention is in fact warranted; and when used in retrospect may reveal where research has been a waste.
+Given it has been over a decade since Hatzigeorgiadis et al.
+[-@hatzigeorgiadisSelfTalkSportsPerformance2011] published their meta-analysis of self-talk interventions, we used this as an example to demonstrate these methods.
+We now discuss the implications of our results regarding this example and make suggestions for researchers in the sport and exercise sciences to aid them in planning of research.
+
+## Would a new study of a self-talk intervention have changed our prior belief in their effects based on the results of Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011]?
+
+As noted, it could be argued that the estimate of the effectiveness of self-talk interventions was sufficiently precise based on the research conducted prior to 2011.
+The effect estimate from the meta-analysis of Hatzigeorgiadis et al.
+[-@hatzigeorgiadisSelfTalkSportsPerformance2011] has a width spanning 0.2 SMD, and similarly so for many of the moderator estimates.
+Given this, a researcher considering whether or not to conduct a study of self-talk interventions effects on sports/motor performance could consider whether this is worthwhile by using Bayesian updating with simulated studies to determine both how large an effect, and how large a sample, would be needed to meaningfully shift the prior to posterior distribution.
+If an unrealistically large effect (whether positive or negative) or an impractically large sample size, or both, would be needed for a new studies effect estimate to shift belief in the effect estimate then it might be considered that it is either implausible or simply not worth the resources to conduct such a study.
+In such a case it might be considered that the current estimate of the effect is sufficiently precise.
+Indeed, this appears to be the case with the effect estimate from Hatzigeorgiadis et al.
 [-@hatzigeorgiadisSelfTalkSportsPerformance2011].
-Since that time a further `r length(unique(data$study))` new studies had been published which were identified in our searches and we could include all but one in our analysis.
-Our finding suggested that the cumulative impact of this research over the last decade and more has done little to further our understanding of the effects of self-talk interventions.
+
+As can be seen in @fig-additional-study, given the precision of the prior distribution  from Hatzigeorgiadis et al.
+[-@hatzigeorgiadisSelfTalkSportsPerformance2011], irrespective of the sample size or magnitude of effect and the extent to which it disagreed with the prior estimate, no single new study could shift the posterior distribution to an extent that it didn't still have ~95% of its mass within the 95% quantile interval of the prior distribution.
+As such, taking the estimate from Hatzigeorgiadis et al.
+[-@hatzigeorgiadisSelfTalkSportsPerformance2011] at face value, we would likely conclude that performing a new study would be a waste of resources.
+The number of studies since 2011 has roughly doubled and yet no single study *a priori* would have been able to shift belief in the estimate of the effects of self-talk interventions.
+Of course, it may be that this sheer volume of additional evidence might have updated belief in the estimate of their effects (indeed, this is something that could have also been simulated i.e., how many additional studies with particular effect sizes and sample sizes would be needed to shift belief?).
+But, had this been considered during study planning, it might have saved researchers in this field considerable resources that could have been directed towards other research questions or programmes.
+
+## To what extent have studies published since Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011] updated belief in the effects of self-talk interventions?
+
+Although *a priori* the use of simulation is valuable to see whether a new study is worth adding to the body of literature because it will meaningfully change our beliefs in an effect, in the example of self-talk interventions there has already been a considerable addition of evidence to the corpus.
+In such a situation it's worthwhile to consider the extent to which this new evidence has shifted beliefs.
+The use of Bayesian updating for meta-analysis, where there is already a previous meta-analytic estimate on which to base a prior distribution, can also be a more efficient means of conducting evidence synthesis as searches and inclusion of studies can be limited to dates *after* the publication of that previous estimate.
+The extent to which new evidence has shifted beliefs can be quantified and the value of such work can be reflected on.
+
+So, we also updated using Bayesian methods the results of Hatzigeorgiadis et al.
+[-@hatzigeorgiadisSelfTalkSportsPerformance2011] with studies published since 2011.
+Since that time a further `r length(unique(data$study_code))` new studies had been published which were identified in our searches and we could include all but one in our analysis.
+Our findings suggested that the cumulative impact of this research over the last decade and more has done little to further our understanding of the effects of self-talk interventions.
 The results showed that the overall pooled estimate from the meta-analysis was a SMD of `r round(tidy_main_model$estimate[1],2)` [95% quantile interval: `r round(tidy_main_model$conf.low[1],2)`, `r round(tidy_main_model$conf.high[1],2)`].
@@
 [-@hatzigeorgiadisSelfTalkSportsPerformance2011] of 0.48 [95% confidence interval: 0.38, 0.58].
-The Bayes factors calculated indicated that the included studies largely reflected “Weak”, or even very mildly "Negative", evidence against effects ranging from `r round(Jeffreys_scales$min_effect[9],2)` to `r round(Jeffreys_scales$max_effect[10],2)`, and only provided "Decisive" evidence updating the prior against effect sizes ranging from 0 to `r round(Jeffreys_scales$max_effect[1],2)` and from `r round(Jeffreys_scales$min_effect[2],2)` to `r round(Jeffreys_scales$max_effect[2],2)`.
+The log10(BF) calculated indicated that the included studies largely reflected “weak”, or even very mildly "negative", evidence against effects ranging from `r round(Jeffreys_scales$min_effect[9],2)` to `r round(Jeffreys_scales$max_effect[10],2)`, and only provided "decisive" evidence updating the prior against *a priori* implausible effect sizes ranging from 0 to `r round(Jeffreys_scales$max_effect[1],2)` and from `r round(Jeffreys_scales$min_effect[2],2)` to `r round(Jeffreys_scales$max_effect[2],2)`.
 
@@
 lochbaum <- c(0.57,1.35,0.65,0.32,0.24,0.51,0.51,0.48,0.72,1,0.22,0.49,0.48,0.47,0.68,0.28,0.2,0.44,0.32,0.34,0.84,0.38,0.38,0.38,0.74,0.72,0.82,0.72,0.15,0.47,0.31,0.49,0.49,0.65)
-# Prediction interval
-targets::tar_load(main_model)
+```
+
+```{r}
 nd <- data.frame(study = "new", vi = 0)
+
 pred_int_data <- brms::posterior_predict(
@@
   )
-  pred_int_data <- tidybayes::median_qi(pred_int_data) %>%
-    mutate(label = as.character("Posterior Pooled Estimate"))
+
+pred_int_summary <- tidybayes::qi(pred_int_data)
 ```
 
-The findings of our updated Bayesian meta-analyses reiterate the positive effect of self-talk interventions on sport/motor performance on average.
+In one sense, the findings of the updated Bayesian meta-analyses do reiterate the positive effect of self-talk interventions on sport/motor performance on average reported by Hatzigeorgiadis et al.
+[-@hatzigeorgiadisSelfTalkSportsPerformance2011].
 Indeed, the estimate reflects the typical effect of other psychological interventions (0.51 \[95% confidence interval: 0.42, 0.58\]) as identified by Lochbaum et al.
-[-@lochbaumSportPsychologyPerformance2022] in their umbrella review; though notable they also reported a wide range of overall effect estimates between positively directed interventions/strategies (`r min(lochbaum)` to `r max(lochbaum)`).
+[-@lochbaumSportPsychologyPerformance2022] in their umbrella review; though notably they also reported a wide range of overall effect estimates between positively directed interventions/strategies (`r min(lochbaum)` to `r max(lochbaum)`).
 Reflecting this, Hatzigeorgiadis et al.
 [-@hatzigeorgiadisSelfTalkSportsPerformance2011] reported $\tau$ = 0.27 (though as noted in footnote$^7$ it is not clear which level this pertains to) for the self-talk intervention studies they explored, and our study level estimate was not dissimilar to this ($\tau$ = `r round(tidy_main_model$estimate[2],2)` [95% quantile interval: `r round(tidy_main_model$conf.low[2],2)`, `r round(tidy_main_model$conf.high[2],2)`]).
-Indeed, our prediction interval ranged from `r round(pred_int_data$ymin,2)` to `r round(pred_int_data$ymax,2)`.
+Indeed, our prediction interval ranged from `r round(pred_int_summary[1],2)` to `r round(pred_int_summary[2],2)`.
 Considering this heterogeneity in effects, Hatzigeorgiadis et al.
-[-@hatzigeorgiadisSelfTalkSportsPerformance2011] previously examined varied theoretically plausible moderators of the effectiveness of self-talk interventions.
+[-@hatzigeorgiadisSelfTalkSportsPerformance2011] previously examined varied theoretically plausible moderators of the effectiveness of self-talk interventions which we were also able to update with new evidence.
+It may be the case that since 2011 the majority of research has focused on understanding exactly how best to employ self-talk interventions.
 
 Hatzigeorgiadis et al.
-[-@hatzigeorgiadisSelfTalkSportsPerformance2011] suggested that, under certain task conditions, or the nature of the intervention, or the specific participants, there could possibly be differential effects of self-talk.
+[-@hatzigeorgiadisSelfTalkSportsPerformance2011] suggested that, considering theoretically driven moderators, there could possibly be differential effects of self-talk interventions under certain task conditions, based on the nature of the intervention, or for different participant populations.
 Their results suggested that, whilst self-talk interventions in general were effective, greater effects were seen for fine motor tasks and the performance of novel tasks.
@@
 [-@hatzigeorgiadisSelfTalkSportsPerformance2011].
-Posterior estimates were largely similar for all moderators which were updated, and Bayes factors suggested that the newer evidence provided relatively weak evidence against the prior effects reported by Hatzigeorgiadis et al.
+Posterior estimates were broadly similar for all moderators which were updated, and log10(BF) suggested that the newer evidence provided relatively weak evidence against the prior effects reported by Hatzigeorgiadis et al.
 [-@hatzigeorgiadisSelfTalkSportsPerformance2011] or evidence suggesting slightly smaller effects for certain moderators (though qualitative conclusions remained the same).
+Where there were clearer shifts in the posterior distributions these were typically towards the overall pooled effect size within the main model possibly suggesting that some factors were not as strong in moderating effects as previously thought.
 
-Despite further supporting the effectiveness of self-talk interventions and the factors that moderate this, our results suggest that cumulatively the past decade and more of research has done little to further our understanding of these effects.
-Of course, as we noted in the introduction, this lack of change to our beliefs despite the cumulative evidence could be considered as evidence that the production of such evidence is wasteful.
-The present updated Bayesian meta-analyses makes this quite clear; considering the limited resources and time for conducting research, it may be worth moving onto to other more pertinent questions regarding psychological interventions for sport/motor performance.
+Despite supporting the effectiveness of self-talk interventions and the factors that moderate this, our results suggest that cumulatively the past decade and more of research has done little to further our understanding of these effects.
+Of course, as we noted in the introduction, this lack of change to our beliefs despite the cumulative evidence could be interpreted as evidence that the production of such research could be considered wasteful.
+The present updated Bayesian meta-analyses, and indeed the *a priori* simulations too, makes this quite clear; considering the limited resources and time for conducting research, it may be worth moving onto to other more pertinent questions or research programmes.
+But, both simulating the impact of a new trial to determine if it is worth performing, or updating a prior meta-analysis estimate with new evidence from subsequent trials, entail the assumption that the previous estimate is not itself biased by questionable research practices [@friesePHackingPublicationBias2020].
+Further, in updating a prior estimate there is the assumption that the newer evidence is also free from such questionable research practices.
 
-It is worth noting though that any conclusions regarding “research waste” are specific to the context explored here: namely, self-talk *interventions*.
-As explained, the post-2011 years have seen theoretical advancements in conceptualisation of the construct of self-talk [@brinthauptSelftalkResearchChallenges2023; @geurtsMakingSenseSelf2018; @hardyReflectionsMaturingResearch2018; @latinjakSelfTalkInterdisciplinaryReview2023; @vanraalteSelftalkReviewSportspecific2016; @latinjakSpeakingClearly102019].
-A key distinction in modern integrative reviews of the construct in relation to sport/motor performance is between “strategic” and “organic” self-talk [@latinjakSpeakingClearly102019].
-Latinjak et al.
-[-@latinjakSpeakingClearly102019] highlights this and note research has focused primarily on the former given it, by definition, can be deliberately employed in a predetermined interventional manner.
-As such, most research has focused upon the exploration of self-talk *interventions* at the expense of exploring the use of spontaneous or reflexive self-talk that organically occurs as thoughts for the performer addressed to themselves.
-Latinjak et al.
-[-@latinjakSpeakingClearly102019] argue that future research on any kinds of self-talk interventions can improve our understanding of the effectiveness of self-talk strategies, we would disagree given the results of our updated analyses.
-However, we do agree with Latinjak et al.
-[-@latinjakSpeakingClearly102019] that it may be more appropriate to focus on other research questions regarding self-talk.
-For example, in their reflection Hardy et al.
-[-@hardyReflectionsMaturingResearch2018] argue that greater efforts should be made in extending the existing cross-sectional work exploring organic self-talk into longitudinal designs and the use of structural equation modeling (preferably informed by causal directed acyclic graphs).
-The use of such designs might allow for the exploration of causal effects of organic self-talk strategies which might be less amenable to structured experimental intervention research, as compared to the glut of strategic self-talk intervention studies.
-These can also support cumulative evidence synthesis through meta-analysis as techniques have been developed to combine and analyse them in such a framework [@cheungMetaAnalysisStructuralEquation2015; @cheungMetaAnalyticStructuralEquation2021].
+## Is there evidence of questionable research practices in the self-talk interventions literature?
 
-ADD - https://www.researchgate.net/publication/338361731_Careful_what_you_say_to_yourself_Exploring_self-talk_and_youth_tennis_performance_via_hierarchical_linear_modeling
+As explained, we limit our examination of the presence of questionable research practices to the subsequent post-2011 literature and make the reasonable assumption that, given the replication crisis and subsequent methodological reform efforts kicked off proper in the early 2010s [@lakensConcernsReplicabilityTheorizing2023], the presence of questionable research practices was likely as bad if not worse in the literature included in Hatzigeorgiadis et al.
+[-@hatzigeorgiadisSelfTalkSportsPerformance2011].
+The existence of evidence suggesting prior questionable research practices such as publication bias or *p*-hacking might be cause for an evaluation of whether prior research is in fact worth building upon, or whether instead it may be worth starting afresh to determine if there really is an intervention effect whilst incorporating safe-guards for such issues e.g., pre-registration/registered-reports [@chambersPresentFutureRegistered2022].
+
+The results of our exploration of possible questionable research practices sadly paint a troubling picture for self-talk interventions.
+There is strong evidence that both publication bias and *p*-hacking seem to be present.
+The adjusted estimates in all of the methods examined were reduced compared to the unadjusted estimated effect of self-talk interventions with this being most evident considering models of publication bias and to an extent that it was compatible with a null effect (i.e., PET-PEESE and RoBMA model averaging).
+Granted, in our present example we have only considered the newly produced evidence since 2011 and it might be argued that the studies prior to this may not be subject to such questionable research practices.
+However, as noted we think it is a reasonable assumption that things were probably as bad, if not worse, prior to 2011.
+Further, in the Bayesian mixture model for *p*-hacking, and the RoBMA, we were also able to explore adjusted estimates whilst accounting for the prior estimate from Hatzigeorgiadis et al.
+[-@hatzigeorgiadisSelfTalkSportsPerformance2011].
+Even when considering this we still find strong evidence of questionable research practices influencing this literature.
+
+## Has research conducted since Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011] been a waste?
+
+Given the results presented we find it hard to conclude anything other than that there has been considerable "research waste".
+Some might see this conclusion as being quite uncharitable but we think that it is justified regarding the specific  context explored here: namely, the literature on self-talk *interventions* and their effects on sports/motor performance.
+Considering the general lack of impact seen upon the prior estimate from Hatzigeorgiadis et al.
+[-@hatzigeorgiadisSelfTalkSportsPerformance2011] from simulating a new study, and the relative lack of impact from the updating of this prior estimate with newly conducted studies post-2011, in so far as the effects of self-talk interventions are concerned we have not learned anything new.
+
+An objection to concluding that these post-2011 studies are "research waste" though might be that they may have refined understanding of more specific questions, such as the impact of different moderators on the self-talk interventions effectiveness, which may have been the goals of these new studies (not merely whether self-talk interventions in general improve performance).
+As mentioned, some had concluded that post-2011 the field had "matured" and, under the assumption that self-talk interventions do indeed improve performance, moved towards theorising and exploring the possible mechanisms for *why* it was effective [@hardyReflectionsMaturingResearch2018; @galanisChapterWhySelfTalk2016].
+However, as we also saw, many of the theoretically informed moderators that were explored also updated little and where they did they tended to shift closer to the overall posterior pooled effect estimate.
+Further, considering the results of our exploration of questionable research practices, it is not particularly clear whether the already proven positive effects of self-talk interventions is a reasonable assumption to work from any more, and research addressing the question of *why* the interventions are effective might be built upon a house of cards.
+Based upon the results presented here it is not clear whether self-talk interventions have any impact on sports/motor performance.
+
+The amount of research since Hatzigeorgiadis et al.
+[-@hatzigeorgiadisSelfTalkSportsPerformance2011] roughly doubled.
+Had approaches such as those presented here been employed *a priori* by researchers in planning these studies to consider the impact that such evidence might have had on updating prior estimates of self-talk interventions effects, or indeed the quality of those prior estimates, a lot of waste might have been avoided.
+Granted, some of the methods presented here were not necessarily readily available to understand and utilise by researchers at the time they were conducting their work.
+But, the example of self-talk interventions can act as a warning to researchers in the sport and exercise sciences about what kinds of questions they should ask themselves prior to beginning their work.
+
+Although the literature on self-talk *interventions* and their effects on sports/motor performance specifically could be considered wasteful, as explained, the post-2011 years have seen theoretical advancements in conceptualisation and operationalisation of the construct of self-talk [@brinthauptSelftalkResearchChallenges2023; @geurtsMakingSenseSelf2018; @hardyReflectionsMaturingResearch2018; @latinjakSelfTalkInterdisciplinaryReview2023; @vanraalteSelftalkReviewSportspecific2016; @latinjakSpeakingClearly102019; @vanraalteCommonLanguageCategorization2019].
+Alongside the discussion within the broader psychological literature regarding replication concerns there have also been calls to improve theorising [@eronenTheoryCrisisPsychology2021] and measurement practices [@flakeMeasurementSchmeasurementQuestionable2020].
+These are important steps that researchers should consider before they move to testing hypotheses such as whether intervening on a psychological construct produces particular causal outcomes [@scheelWhyHypothesisTesters2021].
+As such, it would be unfair to suggest that work aimed in these specific theoretical/operationalisation directions has been wasteful and attempts at cumulative evidence synthesis which draw such conclusions might also consider qualitative appraisal of the broader literature saving conlusions about "research waste" for the specific context explored.
 
@@
 
-This review and meta-analysis has shown that evidence still supports positive self-talk interventions as improving performance since the publication of the meta-analysis by Hatzigeorgiadis et al.
-[-@hatzigeorgiadisSelfTalkSportsPerformance2011].
-Overall, the posterior estimates for both overall and moderator effects in this updated meta-analysis were very similar to the priors from Hatzigeorgiadis et al.
-[-@hatzigeorgiadisSelfTalkSportsPerformance2011], giving confidence in the overall positive effects.
-Therefore, coaches and athletes might still consider implementing positive self-talk to maximise performance.
-However, given that cumulatively the past decade and more of research has done little to further our understanding of self-talk intervention effects specifically it is reasonable to consider it suggestive of “research waste”.
-Considering the limited resources and time for conducting research, it may be worth moving onto other more pertinent questions regarding psychological constructs impact upon sport/motor performance.
-In the case of self-talk specifically, future research should look to explore and test the more recent theoretical contributions regarding the conceptualisation of self-talk and, in particular, the use of appropriate designs to test the effects of organic self-talk upon sport/motor performance.
+This work has demonstrated the application of cumulative evidence synthesis methods including; consideration of the initial probability that a new study of the effects of self-talk interventions would shift our prior belief in their effectiveness, the application of priors taken from the previous meta-analysis to be updated by new studies identified to a new posterior estimate of effect, and consideration of other sources of research waste from questionable research practices such as possible publication bias and *p*-hacking.
+We presented the application of these methods in the example of self-talk interventions for sports/motor performance given it has been over a decade since Hatzigeorgiadis et al.
+[-@hatzigeorgiadisSelfTalkSportsPerformance2011] published their meta-analysis of self-talk interventions.
+The application of these methods highlight that much of the literature on this topic could be considered "research waste"; the impact of any new study upon the prior estimate from Hatzigeorgiadis et al.
+[-@hatzigeorgiadisSelfTalkSportsPerformance2011] would have had added little evidence to change prior beliefs, the doubling of research conducted since 2011 also added little evidence to update the prior estimate, and it is likely that much of the research post-2011 (and likely prior to 2011) has been subject to questionable research practices making it unclear whether self-talk interventions affect sports/motor performance or not.
+This example can act as a warning to researchers in the sport and exercise sciences about what kinds of questions they should ask themselves prior to beginning their work.
+Such methods as those demonstrated here, when used prospectively, can aid researchers in determining whether further research of a particular experimental intervention is in fact warranted; and when used in retrospect may reveal where research has been a waste.
+Considering the limited resources and time for conducting research their application may suggest it to be more worthwhile moving onto other more pertinent research questions or programmes.
+In the case of self-talk specifically, future research might be best placed to continue with the intention of building strong theories regarding the conceptualisation and operationalisation of self-talk and, following this, test if there really is an intervention effect as hypothesised whilst incorporating safe-guards for questionable research pratices e.g., pre-registration/registered-reports [@chambersPresentFutureRegistered2022].
 

### 2024-08-15 _targets.R

@@ -30,7 +30,9 @@ tar_option_set(
     # "RoBMA",
     "publipha",
     "future",
-    "faux"
+    "faux",
+    "quarto",
+    "grateful"
   )
 )
 
@@ -219,6 +221,12 @@ list(
   tar_target(BF_curve_overtness_selection_plot_tiff, make_plot_tiff(BF_curve_overtness_selection_plot, 7.5, 5, "plots/BF_curve_overtness_selection_plot.tiff")),
   tar_target(BF_curve_training_plot_tiff, make_plot_tiff(BF_curve_training_plot, 7.5, 5, "plots/BF_curve_training_plot.tiff")),
   tar_target(BF_curve_study_design_plot_tiff, make_plot_tiff(BF_curve_study_design_plot, 7.5, 5, "plots/BF_curve_study_design_plot.tiff")),
-  tar_target(cumulative_main_model_plot_tiff, make_plot_tiff(cumulative_main_model_plot, 7.5, 5, "plots/cumulative_main_model_plot.tiff"))
+  tar_target(cumulative_main_model_plot_tiff, make_plot_tiff(cumulative_main_model_plot, 7.5, 5, "plots/cumulative_main_model_plot.tiff")),
+
+  # Manuscript
+  tar_target(grateful_report, cite_packages(out.dir = "pre_print", cite.tidyverse = TRUE, out.format = "pdf")),
+  tar_quarto(diagnostic_plots, path = "plots/diagnostic_plots.qmd"),
+  tar_quarto(response_to_reviewers.qmd, path = "pre_print/response_to_reviewers.qmd"),
+  tar_quarto(pre_print, path = "pre_print/pre_print_v2.qmd")
 
 )

### 2024-08-15 _targets.R
Removing unused packages from pipeline calls

@@ -25,12 +25,10 @@ tar_option_set(
     "base",
     "furrr",
     "patchwork",
-    "marginaleffects",
     "broom.mixed",
     # "RoBMA",
     "publipha",
     "future",
-    "faux",
     "quarto",
     "grateful"
   )

### 2024-08-15 R/functions.R
Add pipeline htmlwidget to repo

@@ -243,18 +243,6 @@ make_plot_tiff <- function(plot, width, height, path) {
 
 }
 
-ggplot_2_grob_nback <- function(plot) {
-  plot_grob <- ggplot2::ggplotGrob(plot)
-  plot_new <- ggpubr::as_ggplot(plot_grob)
-
-  remove(plot)
-  remove(plot_grob)
-
-  gc()
-
-  return(plot_new)
-}
-
 get_logBF_curve <- function(model) {
 
   plan(multisession, workers = 5)

### 2024-08-15 pre_print/pre_print_v2.qmd
Update bib file and pre-print with missing ref

@@
 # year: 2025 # defaults to current year
-keywords: [psychological intervention, cumulative evidence, research waste] # optional
+keywords: [psychological intervention, cumulative evidence synthesis, research waste] # optional
 # optional link to Supplementary Material:

### 2024-08-16 pre_print/pre_print_v2.qmd
Final revised v2 preprint

@@
       - ref: 1
+      - ref: 2
     orcid: 0000-0002-8003-0757
     corresponding: true
-    email: james.steele@solent.ac.uk
+    email: james@steele-research.com
 affiliations:
@@
         name: Department of Sport and Health, Solent University, UK
+      - id: 2
+        name: Steele Research Ltd, UK
 abstract: |
@@
 These are important steps that researchers should consider before they move to testing hypotheses such as whether intervening on a psychological construct produces particular causal outcomes [@scheelWhyHypothesisTesters2021].
-As such, it would be unfair to suggest that work aimed in these specific theoretical/operationalisation directions has been wasteful and attempts at cumulative evidence synthesis which draw such conclusions might also consider qualitative appraisal of the broader literature saving conlusions about "research waste" for the specific context explored.
+As such, it would be unfair to suggest that work aimed in these specific theoretical/operationalisation directions has been wasteful and attempts at cumulative evidence synthesis which draw such conclusions might also consider qualitative appraisal of the broader literature saving conclusions about "research waste" for the specific context explored.
+But, whilst it has been argued that cumulative evidence synthesis methods such as meta-analysis to test theoretically derived hypotheses [@haggerTestingTheoryPredictions2024], for self-talk interventions specifically it may be worth starting afresh to determine if there really is an intervention effect whilst incorporating safe-guards for such issues as the questionable research practices explored here e.g., pre-registration/registered-reports [@chambersPresentFutureRegistered2022].
 
@@
 Considering the limited resources and time for conducting research their application may suggest it to be more worthwhile moving onto other more pertinent research questions or programmes.
-In the case of self-talk specifically, future research might be best placed to continue with the intention of building strong theories regarding the conceptualisation and operationalisation of self-talk and, following this, test if there really is an intervention effect as hypothesised whilst incorporating safe-guards for questionable research pratices e.g., pre-registration/registered-reports [@chambersPresentFutureRegistered2022].
+In the case of self-talk specifically, future research might be best placed to continue with the intention of building strong theories regarding the conceptualisation and operationalisation of self-talk and, following this, test if there really is an intervention effect as hypothesised whilst incorporating safe-guards for questionable research practices e.g., pre-registration/registered-reports [@chambersPresentFutureRegistered2022].
 

### 2024-11-26 pre_print/_extensions/smnnlt/sportrxiv/partials/before-body.tex
Final revised v2 preprint
Update preprint to add PCI recommendation (and tidy front formatting)

@@
   \lhead{\href{https://sportrxiv.org}{\includegraphics[width = 40mm]{logo.png}}}
-  \chead{$printnote$}
+  \chead{\scriptsize{Reviewed and recommended through \href{https://healthmovsci.peercommunityin.org/articles/rec?id=44}{Peer Community in Health and Movement Sciences}}}
   \rhead{\$license-type$\vspace{0.2mm}}
-  \lfoot{\color{gray}All authors have read and approved  this version  of the manuscript. \linebreak The manuscript was last updated on \today}
+  \lfoot{\color{gray}\footnotesize{All authors have read and approved this version  of the manuscript. \linebreak The manuscript was last updated on \today}}
 }
@@
 \vspace*{0.1cm}
-{\huge{\textbf{$articletitle$}}}
+{\Large{\textbf{$articletitle$}}}
 \end{spacing}
@@
 \begin{spacing}{1}
-Cite as: \shortauthor$if(year)$($year$)$else$(\the\year)$endif$. $articletitle$. \emph{SportRxiv.} \\
+Cite as: \shortauthor$if(year)$($year$)$else$(\the\year)$endif$. $articletitle$. \emph{SportRxiv.} DOI: 10.51224/SRXIV.348 \\
 \end{spacing}
@@
 \begin{abstractbox}
-  $abstract$ 
+  \footnotesize{$abstract$}
   $if(keywords)$
-  \\ \\
   Keywords: \emph{${for(keywords)}${keywords}${sep}; ${endfor}}
